\section{Argentum Consortium}
\label{sec:Argentum Consortium}

The idea for the Argentum Consortium was born when specialized adventurers were
needed to fend off the multifarious forces of evil. After the power struggles on
a distant plane that doomed an entire island, the founder of the Argentum
Consortium and his associates fled to the nearby continent of
\nameref{sec:Goltir}. Rewis Byne, an outsider to the world of Aror, then
founded the Argentum Consortium in order to help people in need.

The concept of the Argentum Consortium allows anyone to sign up and go on
missions assigned by the leadership. Originally, every specialized group of
adventurers would have their own leadership, which again would be lead by a
council of five. This idea has since shifted, and these specialized groups have
been dissolved. Nowadays, these groups are categorized by city, region or even
continent, rather than specialisation.

The longer an adventurer is employed by the Argentum Consortium and the more the
adventurer contributes to its success, the better is his standing in the
association. This includes services as insurance, resurrection (when possible),
and even rescuing from other planets if needed.

The downfall of the distant planet, on which the Argentum Consortium was
founded, dissolved the Argentum Consortium for several decades. Rewis Byne,
amongst others, was picked up by Henri Durant to help him fight off the devil
invasion of \nameref{sec:Forsby} in the year \emph{MI:2017}. Before the final
fight, and afterwards, they joined together to re-found the Argentum
Consortium in the world of Aror. Rewis Byne pulls the strings behind the
scenes, and stays unseen for the public. Henri Durant is still the chief of
the Argentum Consortium, but only entangles in affairs that are of utmost
importance.

Members of the Argentum Consortium gain access to the guild's resources (such
as spell crafting services, adventuring equipment, and insurance policies),
but are required to return a specific percentage of earnings from adventures
back to the guild. The guild has branches in most city kingdoms, and has its
headquarters in \nameref{sec:Forsby}.

\begin{35e}{Argentum Consortium}
  The Consortium is a lawful neutral adventurer's guild that offers services
  to adventurers in exchange for a share of the profit. It serves only its
  members, but can also be hired should anyone require its services, or the
  aid of mercenaries.
\end{35e}
