\section{Church of Light}
\label{sec:Church of Light}

The \emph{Church of Light} was the main church of the lesser deity
\nameref{sec:Griannar} before his death during the \nameref{sec:Holy
Crusade}. It was both a knight order, as well as a church for the common man,
and held vast political and military power before its fall shortly after
the disappearance of its patron deity.

They openly advocated for a celibate, tempered life style filled with humility
and service to the church. The church itself advocated a fight against evil in
all its forms, and abhorred devil worship, the undead (even vampires), and
fey. Many knights of the church joined the \nameref{sec:Second Crusade}, in an
attempt to stop the spreading of fey and evil druids. Most congregation were
lead by a single priest, who gathered for masses in small churches once per
week. These churches were not only places of worship, but also places from
which the priest would work for charity towards his congregation, and
strangers that required aid. The church, and its followers, were upheld by
their holy scriptures not to amass wealth, yet give to the poor and those in
need. A common criticism of the church was that the highest clergy, the
abbots, cardinals and bishops had lost sight of that directive by becoming
rich, and powerful aristocrats. Nevertheless the common priests, and acolytes
were seen as a force of good in their respective communities, even splitting
the church of the Silent Queen on whether they should be prosecuted or not.

Very little is known about the church's dogma, organisation or its members in
modern times, since the followers of the \nameref{sec:Silent Queen}, as well
as those of \nameref{sec:Aria} went to great lengths to eradicate any written
accounts of the church, and its dogma. After its fall the holy scripture of
the church was burned en masse, its clerics and priests were driven into exile,
and its congregations broke apart opting to join other churches, and religions.

Even though the church played such a pivotal role in Aror's early history,
not many historians pursue a historical research to the church, its doctrine,
or symbolism. Nowadays, all that remains is its symbol, a stylised version of
a sun with eight rays of sunshine emanating from it, upon crumbling old ruins,
and hidden away in the heraldry of long forgotten houses of nobility.
