\section{Ancient Deepkin Clans}
\label{sec:Deepkin Clans}

The early ages of the before the great exodus (GT:-600 up until GT:500) saw the
foundation of many great \nameref{sec:Deepkin} clans and families, that held
vast and unparalleled power over many early Deepkin settlements and cities
beneath the surface. Each clan was specialised in few areas of craftsmanship,
and regularly traded with each other. Together they formed a loose coalition
called the ``moot'', whose power rivalled even that of greater dwarven clans
of the deep.

These ancient clans were responsible for developing the \nameref{sec:Arcane
  Marks}, which were used to mark the most distinguished members of each house.
The arcane mark of a Deepkin clan bore both the symbol of the clan itself,
name of the bearer, their rank within the house, and often also with custom
arcane enhancements the wearer might find useful in their journey or
profession. The knowledge to craft and apply arcane marks survived to the
modern day, as did many of the most important technologies that were developed
by these houses. Deepkin marks are hereditary (even across many generations),
but may or may not manifest in distant generations. Since Deepkin were always
happy to inter-marry with the other core humanoid races, it is not uncommon
for elves, dwarves, halflings or humans to bear clan marks granted to them by
a distant ancestor.

Ultimately this moot dissolved and founded \nameref{sec:Stenheim}, which many
of these ancient Deepkin families joined voluntarily. While elements of the
individual families survive in Stenheim and beyond, over the years the clear
labour division between the families and clans have eroded away. Most of their
glory, knowledge and power has been lost during the great exodus, and what
remains can now be found as part of the kingdom of Stenheim.

\subsection{Nicte}
\label{sec:Nicte}
The largest clan was the deepkin clan of ``Nicte''. They were mostly traders,
diplomats, bankiers and organisers. In terms of financial wealth and power,
clan Nicte was unsurpassed in the earlier days. To this day, descendants of
the Nicte clan run most of the banks and larger trading outposts of Stenheim.
Their symbol were the two suns, partially overlapping surrounded several rays.
One of the clans greatest daughters is \nameref{sec:Aren Fel}. Their greatest
invention are the \nameref{sec:Blood Locks}, which are still in use to this
day.

\subsection{Aru\'el}
\label{sec:Aru'el}
The clan of ``Aru'el'' were the largest and most proficient arcane smiths among
the Deepkin. Their golem craftsmanship became legendary, even among other
races, and it is thanks to this clan that Deepkin have a reputation for being
extra-ordinary engineers and smiths. Everblack golems crafted by clan Aru'el
were instrumental in defeating the \nameref{sec:Ilians}, paving the way for
establishing Stenheim in relative peace. Their symbol were two hammers,
crossed over a furnace. Their greatest invention was the
\nameref{sec:Everblack Golem} which helped to win the war against the Ilians.

\subsection{Loras}
\label{sec:Loras}
Clan ``Loras'' were society builders, specialising in civil technologies,
engineering, as well as sciences of building, organising and maintaining large
communities such as cities and kingdoms. They were avid lawyers, judges,
scientists, leaders and engineers. Clan Loras did not fully join Stenheim
after the great exodus, instead its members split across the world offering
their knowledge and services to the other kingdoms and large baronies. Their
symbol was a scale, held aloft by a hand. Their greatest invention was a
common set of basic laws and principles, called ``Loras' Law'' that is the
foundation of many modern frameworks of law and order.
