\section{Helemic Order}
\label{sec:Helemic Order}

The Helemic Order is a secretive, monastic order whose members are all
wielders of psionic powers. Although the members themselves do not lie about
their affiliation to Helemic Order, the order attempts to remain hidden
throughout Aror. Their bases of operations are a secret, only known to trusted
members, and they also hold their meetings in secret. The order's symbol is a
violet sun from which eight rays emanate.

In their philosophy and teachings, psionic powers are the superior form of
magic, as it stems from a well trained and disciplined mind, and also
represents the next step in the progress of any of the intelligent
species. They train anyone who shows latent psionic abilities, and form
schools, academies and learning centres where they train the psionic gifts of
those that show potential.

The Order has head quarters in most major city kingdoms, but are said to hail
originally from \nameref{sec:Fes al-Bashir}. From those head quarters they
send out their agents, psionically gifted warriors, to find other gifted
people and recruit them into their order. There are rumours that a specially
constructed psionic beacon, called the \emph{Monolith}, allows them to scour
the world for those that have latent psionic abilities. The Order rediscovered
how to store psionic powers in \nameref{sec:Everblack}, a process originally
invented by the \nameref{sec:Ilians}, which turns the crystal green in the
process. It is said that the \emph{Monolith} is a large everblack crystal
charged with psionic powers that amplifies any psycer's power that
telepathically links with it. The monolith also has a drawback, as it may
easily overwhelm a poorly trained psionic mind.

Many of the other religious organisations, especially those of
\nameref{sec:Lor}, \nameref{sec:Order}, and those that follow devils, show
animosity or sometimes even hostility against the Helemic Order. The most
common accusation is either being in league with surviving pockets of the
\nameref{sec:Ilians} or being outright corrupted, and forced into service of
the \nameref{sec:Abyss}. Their secrecy only adds fuel to the fire, as many
claim they are worshipping the Abyss in secret. Those accusations are not
unfounded, as demons and the abyss have corrupted powerful psykers in the
past. Weak psykers are especially at risk of being corrupted and are thus
always accompanied by a more experienced psyker to aid, shield, and train
them.

Outside of recruitment the main purpose of the Helemic Order is to gather and
hoard psionic knowledge and artefacts. They try to stay out of most conflicts
regarding evil, but are known to join adventurer's guilds, groups and
expedition if they believe a psionic artefact or knowledge can be uncovered.

Since psionic potential is incredibly rare on Aror the order struggles to
recruit enough members to remain relevant. Many of those few that do develop
psionic powers later in life, do not wish to join the other for various
reasons. Most fear prosecution by the churches, social isolation through the
orders secrecy and lack of good standing with other organisations, or outright
corruption by either linking with a monolith or by being found by the Abyss.
