\subsection{House Ranian}
\label{sec:House Ranian}

House Ranian is a bank that was founded in \emph{MI:1600} in
\nameref{sec:Tredegar} and has since grown to be the largest bank in all of
Aror. It's banner is a large scale that is perfectly balanced.

It is run by two noble families: the half-elven family \emph{Ranian} as well
as the elven noble family \emph{El'Ereth}. It is the largest financier and
provider of capital, and has many branches all across the world. Many city
kingdoms, trading corporations and wealthy private individuals make use of
house Ranian's services to finance, administer, or organise expensive
endeavours such as expeditions, war or large construction projects.

Over the course of many centuries the house has acquired a lot of wealth,
assets, as well as properties all across the world. Their combined wealth
eclipses many smaller city kingdoms, and they hold vast influence in many
bigger kingdoms and cities. Their main goal is the acquiring of wealth,
but openly and legally.

The bulk of House Ranians members and employees are bankers, financiers,
as well as negotiators it also operates guards and soldiers that protect
assets and the houses' banks. Even though not a clandestine operation,
the bank also hires rogues and spies for counter-espionage and to ensure
that their banks and facilities are secured against break ins and theft.
The House also employs wizards, scholars and historians that identify,
trade and deal with arcane and historical artefacts, as well as art.

Its main rival is the \nameref{sec:Ror-Aram Trading Corporation}, who often
vie over the same resources, properties and trade agreements. Although the
Ror-Aram Trading Corp. is mainly a trading business, it also operates its
own banking branch in direct competition with House Ranian.
