\section{Magistrata Arcanum}
\label{sec:Magistrata Arcanum}
\label{sec:Mages Guild}

The Magistrata Arcanum, or simply the ``Mage's Guild'' in common parlance, is
the official arcane institution of \nameref{sec:Forsby}. It was founded in
\emph{GT:1332}, by the noble family of Lorham.

It operates a large tower within the city's centre, and is responsible for
operating the city's dragon teleporter, investigating arcane occurrences,
registering and keeping track of any arcane wielders within the city, as well
as constructing arcane equipment for the city's military. It gives out arcane
licences to anyone who wishes to practice arcane magic within the city walls.
Before the devil siege, the magistrata was allowed to research into all sorts
of magic, including necromancy, summoning and research into ancient evil
artefacts.

The guild is ruled by a council of high mages, who elect one of theirs to be
the prime representative, called the Arch Mage. The magistrata, in its long
standing history and tradition, has trained many great wizards, scholars,
and arcane researches, including Arch Mage \nameref{sec:Graham Balance} who
was one of its finest Arch Mages from \emph{GT:2120} to his death in
\emph{GT:2148}.

With its long standing history, the magistrata prides itself in its traditions,
and its expertise in all things arcane. Its mages are highly respected, and well
educated. Most of the guilds students are children of nobles, rich merchants or
of families with a long standing history of producing capable mages and wizards.
Thus the magistrata often has a reputation for being plagued with elitism,
nepotism, but is generally considered the second best mage's guild, after the
hall of knowledge of \nameref{sec:Fes al-Bashir}.

The magistrata has lost a lot of power, influence and reputation after the
\nameref{sec:Devil Siege} of Forsby. Many other powerful institution, and most
of the population put the blame on the siege on the guild, even though they
refuted any accusations. The nobility of Forsby and the church of
\nameref{sec:Lor} put heavy restrictions on the guild's operations, severely
limiting in what kind of arcane magic they are allowed to practise.
