\section{Mist Reavers}
\label{sec:Mist Reavers}

The mist reavers (often simply called ``reavers''), are an all-vampire
fighting unit that rose to prominence during the early centuries of the
\nameref{sec:Strife}. They exist all over Aror, and primarily hunt and kill
monstrous humanoids, such as orcs, hobgoblins or goblins, and monstrous
creatures.

They gained their name by always attacking close to dawn, and often using
the mist of dawn as their cover. Mist reavers are highly trained warriors,
scouts, and elite shock troopers that organise themselves into small war
bands of just eight to twelve soldiers. Each individual soldier has been
a warrior for decades, if not centuries, and is thus an effective soldier,
and deadly warrior, skilled with a wide variety of weapons, and tactics.

Mist reavers have a long standing tradition, ancient rituals and only accept
other vampires (or those seeking to become vampires) into their ranks. They
swear to protect the core humanoid races, and must never raise their weapons
against a humanoid. Many swear their oath towards \nameref{sec:Marwaid},
\nameref{sec:Three Kings}, or towards the \nameref{sec:Order}, and
follow a strict monastic, warrior life-style throughout their tenure in the
reavers. Mist Reavers are free to organise their war bands as they wish,
and most reavers usually team up with those that share their philosophical
believes, chosen patron deity, or those that complement their own fighting
style. Reavers may leave their war band and their fighting life style behind,
but swear an oath to train a suitable replacement before they retire. A single
mist reaver is usually responsible for training one recruit, so each war band
usually consists of veterans and recruits in equal measure. The mist reavers
abhor the use of \nameref{sec:Ramesk}, and instead rely on feeding on
captured, and defeated monstrous humanoids to survive. They believe that
Ramesk makes vampires weak, and complacent.

Since mist reavers rely on speed, and surprise attacks in their attacks, they
rely on ``telescoping'' weapons, armaments that can fold into a compact
size. These telescoping weapons were forged by the ancient Deepkin clan
\nameref{sec:Aru'el}, and that craft has since been lost with the fall of
the ancient clans. Telescoping mist reaver weapons are priced possessions
for arcane smiths, highly valued trophies among the monstrous races, and
holy relics for the mist reavers.

While the mist reavers are welcomed, celebrated and highly decorated heroes
among the humanoid races, they are seen as butchers amongst the monstrous
races. Many mist reavers war bands slay entire monstrous villages, including
the weak and young, often launching preemptive strikes against monstrous
war camps, and cities. Still, many battles and wars during the strife would
not have been won without the mist reavers' help.

\begin{35e}{Mist Reavers}
  Mist Reavers adhere to a strictly organised life of training, fighting and
  prayer towards their chosen patron deity. Their deity must represent order,
  protection or war, and often Marwaid, the Order or one of the Three Kings is
  chosen by each individual reaver, or by an entire war band.

  Mist Reavers are thus always some degree of \emph{lawful}.
\end{35e}
