\section{Nightwatch}
\label{sec:Nightwatch}

The Nightwatch (often simply shortened to ``the watch'') is a monstrous
organisation that actively hunts and kills \hyperref[sec:Vampires]{vampires}.
They trace their origins back several thousand years, although they do not
keep an active history.

After \nameref{sec:Morana} had gifted the humanoid races the vampires as a
sort of special attack force against the monstrous races, many monstrous
tribes and villages formed a common defence to protect themselves from this
new threat. Many villages created a defence force including warriors, archers,
hunters, trackers and priests that would guard cities, towns, roads and
outlying farms from attack from the vampires. Although initially highly
localised and specific to a few initial tribes of orcs and hobgoblins, the
need for defence against this new supernatural threat became ever more
important.

It is unclear when exactly, as monstrous records are lacking, but around
GT:-7000 a few monstrous defence forces joined together to form the
\emph{``Nightwatch''}. Their creed, formally shared and pledged upon among all
members, states that they'd defend \emph{anyone} from vampire attacks. Whether
this includes protecting the core humanoid races from feral vampires is a
contentious issue that divides its members to this day. With a majority
stating that the core humanoid races do not deserve protection, or even
rescue, from their own folly. They will however, come to the aid of any
monstrous race, regardless of politics or past feuds against that race.

Members of the Nightwatch are often highly skilled warriors, trackers, hunters
but also priests of the \nameref{sec:Three Kings}, or \nameref{sec:Lor} of the
various monstrous races (such as bugbears, ogres, orcs, hobgoblins or even
trolls). The Nightwatch makes no distinction on whether the vampires are feral
or not, and will also not spare any obviously innocent vampire (such as those
recently turned by a bite of a feral). They follow a strict and militant
policy of eradication. While not technically undead hunters, they will also
destroy any other undead that are in close association with vampires (such as
ghouls or vampire spawns). The Watch is extremely knowledgeable and well
prepared to face the vampire threat, often having dedicated weaponry, spells,
and tactics in their arsenal to combat the threat.

The Nightwatch is highly regarded among many monstrous tribes, and joining the
Nightwatch as a vampire hunter is seen as a great honour in many monstrous
cultures. Members of the core races have been known to join as well, although
these instances are rare. The watch is also well received with those with
equally radical and militant opposition to the undead - such as the temples
and knights of \nameref{sec:Lor}. Many humanoid kingdoms oppose the watch,
especially the kingdom of \nameref{sec:Helmarnock} has declared the
organisation as an ``enemy of the state''.

\begin{35e}{Nightwatch}
  All in all the organisation is considered \emph{lawful neutral}, perhaps
  with slight leanings towards \emph{lawful evil}. They favour silver weapons,
  and their symbol is the crude shape of a four fingered silver hand, pointing
  downwards.
\end{35e}
