\section{Five Holy Orders}
\label{sec:Five Holy Orders}

Officially \emph{The Holy Churches of the Order Above Chaos}, are four closely
connected smaller orders, that all follow a common religious dogma that
worships the \nameref{sec:Order}. The five orders where founded together, some
time around GT:-3000, making them the oldest humanoid organisation on Aror.

The church was once composed of five holy orders, of which one has split off
into independence in \emph{MI:890}. The \emph{Fourth Order} is now known as
the \nameref{sec:Holy Church of Aleaste}.

\aren{At the time Graham wrote this part of the book, the split had not yet
  happened. So excuse the confusion within the article, regarding whether
  there are four or five holy orders.}

The banner of the five holy orders is a simple but petite dagger pointing
towards the ground, forming a cross. All anointed members receive a
\hyperref[sec:Dagger of the Order]{ceremonial dagger}, as well as a holy
symbol of the order. These items are used in ceremonies, for identification,
as well as holy focuses and symbols for divine spell casting.

The Five Holy Orders are staunch believers in a basic set of tenements, laws
and guidelines, and will fight and work for see them implemented, and upheld,
even if local laws would contradict. They are a fierce opponents of slavery,
indentured servitude, as well as defilement of the dead through necromancy, or
the corruption and manipulation of souls. They are not against sentient undead
as such, but will seek and destroy any corrupted, and evil undead.

\subsection{First Order}
\label{sec:First Order}

The first, and main order of the church, is responsible for keeping, maintaining
and teaching the main dogma of justice, law, and preaching the fight against
corruption and evil in all its many forms. It trains both clerics and priests,
as well as judges and negotiators that offer their services to anyone who
seeks their aid.

The Holy Orders believe that above all creatures and humanoid resides a bigger
structure of law and order. This order reigns absolute, and anyone who attempts
to place himself above it are doomed to fail or be corrupted into evil. It
further stipulates that this order is intrinsic to \emph{all} sentient
creatures, and that the five holy orders only help that true hierarchy of order
and law come forth within modern societies.

The first order is mainly known for providing experienced, well trained judges
and jurors to settle disputes, as well as offering their churches and
universities as neutral ground to settle disputes or to host diplomatic
meetings.

Those that join the First Order are granted training as clerics, priests,
judges, lawyers, diplomats as well as scholars on legal issues and
philosophy. And even though their word and judgement is held in high esteem by
many people, they are often in direct conflict with local laws and customs.

\begin{35e}{First Order}
  All in all the first order is seen as \emph{lawful good}, and its members
  are made up of clerics, bards (working as lawful diplomats), and rogues (as
  investigators and diplomats). Their favoured weapon is the warhammer, and
their domains are law, good, protection and healing.
\end{35e}

\subsection{Second Order}
\label{sec:Second Order}

The Second Order is responsible for keeping and maintaining the vast knowledge
the five orders have amassed over the centuries. They write and collect all
knowledge, dogma as well as the laws and rulings of the other orders, offering
them for all to read, learn and study. They are scholars, librarians,
explorers, archaeologists as well as practitioners of the arcane arts.

People that join the second order are often trained to be seekers of
knowledge, such as wandering priests, arcane scholars as well as those that
venture forth into ruins and foreign lands to seek new knowledge to add the
vast libraries the order maintains.

The libraries of the second order are open to anyone, and think that knowledge
will help anyone who is willing to help themselves. They are often in bitter
conflict with the \nameref{sec:Well of Truth}, and \nameref{sec:Aria}
followers in general, who seek to hide and hoard knowledge instead of
providing it to those that seek it.

\begin{35e}{Second Order}
  The Second Order is considered \emph{neutral}, and its members are often
  clerics, wizards, scholars, researchers, scientists and any that seek to
  collect and preserve knowledge. Their favoured weapon is the light pick,
  and their domains are knowledge, law, magic, and travel.
\end{35e}

\subsection{Third Order}
\label{sec:Third Order}

The Third Order is an order of knights, inquisitors and honourable warriors
that act as the executive branch of the five orders. They are sent to arrest,
imprison or even execute criminals, as well as defend the innocent, pilgrims
and priests, judges and scholars of the other orders.

As knighthood they only accept members of nobility as knights, but offer
inquisitor positions to anyone who succeeds a gruelling five year tutelage
under an already established inquisitor or knight. Those that join the third
order are trained to be jurors, investigators as well as fighters, warriors and
crusaders against injustice and corruption.

Knights and inquisitors of the third order are also often sent to deal with
supernatural threats or destroy evil creatures, such as corrupted undead,
werewolves, daemons, devils, fey or evil spell casters. Even though this is
not the main purpose of the Third Order, they are notoriously efficient in
eliminating those threats in combination with priests and holy men of the
First Order.

Highly unpopular within most city kingdoms, the inquisitors of the Third Order
enact their justice without the aid of the local law enforcement agency, and
often punish people whose actions are morally wrong, but still legal by local
law. Although the inquisition is known to side with those that are treated
unfairly, their popularity and support among the general population is
limited. Many see it as a bad omen or a sign of trouble when the Inquisition
appears to render justice.

\begin{35e}{Third Order}
  Even though the Third Order is considered \emph{lawful neutral}, there are
  some \emph{lawful evil} elements and members present within the order. Their
  favoured weapon is the heavy mace. The Order's members are mostly clerics,
  paladins (of all lawful alignments), knights, fighters, duskblades and
  eldritch knights as well as rogues that act as investigators. Their domains
  are war, strength, protection and law.
\end{35e}

\subsection{Fifth Order}
\label{sec:Fifth Order}

The fifth order is a monastic church, that believes that law and order can only
be brought forth by inner piece and calm. They often live secluded lives in
monasteries and temples, renounce any worldly pursuits and instead focus on
spiritual and fundamental issues through philosophy. Even though they train
their bodies physically in martial arts to achieve greater discipline, they
believe that violence is only justified if all other pursuits have failed.

Those that join the Fifth Order are devout students of philosophy, natural
sciences, but also of religious dogma and believes. They are often, diplomats,
philosophers and scholars, and widely respected as such all over Aror.

\begin{35e}{Fifth Order}
  The Fifth Order is considered \emph{lawful good}, and its favoured weapon is
  the unarmed strike. Its members are mostly paladins, and clerics, but they
  will accept anyone who seeks redemption and spiritual enlightenment through a
  monastic way of life. Their domains are law, good, knowledge and strength.
\end{35e}
