\subsection{Ror-Aram Trading Corporation}
\label{sec:Ror-Aram Trading Corporation}

The \emph{Ror-Aram Trading Corporation} is the largest trading corporation on
Aror, headquartered in \nameref{sec:Fes al-Bashir}. It's wealth surpasses
that of most baronies, and even smaller kingdoms, and it operates a vast fleet
of both war- and trade ships.

It's main responsibility is to export the goods produced within Fes al-Bashir
to the other city kingdoms, but also import the products from other regions
into the kingdom. The companies success has made Fes al-Bashir one the richest
kingdoms, in which a wide variety of luxury goods (such as furs, spices and
precious stones) are common even among the middle class society. The company
has offices is all major city kingdoms, and tends to hold good relations with
these kingdoms.

However the company is also known for its predatory and unethical business
tactics, especially where it faces weaker opponents such as small native
tribes that happen to be on land of natural riches, smaller trading
corporations or even smaller villages and towns. The company openly trades
with slaves, often with the \nameref{sec:Velvet Hand} or the
\nameref{sec:Hunters Guild}. Although the company has its own fleet of war
ships, mostly to protect ships against pirates, it has also financed
privateers and pirates in the past to attack and weaken competitors.

The trading company also operates a bank, and is a main financier of
adventurers, expeditions, as well as survey teams looking for ancient ruins,
artefacts, natural resources, or new land. It mostly employs merchants,
traders, guards, entire crews for both its war, trading and privateer vessels,
as well as all sorts of people for expeditions and surveys.

A company of immense wealth and power, it holds vast political influence
within Fes al-Bashir and beyond. It keeps that power with its immense
wealth, but also by unethical means such as black mailing, sabotage and
espionage.
