\section{Scions of Silence}
\label{sec:Scions of Silence}

The ``Scions of Silence'' (or often simply shortened to ``scions'') were the
military wing of the \nameref{sec:Gathering of Silence}, the church of the
\nameref{sec:Silent Queen}. As a militant and martial order, its members were
trained knights, fighters, warriors, scouts as well as assassins tasked to
protect the members and institutions of the gathering, as well as find,
capture and deal with its many enemies.

Unlike other militant orders the scions employed many mercenaries, paid by
the tithe that every member of the gathering had to pay towards the church.
The scions had very few official members, often just high ranking, and well
trained officers that oversaw the operations undertaken by hired swords. It
held excellent relations to many mercenary outfits, both big, and
small. Within days it could raise a formidable army to defend the Gathering's
many holy places, or bring the fight to the churches many enemies. It
recruited members, and officers out of the normal congregation of the
Gathering.

As many martial orders, it used a strict hierarchy of ranks to keep itself
organised, with the highest rank being that of the ``High Scion''. There were
always two high scions throughout most of the history of the order. One who
led the military arm, and oversaw conventional warfare, and one that lead the
order of assassins, and spies who oversaw unconventional warfare, and
espionage. Both sections of the scions followed a teaching of silence, which
meant that they must hold themselves to speak as little as possible about the
inner workings of the scions to outsiders. Many of the structures, members,
organisations, and places belonging to the scions were a tightly kept secret,
and the scions did everything in their power to ensure that these secrets were
kept.

The Scions were the main faction that fought for the Silent Queen in the
\nameref{sec:Holy Crusade}. It was also during that time that the scions were
at the peak of their power. Much like the rest of the gathering, the scions
were hunted down by the newly formed church of \nameref{sec:Aria}, after the
Silent Queen vanished. Many of its members, officers, and leaders left the
scions, and joined the private mercenary corps that they had previously hired
to fight in the war.

The order of assassins is the only remaining arm of the Scions of Silence.
Their continued existence is a fact among scholars, although it is
often merely a myth to the common folk of Aror. In common parlance the word
``Scion'' now almost excursively refers to the assassins that still carry on
the traditions of the Silent Queen. They buy young children who they could
mould to become killers through extensive and often lethal training, abuse,
torture, and brainwashing. Any prospective new member that survived their
training, would go on to participate in a blood ritual called ``the joining''.
Recruits would first swear the oath of silence, which demanded that they never
speak about any aspect of the scions with outsiders. Some recruits take this a
step further, and swear a complete oath of silence, upon which the ritual
master literally sews their mouths shut after the ritual has been
completed. Then they all drink from the blood of the ritual master, which had
been enchanted with psionic powers. The sip would cause about half of the
recruits to awaken to their latent psionic abilities. But before those select
few psionic recruits were allowed to join as full members, they had to kill
the remaining recruits that had not awoken. Thus all member of the
assassination sect of the Scions of Silence are psykers of varying degrees in
power. To finance their organisation after the fall of the gathering, the
scions now accept assassination and espionage contracts from third parties.
They still hunt followers of \nameref{sec:Aria}, and do so with ruthless and
deadly efficiency.

\aren{Of course the most militant, lunatic and fringe aspect of my religion
  survives, while all those wonderful libraries, studies and teachings were
  lost forever.
}

\begin{35e}{Scions of Silence}
  The old military wing of the scions of was considered \emph{lawful neutral}.

  The assassins were always, and are still \emph{neutral evil} in alignment.
\end{35e}
