\section{Silver Hand}
\label{sec:Silver Hand}

The \emph{Silver Hand}, a shadowy organisation found all around Aror, uses the
power of wealth to increase its influence all across the world. Their main goals
are to increase the individual wealth of its members, as well securing power,
influence and favours from powerful individuals to maintain their own standing
within society.

The organisation itself is secret, and so are its members. Only wealthy, and
powerful individuals are allowed to join, and must swear an oath to never
reveal or betray the organisation itself. Secrecy is upheld at all times, and
most of the times members do not know all other members of the society at any
given time. Members that join do swear to help each other, and to pool
resources against common threats and dangers.

The Silver Hand itself does not own any businesses, organisations or
influence, but their members do. Its members are often wealthy traders, crime
lords, or well connected politicians and nobles. Their members prefer to
operate covertly, plotting, stealing, spying and scheming in the background
over direct open involvement. Members of the organisation are very well
connected, and are capable of hiring any sort of service that would be
required to complete their objectives. They have connections to local
thieves', fighters' and assassins' guilds, as well as connections to corrupt
politicians and guards to remain in power. Members of the organisation meet
rarely, and always in complete secrecy. Often members arrive costumed or
disguised to avoid revealing their identities to others.

The organisation itself is centred around a select few individuals called
``beacons'' who know a limited subset of members called ``associates''. These
associates are often from the same kingdom or nation as the beacon. Beacons
also know one or two other beacons and can thus relay messages to other
branches of the silver hand. Messages, meetings, as well as combined
operations are organised through these beacons, who in turn relay these
messages and orders to their associates. This structure has allowed them
to compartmentalise their entire organisation, so that if one beacon or
associate is compromised the amount of information he could reveal is limited.
To get in contact with the Silver Hand, or to request aid from someone, a
member would contact his beacon, who in turn would further that request or
message throughout the organisation.

Individual members of the Silver Hand use the organisations power and
influence to eliminate competitors, gain unfair advantages in trade and
business, and avoid the repercussions and punishment of the law. The
organisation is known to spy, steal, murder and blackmail on all those
that might stand in its way.

Many members, and the organisation as a whole, is deeply connected to the
worship of \nameref{sec:Aria}, who sees the organisation as a logical
conclusion of her own teachings and dogmas.

\begin{35e}{Silver Hand}
  The organisation can be considered \emph{neutral evil}, and only accepts
  wealthy and powerful members.
\end{35e}
