\subsection{Knight Order of Tavos}
\label{sec:Knight Order of Tavos}

The \emph{Holy Knight Order of Tavos} is one of the oldest and most
prestigious knight orders and fighter guilds on Aror. They follow the
religious tenets laid down by a dwarven matriarch Sir Tavos of Renfeld, who
received instructions to form the knight order by \nameref{sec:Lord} himself.
The knight order is always lead by a patriarch or matriarch, who oversees the
entire order from their headquarter in \nameref{sec:Hraglund}.

Their banner is a stylised eagle, that spreads its wings downward toward the
ground, while a sun, representing Lor, rests overhead.

Although the knight order only accepts nobility as knights, they order demands
of them a monastic lifestyle. Members that join must forfeit their wealth and
earthly possessions, which are often donated to the poor and needy. The
Order's goals are to bring both law and Lor's light to its members, as well as
the world as a whole. Members must remain celibate, and follow a strict daily
routine meant to train their bodies, minds and will.

Knights and warriors of the Knight Order are also often tasked with protecting
the churches, priests, monasteries and pilgrims of Lor. As well as seeking out
and fighting creatures such as evil vampires, undead and daemons.

Members of the order are often paladins, knights, fighters, clerics as well as
rogues that wish to do good in the name of their patron god \nameref{sec:Lor}.
They can rely on a tight network of churches, monasteries as well as outposts
dedicated to their god for support. Knights of the Order of Tavos are well liked
and received with most populations of the city kingdoms.

However the Order was directly involved in the \nameref{sec:Religious Civil War}
in Norbury, which lead them from being exiled from the kingdom. They also fought
alongside the forces of \nameref{sec:Forsby} during the devil siege, which made
them ever more popular within that city.

By their very nature, and through the god they worship, they are often in
conflict with knights worshipping the \nameref{sec:Three Kings}, as well as
the two holy orders that follow the \hyperref[sec:Order]{Order}. They often
fight the former, while they are known to cooperate with the latter should
their goals align. Tavos' Order is also banned from \nameref{sec:Helmarnock}
for several incidents with the local vampire and umgeher population.

\begin{35e}{Knight Order of Tavos}
  The Order is considered \emph{lawful good}, and accepts knights, paladins,
  monks, fighters, rogues, clerics, duskblades as well as rangers. Their domains
  are strength, law, good and war.
\end{35e}
