\section{Two Courts}
\label{sec:Two Courts}

Aror has two organisations, two courts to be exact, whose sole purpose is to
deal with planetary wide threats and events. These two organisations are the
\emph{Court of the Moons} (often shortened to the ``moon court'') and the
\emph{Court of the Suns} (often shortened to the ``sun court'').

The Court of the Moons includes every major political figure of Aror, such as
kings, queens, powerful barons, representatives from various powerful
organisations such as the Ror-Aram Trading Guild, Velvet Hand, and House
Ranian.  The court meets frequently, often several times a year, in different
city kingdoms. Its main purpose is to coordinate the larger kingdoms and
organisations in times of crisis, but also to settle disputes and diplomatic
altercations. Wars between nations are brought before the court, and the peace
treaties that followed are also negotiated within the court. Large treaties
and accords, such as the \nameref{sec:Vonir Accord} were also negotiated
within the Court of the Moons, and the court is thus instrumental to keep and
maintain global peace.

The other court is called the ``Court of the Suns'', and is generally held in
\nameref{sec:Fes al-Bashir} albeit less frequently compared to the Court of
the Moons. Any member of the Court of the Moons is also automatically a member
of the Court of the Suns. Furthermore the court also includes particularly
powerful individuals, such as powerful wizards, priests, soul witches, leaders
of the various knight orders, powerful psykers, but also powerful criminal
elements that could potentially aid with a global crisis, such as pirate
kings, smugglers organisations, and various thief and assassin guilds. Members
of the court may vary depending on the topic the court wishes to address. The
main purpose of the Court of the Suns is to detect and repel planet wide
threats such as devil invasions, plagues, incursions of the scourge,
awakenings of ancient evils, nefarious gods or evil powerful individuals that
seek to bring harm to the world. Being appointed to the Court is an honour to
most, and also comes with certain benefits. Any member travelling to, or on
the behest of the court is granted immunity and often special diplomatic
powers. The court is generally regarded highly, and seen as a global effort
undertaking by the humanoid community to maintain peace, and the well being of
the entire planet.
