\section{Velvet Hand}
\label{sec:Velvet Hand}

The \emph{Velvet Hand} is a slaver organisation that oversees the majority of
the slave trade within the kingdom of \nameref{sec:Fes al-Bashir}. The
organisation's banner is the Fes al-Bashir half moons in velvet colours upon a
white flag. The Hand is always lead by one leader, and a regime of under
bosses and corporals.

They are responsible for claiming, registering and selling most of the slaves
within the kingdom, much like their Norbury counterpart the
\nameref{sec:Hunters Guild}. They often work closely together with the
\nameref{sec:Ror-Aram Trading Corporation} to sell, buy and hunt for their
goods outside of the kingdom.

Unlike the more sophisticated arcane tactics of Norbury, the Velvet Hand still
relies on branding behind the ears to mark slaves and their respective
owners. However do have copied the colour coding of slaves from the Hunter's
Guild in recent years.

The Velvet Hand is bound to the \nameref{sec:Vonir Accord}, and may thus not
enslave citizens of signing nations. Even though it is technically illegal,
they are known to break the accord regularly, and are thus notorious and even
feared all across the world of Aror. The Velvet hand also employs slavers that
actively seek new merchandise to sell back to the city. Their slavers often
roam the land with caravans, or the high seas with ships and prey on any they
perceive as potential new merchandise. This often brings them in direct
conflict with other city kingdoms or powerful organisations. The Hand manages
to stay out of these diplomatic incidents by allowing third party slavers act
without their knowledge and with plausible deniability.

The Velvet Hand often hires anyone willing to become slavers, and cares very
little on how their slaves are acquired. Velvet Hand slavers are notoriously
feared and despised all across the world, but the Hand remains a powerful,
rich and well connected organisation that is not easily unseated from their
place of power.

\begin{35e}{Velvet Hand}
  All in all the Velvet Hand is considered \emph{neutral evil}, and will hire
  any adventurer that is willing to do business with them. They operate like
  a criminal business venture, and are mostly interested in profit.
\end{35e}
