\section{Wayfaerer's Guild}
\label{sec:Wayfaerers Guild}

The Wayfaerer's Guild is the original hunting and adventurer guild that was
instrumental in founding of \nameref{sec:Hraglund}. Their members are prolific
hunters of all kind (such as warriors, rangers and wielders of magic), that
price themselves with being able to hunt and kill all wild and dangerous
beasts that may threaten civilisation.

The guild flies a green banner with a white shield, depicting a five headed
hydra. This is the same banner that is also used by the kingdom of Hraglund,
which sometimes causes confusions.

Members of the guild can be hired by anyone who need a dangerous beast or animal
taken down. It deploys many capable trackers, hunters, as well as fighters,
mages and scholars trained to defeat dangerous creatures such as undead, demons,
vampires, lycanthropes or even dragons. Although the guild itself is rather
small, and mostly centred around Hraglund and the outlying reaches, it can boast
with a century long tradition and track record.

Hunters of the guild may not hunt for sport, but instead must swear an oath to
only hunt and kill those creatures that would endanger others or the innocent.
Although they are allowed to hunt sentient creatures (such as evil undead, or
lycanthropes), they may not pursue sentient creatures without express permission
of the local law enforcement. The guild has a favourable reputation across all
of Aror, and are often called from remote corners to aid in the hunt of the
most dangerous of game.

The guild itself has several smaller outposts and save houses strewn across the
world for members to use, and will give any member the means to hunt and kill
whatever dangerous game they are after. It provides spell crafting services,
such as divination spells to track down prey, weapons, armours, healing, as well
as lore and knowledge on a variety of subjects. Hunters of the guild earn well,
and will have their families supported should they die during a hunt.

Although small, the guild earns well from the bounties it collects and the fees
it charges for its services. The nobility of \nameref{sec:Hraglund} also bestows
their patronage toward the guild, as an eternal thank you for their services
during the foundation of the city itself.

\begin{35e}{Wayfaerer's Guild}
  All in all the dogma of the Wayfaerer's guild should be considered
  \emph{chaotic good}. They accept anyone who has proven himself as a capable
  hunter and tracker, especially fighters, wizards, rangers, barbarians and
  rogues.
\end{35e}
