\section{Well of Truth}
\label{sec:Well of Truth}

The ``Well of Truth'' was an organisation first founded during the
\nameref{sec:Silent Queen}'s reign. Its main task was to acquire, collect,
study, and guard knowledge, arcane relics, and ancient secrets. It operated a
vast network of both hidden and public libraries. Scholars and scribes of the
well would collect books, artefacts, scrolls and magical devices, while spies
and agents would gather intelligence, secret information, and secrets and
would bring those to a library of the well. There it would be decided whether
the information was dangerous, and thus hidden from the public, or whether the
public was allowed access. Only members, or followers of the Queen had access
to the hidden, and secret libraries containing the forbidden tomes, and
artefacts.

During the great tragedy of the \nameref{sec:Holy Crusade}, the Well of Truth
split into two factions. The bigger, more sizeable part of the well joined
\nameref{sec:Aria}, while a few hidden libraries opted to remain firm in their
faith of the queen. These libraries are now mostly abandoned, lost forever, or
used as bases of operation by the hidden remnants of the \nameref{sec:Scions
  of Silence}. Many adventurers, scholars, and organisations make expeditions
to rediscover these libraries their life's work. Finding them would yield
great secrets, artefacts and magical powers.

Aria ordered all knowledge gathered by the agents of the well to be hidden
away in secret libraries. The public libraries were closed, and their
information moved to the secret installations, and underground vaults. This
of course brought the well of truth in direct conflict with many organisations
that seek knowledge for the betterment of humanity, such as the
\nameref{sec:Second Order}. Furthermore the organisation under Aria's rule is
known to steal information, research and artefacts from others, and even
murdering scientists, witches, warlocks and scholars that dabble in research
that are deemed to dangerous, including \hyperref[sec:Soul Magic]{soul magic},
and \hyperref[sec:Rune Magic]{rune magic}.


\begin{35e}{Well of Truth}
  While originally \emph{lawful neutral} under the Silent Queen, the
  organisation has shifted to \emph{lawful evil} under Aria's guidance.
\end{35e}
