\ifimages
\clearpage
\incgraph[
  overlay={\node[black] at ([xshift=0cm,yshift=-1cm] page.north)
    (main)[text width=0.9\paperwidth]{
      \large \centering
      \textbf{``Baphomet and his most trusted general \nameref{sec:Beleth}''}
    };
  }
]{media/baphomet.\imagesuffix}
\clearpage
\fi

\subsection{Baphomet}
\label{sec:Baphomet}

The supreme ruler of the \hyperref[sec:Devils]{devils} in the layers of hell
is a powerful psyker called Baphomet. With the head of a goat, the upper torso
of a female humanoid, and the lower torso of a male humanoid she is one of the
\hyperref[sec:Scourge]{scourge}'s more unique creations. She rules her realm
from the last layer, called the sanctuary, and spends most her time mediating
the businesses of her realm.

Baphomet is extremely intelligent, and an exceptionally powerful psyker. Many
believe that his power is only second to the \nameref{sec:Scourge} itself. The
dogma of the church of Baphomet state that the early years of the layers were
of chaos, fear, and tumult. The devils were afraid that of the scourge's many
attempts to invade their home to enslave its wayward children once more. The
layers had no structure, no order, and devil fought devil in an attempt assert
dominance, and to gain power over the newly formed nation. Within this chaos
Baphomet simply sat down on the floor, and began to meditate. In its
meditative trance Baphomet used its psionic powers to warn the devils of
impending scourge incursions, and telepathically coordinated the devil's
defences. Baphomet brought order, structure, and above all, security and
stability to the layers.

While not a traditional deity like \nameref{sec:Aria} or \nameref{sec:Lor},
Baphomet is the figurehead of religious cults both within, and outside of the
layers. These cults worship her, either as the supreme ruler of hell, or as
a saviour from the scourge's influence. For many people on Aror she is either
a symbol of tyrannical rule as an opposite of Lor, or the the beacon of
rebellion against spiritual and mental enslavement. Her cults are more
numerous in the layers, but a few dedicated cults also exist on Aror. These
cults are often psykers thankful for the psionic beacon, or immigrant devils
that brought their religion to Aror.

\graham{Her name is often simply taken in vain as a curse.
 `by Baphomet's beard` is my favourite one.}

Baphomet is responsible for projecting a psionic "beacon" or "signal"
across the noosphere of the multiverse. This signal takes the form of a
hellish clock with a pendulum that swings in a 4/4 metre at about 100 beats
per minute. Each swing is accompanied by a psionic "tic", and every fourth
swing makes a psionic "tac". Psykers can use the beacon's steady metre as
anchor to drown out the Scourge's ever present influence. Psionic powers can
be aligned to his beacon, allowing psykers to hide their presence from
the Scourge.

Baphomet does not grant divine favour directly, and never acknowledges her
cults, and rarely speaks to her followers. Her right hand
\nameref{sec:Beleth} directs and instructs these cults instead, and also
grants these cults divine favour in Baphomet's name.

\begin{35e}{Baphomet}
  Baphomet is considered \emph{lawful evil}, and \nameref{sec:Beleth} grants
  divine power in his name. Their domains are knowledge, evil, law and
  strength.
\end{35e}
