\subsection{Forneus}
\label{sec:Forneus}

Forneus is the name given to an otherwise unnamed, extraordinarily powerful
devil from the hellish planar realms. He is often often worshipped as the god
of magic, arcane craftsmanship, and the study of languages and forgotten texts.

His followers are often wizards, scholars of the arcane arts, as well as those
who wish to craft arcane weaponry, artefacts and machinery. He often strikes
deals with mortals through his minions, and in exchange for powerful magical
artefacts he offers arcane, and spell casting services. He also sponsors arcane
research, and provides aid and knowledge to further it, and will often ask for
a copy of the results of this research in return.

He is often depicted as a huge winged arch-duke of hell, but in reality he
rarely leaves his domain, preferring to send minions (often erinyes) to strike
deals. He, and his followers, pride themselves in making fair deals, but will
often punish those that break these deals. An example would be
\hyperref[sec:Medusa]{Medusa}, who were female wizards cursed by Forneus for
betraying him in the past.

Even though many other religions, such as \nameref{sec:Lor}, consider him evil
very few of his minions are considered evil. He does not tempt them to do
evil, and more often than not simply seeks to gain magical artefacts in
exchange for spells, arcane knowledge and arcane services. His followers openly
embrace all forms of magic, including necromancy, which often brings them in
conflict with other religions and deities.

\begin{35e}{Forneus}
  Forneus himself is \emph{lawful evil}, but he accepts anyone as a follower
  that seeks to simply improve their own magical powers and prowess. His
  followers may be of alignment. His favoured weapon is the dagger, and his
  domains are arcane, knowledge, travel and fire.
\end{35e}
