\subsection{Griannar}
\label{sec:Griannar}

\emph{Griannar} was once the lesser deity of light, piety, forgiveness and
repentance, until he was killed by the \nameref{sec:Silent Queen} in
\emph{MI:0}. He was often portrayed as a sunbeam, or as the two suns rising on
the horizon.

\subsubsection{History}

Worship of Griannar stretched back thousands of years, and before his death,
the \emph{Holy Church of His Divine Light} was the dominant religion in most
of the human city kingdoms. His \emph{Holy Church} was the most powerful
institution on \hyperref[sec:Aror]{Aror}, and at its peak, counted tens of
millions of followers. A major source for morality and fundamental values in
most humanoid kingdoms and baronies, the church held vast and unparalleled
influence, and political power. The \emph{Holy Knights of His Divine Light},
the churches military wing, could also rival many armies in terms of manpower,
training and equipment.

\subsubsection{Holy Crusade}
\label{sec:Holy Crusade}

Griannar was always an open rival of the \nameref{sec:Silent Queen}. This
rivalry existed over centuries, and lead to the occasional skirmishes, violent
disputes, and armed clashes between the two religions and their
followers. Over the years the power of the Holy Church grew, and began to
entrench itself deeply in the political landscape of the major city
kingdoms. Since it openly tried to enforce a policy of zero tolerance against
corruption, impurity, debauchery, evil and the undead (regardless on whether
they were evil or not), many noble houses began to secretly support the
followers of the Silent Queen.

The Queen's followers, who where often rich thieves, smugglers, corrupt barons
and nobles, began to fund mercenaries and assassins, to drive the followers of
Griannar of their land, or to assassinate powerful priests and bishops of the
Holy Church. The church retaliated by sending her knights to defend churches,
pilgrims and protect the bishops. As the open engagements between the Queen's
mercenaries and the knights became frequent, more and more noble houses, who
saw the Church as a threat to their power, began funding the Queen's war
campaign.

In \emph{GT:18030} the holy church openly called for a \emph{Holy Crusade}
against the evil that is the Silent Queen and her followers. The declaration
was met by a rival declaration by the \nameref{sec:House deVar}, who openly
supported the Silent Queen in the crusade. This plunged \nameref{sec:Helmarnock}
into war against other city nations that openly supported Griannar, including
\nameref{sec:Hraglund} and \nameref{sec:Forsby}.

The Holy Crusade lasted for almost twenty years, and reached its conclusion
at the decisive siege of \nameref{sec:Hraglund} in \emph{GT:18040}. The
siege lasted three years, and finally ended when the archbishop of Griannar
tried to flee the city in secret. He was betrayed by the nobles of the city,
and delivered to be executed by the high priestess \nameref{sec:Aria} of the
Silent Queen.

\subsubsection{Death}

Scholars still debate Griannar's death to this day, but in \emph{MI:0}, all
priests of Griannar lost their divine power, and their prayers went
unanswered. Alongside him, his rival the \nameref{sec:Silent Queen} disappeared
(or died) as well, giving rise to a new religion surrounding the high priestess
\nameref{sec:Aria}.

\subsubsection{Legacy}

Over the course of many decades the Holy Church of His Divine Light slowly
lost influence and power, until it slid into obscurity. Ruined temples and
churches of the church can still be found all over the world, while the major
sites of worships within the city kingdoms were either demolished or have been
taken over by other faiths.

The death of such a major deity was a major event, and the scholars of
\nameref{sec:Fes al-Bashir} tried for a long time to understand the
intricacies of such a world shattering event. The sad occasion was
immortalised in the dawn of the new aeon of \emph{Midaris} that began with
year zero in the year of Griannar's death.

\begin{35e}{Griannar}
  Griannar was considered lawful-good, his favoured weapon was the longsword.
  Griannar is considered dead, and his followers and priests no longer receive
  divine power.
\end{35e}
