\subsection{Isamir}
\label{sec:Isamir}

\emph{Isamir} is a lesser deity who claims sovereignty over the sea, sea
creatures, storms, rains and the weather. He is often portrayed as a deep
sea dragon that waits and lurks beneath the surface.

\subsubsection{Inua}

The \nameref{sec:Inua} worship him as their patron deity, and it is from
them that he became known to the wider world. The Inua see him as malevolent
deep sea creature that must be appeased with prayer and sacrifice, otherwise
he sends storms and thunder in retaliation. He grants power to those that
worship him, and is said to conjure storms and against those that displease
him.

He preaches respect against the sea, its creatures, and that you should not
defile or pollute his seas, lakes or rivers. His followers should never take
more from the waters than they require, and must not allow buildings that
alter lakes and rivers, such as damns.

Isamir openly encourages the tribes of the Inua to raid and attack foreigners,
as well as their own tribes that stray from the path that he has laid out for
them. Ever since the other city kingdoms have come to the
\nameref{sec:Silver Isles} his worship is threatened by the other religions
of Aror. He especially takes a great dislike against any tribe that would
worship \nameref{sec:Forun}.

The Inua are the only people who build large temples, shrines and places of
worship in his name. These are often hidden deep in the jungles of the
\nameref{sec:Silver Isles}.

\subsubsection{Sailors}

Isamir is also a popular deity to sailors, who pray to him for safe passage
over the sea, lakes and rivers. Sailors that follow Isamir often sacrifice
to him, by throwing provisions or even money overboard to feed the beast
that sleeps beneath the surface. Like with the Inua, he demands that his
lakes, rivers and the sea are respected, and demands that they be not
polluted or even destroyed by damns and diversions.

\subsubsection{Relations}

He openly denounces anyone who would destroy, damage or overfish lakes,
rivers and the sea. And he is a fierce opponent of anyone who follows
\nameref{sec:Forun}.

\begin{35e}{Isamir}
  Isamir is considered \emph{chaotic neutral} or \emph{neutral evil},
  and his favoured weapon is the long spear. His domains are water,
  strength, war and chaos.
\end{35e}
