\subsection{Lilith}
\label{sec:Lilith}

Lilith is one of the generals of the \hyperref[sec:Devils]{devils}, and is
thus also worshipped on Aror as a goddess. She is the goddess of sex, lust,
debauchery, and hedonism. She is there often called the \emph{scarlet whore},
as she encourages people to thrown in promiscuous, lavish endeavours.

She has no official churches, or even dogma, but she is revered among the
wealthy that can frown in all sorts of excesses, those of sexual perversions
but also among sex workers and those sold to sexual slavery. Lilith's followers
indulge in food and sexual orgies, and follow their short-sighted pleasures
and indulgences to wherever they might take them. Lilith's followers range
from harmless but sexually curious, to the downtrodden and exploited sexual
workers and slave, to deranged and perverted. Since the few spoil the apple
basket, and the nature of the deity, most worship of Lilith happens in secret.

Since she has no dogma, no official rules or code to follow, she sends succubi
and incubi to her followers to hand out instructions, demands, as well as
answer prayers and grant gifts. Lilith is known to tempt powerful mortals to
fall for her ways, using her incubi and succubus as tools of temptation. Lilith
uses those debaucheries then also to leverage power and influence among powerful
and wealthy mortals.

\begin{35e}{Lilith}
  Lilith herself is \emph{lawful evil}, but she welcomes anyone to her religion
  that prefers indulgence over restraint. From the neutral good sex worker just
  trying to make a living, to the chaotic neutral gigolo that just lives for
  pleasures.

  Her domains are Passion, Charm, Evil and Trickery.
\end{35e}
