\subsection{Lor}
\label{sec:Lor}

Lor is a lesser deity of justice, law, discipline, good and the fight against
all evil. He is often depicted as an angelic humanoid creature that kneels
down with his two handed sword buried in the soil.

\subsubsection{History}

He is among the older lesser deities of Aror, and was always in direct
conflict with evil elements of the world. His worship is well established
all across the world, and many welcome his knights and paladins as a means
to establish law and order, as well as a way to fight evils, such as
daemons and undead.

\subsubsection{Dogma}

The followers of Lor have one prevailing Dogma, which is strictly controlled
by the Church of Lor. The church, and its leader the reigning patriarch or
matriarch, reside in the city kingdom of \emph{Hraglund}. The church preaches
austerity, monogamy and a strict life that rewards those that help the weak
and wounded. Daily prayers are required, as well as weekly attendance to
masses. The priests of Lor often guide a community of followers either alone,
or with an adept they teach. The followers of Lor are meant to seek out and
destroy evil, even the evil that resides within themselves. He instructs his
followers to repent for their signs and purge evil within them through
flagellation, as well as help and aid others to atone for their signs.

To the followers of Lor undead, devils and fey are evil, and wicked. And Lor
openly encourages seeking out and destroying such evils.

Most followers that dedicate themselves to Lor become priests, knights,
paladins or monks. Lor values dedication, hard work as well as spiritual
strength and resolve.

\subsubsection{Knight Order of Tavos}
\label{sec:Knight Order of Tavos}

The Order of Tavos is a holy knight order of Lor that is under direct control
of the patriarch or matriarch. Only members of nobility are allowed to join as
knights, while any can join as priests or as adepts. To the order virtue,
sacrifice and personal honour are as important as are devotion to Lor and the
Knight Order. The Knight Order never fights wars directly, but is instead
charged with securing and protecting the churches and followers of Lor from
threats, as well as seeking out and destroying evil creatures.

Tavos was the patriarch that established the order in \emph{GT:1632} and was
known as a divine and holy man whose virtue is a example to any that join
the Order or follow Lor.

\subsubsection{Holy Order of Sir Ceartas}
\label{sec:Holy Order of Sir Ceartas}

The Holy Order of Sir Ceartas is a monastic order. They live mostly in
reclusive temples and monasteries in austerity and poverty. They must not
accumulate wealth, give what they earn to the needy and poor, and must fight
evil anywhere they encounter. Often the Holy Order sends forth their pupils to
learn and experience the wide world, and fight evil to defend the
weak. Knights and priests are often sent alongside a more experienced member
of the order, so the master may teach the pupil. Members of the Holy Order
must remain celibate. Much like the Knight Order of Tavos, they are not
allowed to interfere with local laws, and may not join wars.

Sir Ceartas was a knight that was sickened up with the wealth that the church
had amassed, and thought that mingling with the local governments to vie for
power was a despicable and an act unworthy of Lor. Instead he founded his own
monastic order that barred people from acquiring wealth, and teaches them to
focus on the important dogmas of Lor: helping the weak and fighting evil.

\subsubsection{Relations}

Lor is in direct conflict with pretty much all major evil or neutral gods and
religions, especially with \emph{Three Kings}, the \emph{Order}, as well as
the three other major gods \emph{Forun}, \emph{Nyddwr} and \emph{Marwaid}. Lor
sees these as heretic and archaic forms of worship, if not outright evil.

\begin{35e}{Lor}
  Lor is considered Lawful Neutral, and he is the patron of knights, paladins,
  and monks and anyone who seeks to destroy evil. His favoured weapon is the
  two handed sword.
\end{35e}
