\subsection{Old Ways}
\label{sec:Old Ways}

The \emph{Old Ways} are not a god or deity, but instead a set of believes,
traditions, and stories that represent how the ancient humanoids worshipped
the three major deities of Aror. A few minor deities also appear in this
religion, such as \nameref{sec:Morana}.

\subsubsection{Three Mothers}
\label{sec:Three Mothers}

The core of the religion are three female deities that are worshipped as the
\emph{three mothers} of all humanoid races. Each of them represents one stage
of a woman's development. \nameref{sec:Forun} represents the young, hopeful,
and beautiful woman that raises her children with warmth, compassion and
love. She represents youth, beauty, fire and fertility. \nameref{sec:Marwaid}
represents the ageing mother, that has lost children, and sacrificed
everything that she has for her young. She is seen as the hardened, stern and
often embittered woman that raises her children to withstand the harsh
realities of life. \nameref{sec:Marwaid} also represents the strong fighter
within each person, that would fight to the bitter end to protect their
children and family. \nameref{sec:Nyddwr} represents the old woman, the crone,
that offers her immense wisdom to aid her already fully grown children and
family. She represents the tempered, wise, yet hardy old woman that survived
against all odds, and now shares her wisdom with others.

For a while there was a fourth mother, \nameref{sec:Morana}, who stood for the
dead mother, that still protect their children from beyond the afterlife.
After it was revealed that Morana had gained her status among the true deities
through lies and deception, she was cast from her role as one of the main
mothers. She is now vilified in the stories of the Old Ways, as the
\emph{great betrayer}.

\subsubsection{Stories}

Another important part of the Old Ways are how the knowledge, values propagate
and continue to live on: stories. A collection of mystic stories, parables,
and myths that are passed orally from one generation to the other. They often
have several purposes, but most stories are told to children to explain to
them the dangers, beauties, challenges, intricacies, but also the horrors of
the world. The collection of all these stories and myths is called the
\emph{old prose}.

The stories also contain heroic accounts of heroes of old. Bold tales about
people that ventured forth to slay beasts, save the innocent, become kings, or
return a powerful magical artefact back to save the village from certain doom.
But the stories also contain horror stories that end badly, such as the new
mother that goes to the woods only to be eaten by a werewolf.

The most important part of these stories however is to teach the core values
of the ``old ways''. The most important being dedication, loyalty and honour
to your own clan or tribe. Each member of a clan should give what he can, and
take as little as he requires. This not only extends to love, life, family but
also to nature, with which every follower of the Old Ways must strive to
respect.

Some of these stories also tell of failings, crimes, and their appropriate
punishment. While most of these stories tell of compassion for minor offences,
they lay out brutal punishments for serious crimes and even include the death
penalty or slavery for severe crimes such as murder or rape. The same stories
also tell of just rulers, their heroic behaviour and their favourable
personality that made them beloved by their followers.

However these old stories also lay down a strict social construct that often
portraits women as responsible for the household and family, while the man is
supposed to hunt, fight and protect. These structures are then reinforced by
heroic hero stories - who are more often than not - male, and by the stories
of the three mothers whose motherly attributes serve as role models for women.
While heroines, and thus precedent for a balanced and fair society exist - such
as the great huntress \nameref{sec:Eigyr} that slew more beasts than she could
eat, or the powerful witch \nameref{sec:Gweneth} that saved her village from a
terrible plague - many tribes that follow the old ways still see the woman's
place with the family.

\subsubsection{Incantations}

The Old Ways do not have priests, but witches and shamans as spiritual
leaders. Also the ``old prose'' contains incantations that may be cast by
anyone versed well enough in the old stories and ancient Teranim. These
incantations are often soul or divine magic, and quite powerful. However they
often require hours of preparations, several people performing the incantation
together, complicated chants and songs in ancient Teranim, and sometimes even
live sacrifices to the three mothers to succeed. Practising witches and
witchers of the old ways are often the spiritual centre of a clan or
community, and tasked with gathering, teaching and performing these old
incantations when required.
