\subsection*{Runemaster}

The \emph{Runemaster} is an unnamed, extraordinarily powerful devil from the
hellish planar realms, that entices mortals with promises of great power and
knowledge in exchange for sacrifices.

\subsubsection*{Dogma}

The \emph{Runemaster} has no church or concrete following, but his minions can
be summoned through arcane means and will strike deals with mortals. In these
dealings his followers often accept living humanoid sacrifices, powerful
artefacts, or knowledge in exchange for arcane knowledge and power.

\subsubsection*{Runes}

He gained his name from offering a special variant of arcane magic to those
that summon his followers: \emph{rune magic}. With this technique he enables
those that cannot cast magic themselves an easy way to inscribe powerful
arcane runes into the flesh and skin of their own bodies. The magic
incantations to inscribe these runes often require gruesome ingredients, such
as body parts of animals or even humanoids to cast. Although the runes of
lower power require just animal organs, the ingredients become more gruesome as
they grow in power; ultimately peaking at ritual humanoid sacrifice in the
name of the Runemaster.

Most that practise rune magic stop at the lower tiers, never going beyond what
society or standing laws would allow them to acquire in terms of
ingredients. Some however are corrupted by the lust for power, are desperate
or perhaps morally challenged to begin with, and then proceed to fulfil the
Runemaster's ultimate goal: humanoid sacrifices in his name.

\subsubsection*{Runic Lexicon}

He sometimes chooses one of his most loyal follower to write a book about how
to craft these runes, which is simply called the \emph{Runic Lexicon}, in the
hope that this spreads his influence among the mortal races. These books are
priced artefacts, as very few of these actually exist at any given time. Many
are destroyed by the various enemies of the \emph{Runemaster}, and those that
do exist are often shared and traded in secrecy.

\subsubsection*{Relations}

The \emph{Runemaster} is in direct conflict with most good deities that seek
to reign in his powers, and wish to stop his followers from becoming so corrupt
that they'd perform humanoid sacrifice. His enemies include \emph{Forun},
\emph{Lor}, \emph{Order} but especially \emph{Aria}, as she sees everything he
does as an affront to her teachings.

\begin{35e}
  The \emph{Runemaster} is, as most of the devils, \emph{lawful evil} and his
  favoured weapon is a ritual knife (a dagger) that is used to inscribe the
  runes.

  Rune magic is described later in this book.
\end{35e}
