\subsection{Silent Queen}
\label{sec:Silent Queen}

The \emph{Silent Queen} was a powerful lesser deity of the night, shadows,
theft, magic and subterfuge, until she was killed by her high priestess
\nameref{sec:Aria} in \emph{MI:4}. She was often depicted as a hooded woman,
who had her mouth sewn shut.

She was once the patron of all people that worked in the shadows, such as
thieves, spies, smugglers and assassins, but also those that sought knowledge,
as well as those that practised forbidden arcane arts in secret, such as
necromancers or conjurers of devils. She did find a few large congregations
among the ancient \hyperref[sec:Dark Elves]{dark elves} and
\hyperref[sec:Deepkin]{deepkin}.

As the goddess of night, she was always the opposite of \nameref{sec:Griannar},
and the two religions often clashed in violent disputes and skirmishes. These
clashes escalated to a full fledged war, which the followers of Griannar simply
called the \nameref{sec:Holy Crusade}. Although the queen emerged victorious
from the war, she was ultimately slain and usurped by her then high priestess

Although knowledge of her existence is widespread among scholars, she has
drifted into obscurity amidst the general populace. Most of her rites,
teachings and knowledge are all but lost. Depictions of her are still prevalent
in the deep, were the ancient dark elves erected statues in her honour. Although
the followers of Aria were diligent in their erasure of the Queen's history,
they have not yet erased everything, nor killed all of her remaining followers.

\graham{I shall let you know that my co-author is a devout follower of the
  Queen, and some biases might thus be present within the book.}

\subsubsection{Gathering of Silence}
\label{sec:Gathering of Silence}

The ``Gathering in Silence'' was the informal head-council of the church, in
which all high ranking members of the various aspects of the queen would come
together to elect a high priestess. This priestess then lead the followers,
and would ensure that the various organisations within the faith, such as the
\nameref{sec:Well of Truth} or the \nameref{sec:Scions of Silence} would work
together. The gathering was also responsible for collecting a tithe, or tax,
from its member, and distribute the money to fund the churches many
endeavours.

\begin{35e}{Silent Queen}
  She was considered \emph{neutral evil}, but since her death, her followers
  and priests no longer receive divine power.
\end{35e}
