\subsection{Well}
\label{sec:Well}

The well (draconic: ``jinto'', giant: ``fusra'') is an ancient symbolic
narrative, which embeds the gods, the world, and its creations within a
framework of creation, and destruction.

The concept of the well, its waters and darkness are well known within the
lore of the dragons, the giants, monstrous races, and the humanoid races of
Aror.  Some scholars say that the myth of the well originated from the
dragons, others claim that its appearance among all races gives it credibility
as a true representation of creation.

\begin{displayquote}
  ``1: At the darkest depths of the WELL the waters ebb and rise. 2: Yet in the
  motion of receding it gave chance for the void to birth its first children. 3:
  These children shape the void of the WELL with thoughts of love and hatred. 4:
  It is them, and their creations, that were, are, and will be; for their lives
  rest beneath the ebb and the flood.'' WELL 1-4
\end{displayquote}

The myth postulates that the ever flowing waters of the well receded, giving
chance for low entropy to birth creation. The remaining water aided in the
nourishment of this creation, but the flood threatens to return, dissolving
the creation in the heat death of the universe.

Many cultures contain worship of the well, its waters, as the true deity of
entropy, and final decay. The myth of the well is also the basis, in spirit,
principle, and shape, of the \nameref{sec:Soul Well}. Scholars strongly agree
that the well of souls is not the same as the well, and it was merely inspired
by it in its creation.

The well is also seen as the gods, amongst gods, for none may escape the march
towards the ultimate decay:

\begin{displayquote}
  ``25: You might be above the sea, the grass, the mountain, and even the bird;
  but the depths of the WELL are your firmament. 26: For the water of the WELL
  nourished and cradled you, when there was nothing but darkness in its
  depths.'' WELL 25-26
\end{displayquote}

Like any true deity, the well can be worshipped, and will grant divine power as
the representation of entropy, and decay.

\begin{35e}{Well}
  The Well is considered \emph{neutral}. It favours none, and hastens the end of
  all. It has no favoured weapon, and no domains are associated with it.
\end{35e}
