\subsection{Helmarnock}
\label{sec:Helmarnock}

The city kingdom of \emph{Helmarnock} (ancient Teranim for ``land of the
people called Helm'') lies on the south-eastern edge of \emph{Eilean Mor}. It
is unique as the kingdom is resides on four islands as well as the eastern
shore, which were once ruled by separate five baronies that joined together
into one kingdom.

\subsubsection*{Geography}

Helmarnock lies spread out on four different islands off the south eastern
shore of \emph{Eilean Mor}. The islands are joined together by four huge
stone bridges, that converge in a crossroad in the middle of the sea between
the islands. The kingdom also owns land on the shores of \emph{Eilean Mor}.
The northern island is called \emph{Temen}, the eastern island \emph{Thorm},
the southern island \emph{Eledis} and the western island is called
\emph{Saremen}.

All of the islands are covered with city, and the islands are surrounded by
huge harbours and ports. The land on the shore is mainly used as farmland as
the huge stream \emph{Dunast} makes the land fertile for crops.

\subsubsection*{History}

The city kingdom was founded in \emph{GT:984} when the four baronies that
ruled the islands and the shore joined together to form one big city kingdom.
The rulers of these baronies all intermarried and created a new noble family
called house \emph{Helm}. The islands were joined with bridges and a small
public forum was built in the centre of this island from which the king could
rule. However in \emph{GT:1588} the noble family ended up without an heir and
the throne became vacant.

For two hundred years the five noble families fought between each over the
throne. Although the conflict never escalated into full civil war, the houses
raided each other, abducted and assassinated important members of other
houses, as well as sabotaged companies and production facilities. These two
hundred years are now known as the \emph{bloody years}, and it deeply
entrenched itself within the population, splitting them into five major
factions. The deep trenches that divided the people of these islands then can
still be felt after thousands of years since the conflict.

Finally in \emph{GT:1601} the dispute was settled. The noble houses decided
to not elect a new ruler, but instead rule the kingdom as a council of family
leaders. The resulting government is called the \emph{high council} and rules
the city absolute. But stability and security returned slowly to the city
kingdom over the course of many decades.

In \emph{GT:3401} the city kingdom was dragged into the
\nameref{sec:Holy Crusade} by the vampire noble house \emph{de\'Var} who openly
rallied against the Holy Church of \nameref{sec:Griannar}. The other noble
houses followed the war declaration as the united \emph{kingdom of
  Helmarnock}. Although it cost the kingdom many lives, it was ultimately a
victory and a source of national pride, that united the divided spirits under
the banner of one greater kingdom.

\subsubsection*{Culture}

\graham{Their reputation is undeserved. For the most part.}

The citizen of Helmarnock are known to still harbour resentment for each other,
and are mostly patriotic towards their own noble family. Years of underhanded
and illegal dealings, corruption within the city guard and armies have given
the people of Helmarnock a reputation for cutting corners, being sleazy,
lacking in morals or being outright criminals. Although this does not hold
true for the vast amount of the working population; the climate of harsh
competition between the islands tends to promote ruthless and underhanded
business tactics amongst the nobility and upper class citizens.

Even though most people still divide themselves into five distinct cultures
aligned with the five noble houses, the high council is working towards
uniting the kingdom not only in government, but also in culture. The people
are encouraged to move between the islands, are encouraged to see themselves
as citizens of \emph{Helmarnock} instead of the old baronies, and often organise
events such as festivities, plays, concerts and trade festivals in the central
forum in an attempt to unite the kingdom.

\subsubsection*{House Eseriel of Tenem}
\label{sec:House Eseriel}

The northern island of Tenem is ruled by the dark elven noble House of
\emph{Eseriel}. Their banner is a red dragon upon a white background. White
and red are the main colours of the house. They operate a large shipping
enterprise and are mostly responsible for imports and exports of the
kingdom. Being natural traders and business men, House \emph{Eseriel} is the
richest among the noble houses. Members of the house are known as excellent
and reliable business partners, and often fund expensive undertakings such
as expeditions into unknown realms, large construction projects or arcane
or scientific research projects.

\subsubsection*{House Onariel of Thorm}
\label{sec:House Onariel}

To the east reigns the high elven noble house of \emph{Onariel}. Their main
business is information and espionage, as well as offering counter espionage
to the entire kingdom. Their are infamous and notorious for their criminal
activities, such as smuggling, drug trafficking, espionage and oppression
of enemies of the kingdom. The bad reputation the kingdom and its citizen
have, mostly stems from various scandals that have been uncovered in which
House Onariel was involved. The house is known world wide as one of the most
effective spy organisation, that has agents and informants spread all across
the world.

Their banner is a side view of dark green owlbear in a white shield, atop of
which rests a silver crown. White and green are main colours of the house.

\subsubsection*{House Kelemor of Eledis}
\label{sec:House Kelemor}

To the south rule the dwarven noble family of \emph{Kelemor}. They once
hailed from the great divide, but made their riches by building most of
the city's buildings and bridges. They operate most of the smithies and
artisan guilds of the kingdom, and often work together with House
\emph{Eseriel} to export their manufactured goods to other kingdoms.
They also provide the equipment to the joint army of Helmarnock. Kelemor
are often the first to call out other houses for breaking the peace or
for attempting to sabotage the finely tuned political machinery that
is the high council. Although Kelemor is a voice for order and piece within
the kingdom, they are also the fiercest proponent for continuing slavery
within the kingdom.

The house's banner is an upside down golden hammer resting on a white
background. White and gold are the main colours of their house, and their
emblem can be found on my armours, weapons they have produced and buildings
they have built throughout the kingdom.

\subsubsection*{House de\'Var of Saremen}
\label{sec:House deVar}

The western island is ruled by the House of \emph{de\'Var}, whose mainstay
members are vampires made up from various races of \emph{Aror}. Even though
vampires generally pose a threat to the general populace, House \emph{de\'Var}
had to sign a treaty during the foundation of the kingdom to not harm any of
the kingdom's citizen, or citizens of their allied city kingdoms. Although
the idea of being ruled by vampires is scary to outsiders, House \emph{de\'Var}
are fair and just rulers. Their members abide by the law, and do not feast on
humanoids, instead preferring to live off \emph{Ramesk}, a mineral rich fluid
invented by the Ilians as a blood substitute. The liquid also allows the
vampires of House \emph{de'Var} to endure the sunlight for a limited amount of
time, albeit they prefer to wander the streets in daylight with protective
clothing instead.

The house also provides the city guard and justice system for the entire
kingdom, and is paid for this service by the other houses. The island of
Saremen also houses the kingdom's library and arcane institution. Despite
having an obvious reason to be for slavery, house \emph{de\'Var} is openly
against it. They do not require slaves for nourishment, and even if they were
to feast upon them, they'd lose both respect and renown within the very
population they try to rule. The vampires of the house see themselves as
effective and just rulers, since they do not tire or become ill and clouded in
judgement, and wish to proof that very fact to their subjects.

House \emph{de\'Var} was also responsible for creating the race \emph{Umgeher}
in \emph{MI:263}. In their hubris, they attempted to create the perfect
``undead citizen''. Those were supposed to be used as soldiers, guards,
workers and labourers. However the \emph{Umgeher} were poorly received by the
population. Mostly because deceased citizens were used in the process, and
many found their deceased loved ones among the new workforce. Many workers
feared that the undead would replace them, stripping them of their lively hood
and ability to feed their own families. The people of Saremen demanded that
the \emph{Umgeher} should be exiled from their kingdom. Out of fear of
upsetting their population any further, house \emph{de\'Var} gave the
\emph{Umgeher} the gift of reproduction and exiled them from the city. The
exile was lifted in \emph{MI:1100}.

The house's banner shows a blue raven, flying downward upon a white
background.  Blue and white are the main colours of the house.

\subsubsection*{House Liares}
\label{sec:House Liares}

The human house \emph{Liares} rules the territories on the shores and main
land of \emph{Eilean Mor}. Although they are the smallest house of nobility in
Helmarnock, they are one of the most important. They own the vast majority of
farms on the mainland and are vitally important both to provide and produce
the food for the islands, as well as for growing the roots and herbs required
to brew \nameref{sec:Ramesk}, the blood substitution drink for the
vampires. House \emph{Liares} are also responsible for maintaining good
relations with the other city kingdoms, and thus run embassies and provide
ambassadors.

House Liares' banner is a black tree upon white background. White and black
are their main colours.

\subsubsection*{Banner}

The banner of Helmarnock is a shield upon white background, divided into five
section. Each section bears the banner of one the five houses. Top left the
red dragon of Eseriel, top right the owlbear of Onariel, middle right the
golden hammer of Kelemor, at the bottom the tree of Liares, and middle left
the raven of de\'Var.

\subsubsection*{Population}

The kingdom is a sprawling metropolis, housing roughly 18 million people on
all four islands and the mainland. Most numerous are the various kinds of
elves (38\%) followed by humans (31\%) and dwarves (28\%) with the half
races, Umgeher and Diarim making up a small minority (3\%).

\subsubsection*{Society}

Although the high council rules supreme, each distinct old barony (so each
island the main land) has a local government whose main task is to administer
the parts of the kingdom, as well as enforcing laws enacted by the high council.
Slavery is allowed within the city, however slaves do have certain rights. For
example a slave owner must take care, feed and clothe a slave, and a slave
owner who intentionally lets a slave starve is charged with murder.
\emph{Indentured servitude} is quite common, mostly as a way to compensate
victims of crimes by forcing the perpetrator to work off his debts or fine if
they are unable to pay them. The houses of Eseriel, Kelemor and Liares are main
proponents of slavery as they profit most from the free labour. House de\'Var
is a fierce opponent of slavery, but find themselves alone in that position.

\subsubsection*{Academy of Arcane Arts}

Helmarnock is also known around the world for being a generous patron of the
arcane arts and sciences. The academy resides on the island of \emph{Saremen}
and is mainly funded by house de\'Var and house Eseriel. It is both famous,
and infamous, for teaching and researching necromancy. The academy not only
studies and teaches the arcane arts but also most major sciences such as
medicine, physics and astronomy.

\subsubsection*{Expeditionary Force}

The mainstay armies of Helmarnock are called the Helmarnock Expeditionary
Forces (often simply abbreviated ``the forces''). It recruits both from
within the kingdom, but also from people from outside. Foreigners who join the
forces for at least five years receive special consideration when they apply for
citizenship within the kingdom. Many foreigners join, as the expeditionary
forces have a reputation for being a well trained, equipped and capable, who
also pay fair soldier's wages and compensation to families in case of death.

\subsubsection*{Relations}

Due to the widespread acceptance of law-abiding undead throughout the city, the
kingdom has no, or bad relations with most religions and churches that see
undead as an affront to the natural order. Among these are the
\emph{Inquisition of the Third Order}, the \emph{Holy Church of Aleaste} (even
though Aleaste was of House Eseriel) and the various churches and knight
orders of \emph{Lor} are direct enemies of Helmarnock. This rivalry has often
cumulated in skirmishes between the city kingdom and the knight orders, but
neither side risks an all out war.

Helmarnock has signed the \emph{Vonir Accord} with Norbury, and is also one
of Norbury's closest allies.
