\cleardoubleevenemptypage

%% TODO: Artwork

\begin{infobox}{City Kingdom of Morkan}
  %% TODO: Crest
  \begin{multicols}{2}
    \begin{itemize}[label={},noitemsep,leftmargin=0.0cm,topsep=0pt]
      \infoboxitem{Location}{Eastern shores of north \nameref{sec:Iafandir}
      }
      \infoboxitem{Languages}{Teranim, Danvark, Old Teranim}
      \infoboxitem{Government}{Tyranny}
      \infoboxitem{Major Religions}{\nameref{sec:Church of Morkan}}
      \infoboxitem{Area}{est. 40,000 $km^2$}
      \infoboxitem{Population}{est. 490 thousand registered citizens, est.
        2 to 3 million non-citizens and slaves
      }
      \infoboxitem{Non Grata}{monstrous races, undead except vampires, Gorgons,
        devils, druids
      }
      \infoboxitem{Magic}{Magic use outlawed for anyone, except sanctioned
        government agents
      }
      \infoboxitem{Slavery}{yes, all forms, signer of the \nameref{sec:Vonir
          Accord}
      }
      \infoboxitem{Special Laws}{all religions except the Church of Morkan are
        outlawed, monstrous races (including Gorgons) are enslaved or culled
      }
      \infoboxitem{Notable Organisations}{\nameref{sec:Church of Morkan},
        \nameref{sec:Kaltar}
      }
      \infoboxitem{POI}{Central Spire of \nameref{sec:Taras}, slave auction
        houses, as well as a blood arena, and Colosseum, cathedral to
        \nameref{sec:Taras}
      }
    \end{itemize}
  \end{multicols}
\end{infobox}

\clearpage

\subsection{Morkan}
\label{sec:Morkan}

\aren{Oh Ishmael, thy weakness caused so much tragedy and death.}

Morkan (old Teranim for ``beacon'') is a city kingdom on the south eastern
shores of \nameref{sec:Iafandir}. It is often referred to as the ``northern''
or simply the ``tyrant kingdom''.

The kingdom of Morkan has a red, and white banner with a large golden grown
nested in the middle of a shield. Red and white are the main colours of
Morkan.

\subsubsection{History}

The youngest city kingdom of them all, it was founded in MI:1938 by Xian, a
human warrior and barbarian native to Iâfandir. He gathered support for a
campaign towards Iâfandir in \nameref{sec:Hraglund} and \nameref{sec:Norbury}
to establish a human settlement and military outpost in the rather
inhospitable lands of the beast races. Especially in Norbury his plan of
another military outpost against the invasion was well received, and liked
among both nobility and the general populace. He sailed from the shores of
Norbury with his friends and allies Arissa, and Taras in MI:1930. It took Xian
eight years to build a small settlement, as well as bringing most of the local
humanoid tribes of his new land under his reign. But in MI:1938 Norbury
officially supported and endorsed the foundation of a new monarchy, ruling
over the city kingdom of Morkan.

Xias ruled just, and preferred inviting and integrating tribes, rather than
conquering them. Most of the local tribes were humanoid, and many of his
followers from Norbury supported that decision. But when Xias peacefully
integrated non humanoid races, namely a tribe of trolls and ogres, his
popularity waned within his own kingdom. Taras openly opposed him, claiming
that beast races had no place within city kingdoms. In MI:1942 an
altercation between a handful of dwarves and ogres escalated into a short
civil conflict, costing the lives of almost 400 citizens. Xian, still insisted
on finding a peaceful solution to the problem, lost the majority of his power
in a coup to Taras who proclaimed himself ``steward''. Taras continued to
consolidate his power in the royal court, and also gained the support of the
humanoid population by forcing the ogres into exile.

The ogres were forcefully and violently driven from the town in the winter of
MI:1942, and many of the tribe - especially weaker ogres such as the
elderly, women and children - starved or froze to death during the exodus. Even
though the trolls were innocent in this altercation they supported the ogres,
leaving the town along with them. Xian, with his position of power now
severely weakened, found himself on the throne without any real power. His
fate as a ruler was sealed, when in the spring of MI:1943 the tribe of
ogres and troll returned to lay siege upon the city.

The ogres and trolls laid siege the small kingdom of Morkan for several
months. And although the kingdom withstood, the small nation was brought to
the brink of collapse. Taras was sent forth to secure aid from Norbury, while
Arissa and Xian tried to break the siege. Unbeknownst to Taras, they attempted
to break the siege through diplomacy. During the summer of MI:1943 Xian
had secured peace with the trolls and ogres through diplomatic means, and
called Taras home. However Taras returned with an army of volunteers from
Norbury, and rejected the peace treaty. Taras still had the support of a large
portion of the populace, and thus broke the siege forcefully killing most of the
ogres and trolls, while enslaving the rest. His popularity soared after the
victory, and he had Xian and Arissa arrested for high treason.

\subsubsection{A new ruler}

Taras outlawed all beast races from the city kingdom, instituted slavery,
and turned his gaze outward. He proposed a new plan for Iâfandir: make it free
of beast races that would otherwise go forth and raid Eilean Mor and terrorise
peaceful and innocent humanoids in the process. And in turn he'd give the newly
conquered land to those humanoid races to farm and settle upon. Although many
moderates disagreed with him and returned to Norbury, their word of mouth
attracted the radical hard-liners that found Norbury's policy of defence
insufficient or even a weakness.

Taras continued to reign absolute in the small northern kingdom. In MI:1968 it
was revealed that Taras had achieved lich-dom, potentially sealing his reign
of the kingdom for eternity.

\subsubsection{Beast Wars}
\label{sec:Beast Wars}

Taras formed two new armies: the red legion and the iron hand, and set them
loose upon the continent to enact his plan. Morkan is engaged in a never
ending genocidal campaign against any non-humanoid beast races (such as ogres,
trolls, harpies) while offering sanctuary to humanoid species (such as pale
elves or the northern human barbarian tribes). The campaign of massacres,
genocides and massive enslavement of the tribes and species of the continent
became known as the beast wars. The armies of Morkan move further west with
each passing year, forcing all other tribes to flee westward. Some tribes have
tried to flee across the ocean toward Eilean Mor, but are intercepted - and
often slaughtered - on the high sea by Norbury. As of MI:2022 this campaign
has been going on for almost eighty years, without any end in sight.

\subsubsection{Growth and Prosperity}

Over the course of decades Taras shaped the city kingdom of Morkan into a
prosperous, huge city kingdom. Although the continent was harsh and lacking
fertile farmland, he built the wealth of the kingdom by exporting precious
minerals and slaves. By MI:2000 it had roughly 490000 registered citizens, and
uncountable number of slaves. Most of the citizens were humans (33\%) and
elves (31\%), with dwarves (20\%) and halflings (16\%) being in the
minority. Slaves are not counted as citizens, but it is estimated that Morkan
has around 150.000 to 200.000 slaves.

Common male names are: Aki, Asvald, Björn, Einar, Folke, Gunar, Halfdan, Ivar,
Ketill, Olvir, Sigurd, Thorbjörn, Thorgnyr, Toki, Ulfrid, Walther, Yngvar

Common female names are: Alfhild, Asa, Brynja, Eydis, Gyda, Idunn, Katla,
Miriam, Nele, Siglind, Yngvild

\subsubsection{Culture}

Morkan is a tyrannical, fascistic regime that actively represses any dissident
within its own population. Youth are brainwashed at an early age to support
the kingdom's goals of the beast wars. Citizens of Morkan see themselves, and
the pure humanoid races, as the true rulers of Aror and have great disdain for
all beast races, and even half humanoid, half beast races (which they call
``mongrel races'').

The average Morkan is patriotic, militaristic and heavily aligned with the
ideals of the kingdom. Art, song and creative enterprises have no place within
Morkan, unless it furthers the kingdom's narrative of racial supremacy. However
Taras promotes a culture and idolised ``citizen of Morkan'': A person who is
orderly, hard working, conscientious always ready to pick up a sword to defend
king and country, and to whom family, camaraderie is as important as the
``common goal'' of the empire.

Foreigners are often greeted with mistrust, as they are often seen as spies
from foreign powers, trying to undermine the righteous goals of Morkan.
Visitors must expect to be under constant surveillance while staying in the
kingdom, as well as having any business dealings put under intense scrutiny.

\subsubsection{Laws}

Taras rules supreme, and not even his aspects (generals, advisers and
representatives) dare to speak against his word. Slavery is encouraged, as well
as enforced upon beast races and those deemed of ``impure'' blood, criminals
and citizens. Slaves have no rights, no freedoms, and are often sold for
profit to other city kingdoms.

A secret police called the Kaltar silences dissident movements and resistance
cells both outside and within Morkan. They are known to torture and abduct
people, and spy on the general populace to obtain information on dissidents.
The Kaltar are only responsible for anti-government crimes, while the
Inquisition handles criminal and civil law cases. Citizens of Morkan can
expect a reasonably fair trial, unless their crimes include treason or
anti-government activities.

\subsubsection{Aspects}

Taras appointed various high ranking officials with to be his aspects. He
proclaimed that these aspects are a mere extension of his will, and thus
entrusted them with a specific task within the kingdom.

Arissa, the Aspect of Shadow. The elven rogue, and diplomat Arissa returned
from her imprisonment in MI:1978 openly denouncing the actions of Xian, and
joining the kingdom at Taras' side as an aspect of his rule. She oversees the
Kaltar, the secret police and spy organisation of Morkan.

Torem, the Aspect of War, a human barbarian leads the Red Legion, the kingdoms
main fighting force. A brutal, and savage slaughterer of thousands, but also a
brilliant tactician and general.

Eilane, the Aspect of Law, a snow elven diplomat, and wizard. She oversees the
Inquisitors, a small but effective army of judges and executioners. She is
responsible for enforcing Taras' civil law both within Morkan and in the newly
conquered regions.

Karim, the Aspect of Purity is a dwarven cleric of the church of Morkan. He's
mainly responsible for leading the kingdom in spiritual matters, as well as
spreading the church of Morkan among the newly conquered territories.

Telena, the Aspect of Truth, is a human sorceress. She is responsible for the
internal propaganda of the kingdom. She is also directly responsible for the
diplomatic relations with other city kingdoms and nations.

\subsubsection{Church of Morkan}
\label{sec:Church of Morkan}

One by one Taras outlawed the other religions in Morkan. He replaced them with
a Church of Morkan, a religious institution headed by Karim the aspect of
purity. In the canon Taras himself is praised as the divine incarnation of the
will of his people to bring peace and purity upon the land. Membership in the
church is not mandatory for citizens, but required if one wishes to have a
prosperous career within Morkan. The church holds daily masses at midday, but
also teaches prayers and rituals to be held should one not be able to attend
church. Scholars do not know how or why, but priests and paladins of the
church of Morkan are granted divine spells and power. It is still an unsolved
mystery how Taras accomplishes this feat, as he is the sole deity worshipped
by the Church of Morkan.

\subsubsection{Iron Hand}
\label{sec:Iron Hand}

The Iron Hand are the elite soldiers of Morkan. Heavily armed, armoured and
well equipped with magical equipment, they partake in the conflicts of the
beast wars as necessary, but are also the personal guard of Taras
himself. They are picked from the best of the best of the Red Legion and also
trained in special operations. For many, there is no greater honour than to
serve as personal guards to Taras himself.

\subsubsection{Red Legion}
\label{sec:Red Legion}

The Red Legion is the main stay army of Morkan. It is known for its
fierceness and brutality in battle, as well as for its cruelty it inflicts
upon captured towns and villages. All subjects of Morkan must complete a
three year service within the red legion to attain citizenship status. Humanoid
slaves must complete a ten year service within the legion before they are
granted citizenship status.

The legion takes able bodied humanoid men and women from towns they
capture, while killing the rest. Those that show promise as fighters are
recruited, while the rest are enslaved. They are also tasked with enacting the
decree of purity, the genocide of beast races, upon Iâfandir.

A sizeable amount of legionaires were also sent to fight with the coalition
against the \hyperref[sec:Devil Siege]{devil invaders of Forsby}. Although
less organised and disciplined than its counter part armies, it proved itself
as a strong and ruthless fighting force in the face of a superior enemy.

\subsubsection{Kaltar}
\label{sec:Kaltar}

The Kaltar (old Teranim for ``owl'') is the secret police of Morkan. Lead by
the Arissa the aspect of shadow, it is tasked with finding and eradicating
dissident movements, traitors and enemies of the state.  It achieves this goal
with a vast network of civil informants, highly trained spies and field
operatives, and various outposts all over the world that help it enact Tara's
will outside of the city gates. The Kaltar are feared all over the kingdom for
abducting, torturing and murdering everyone they suspect of undermining the
rightful rule of Taras.

\subsubsection{Relations}

Morkan has only one true ally: Norbury. All other city kingdoms paused their
diplomatic relations with the kingdom after the beast wars began. The kingdom
of Morkan is a signer of the \nameref{sec:Vonir Accord}.

It is an open secret that Norbury trades heavily with Morkan. In exchange for
slaves, iron and copper, Norbury sends massive amounts of food and medicine to
its northern neighbour. The rapid and aggressive expansion, combined with a
scorched earth policy, and a heavy governmental focus on warfare has made
Morkan highly dependant on the aid of Norbury to be able to feed its own
population.
