\subsection{Stenheim}
\label{sec:Stenheim}

The city kingdom of \emph{Stenheim} (also ``Stoahom'' in some local dialects)
lies on the north western shores of \hyperref[sec:Goltir]{North Goltir},
situated on the foot of the coastal mountain range of the Aldenes, where the
Taraun river flows into the sea.

While the majority of the newer city has been built at the food of the
mountain, the old city centre, the castle and main fortifications reside in
natural and hewn caverns in the mountain.

\subsubsection{History}

It was officially recognised as a city kingdom in GT:1551, but is considered
far older. Earliest record dating back to almost GT:531 were found in the
vault of the city, albeit it was but a small deepkin settlement back then. It
began as a small tribal city, but soon the favourable conditions of the
settlement's location, namely access to the shore and fresh water from the
river, attracted more and more deepkin, and dark elven clans. Unlike most of
the dwarven clans that lived in the Aldenes, the deepkin clan welcomed their
surface brethren into their deep caverns from the beginning.

The deepkin built another smaller city outside their caverns, and used it to
trade the ores and gemstones to the other nations and kingdoms. The access to
the river, the easy connection to the sea (and thus trade), and its beautiful
and scenic lake scenery attracted more and more of the surface races, and the
city grew over the course of many centuries.

\subsubsection{Wars}

The kingdom was involved in many defensive wars over the course of its early
history. Many dwarven clans, especially the \emph{Black Hill} and
\emph{Snowhammer} clans, as well as remnants of the various Ilian empires of
the deep tried to seize the deepkin workshop. None of these assaults and sieges
was successful, and nowadays the kingdom of Stenheim has eclipsed all dwarven
and Ilian clans in size and power.

The deepkin had used their ingenuity to construct advanced war machinery such
as arcane siege weapons, arcane weapons and armour, as well as war golems to
defend their home. This distinct technological advantage helped them defeat
their aggressor, even though they often had superiority in numbers.  This
technological advantage did not sleep, and still to this day the city kingdom
is considered one of the strongest in terms of military power, capable of
fielding an army well equipped with arcane gear, as well as countless combat
ready golems, as well as arcane war and siege machinery.

Compared to many other more warring clans of the Aldenes, the deepkin never
enslaved or seized the lands of other clans. Most of the wars the deepkin
thought were defensive in nature. Their less aggressive approach, as well as
their propriety to get along, diplomatically and culturally, with the other
deep races made their kingdom an attractive destination for the other mountain
clans. Many smaller dark elven, and dwarven clans migrated to the city and
integrated well into the deepkin culture.

\subsubsection{Population}

The outlying city of Stenheim, as well as the deepkin workshop and castle holds
roughly 19 million people, of which the majority are deepkin (39\%) and dark
elves (22\%), while humans (11\%), elves (10\%), while halflings (4\%) and
dwarves (3\%) make up the minority. Due to the deepkin's liberal and welcoming
nature, Stenheim has become a destination for many half races (9\%) as well as
undead (2\%).

The city also uses humanoid-like golems for dangerous tasks such as city
defense, or difficult menial labour such as mining, construction or hauling.
They are called ``Homunkulus'' within the city, but outsiders know them mostly
from the many defensive wars where they earned the nickname ``Warforged''. The
vast majority of these golems are nothing more than well programmed, and
arcane automatons made of steel and Everblack. But some have gained
consciousness and self-awareness. Stenheim has retroactively freed and
liberated all self-aware Homunkulus from servitude, and given them citizen
rights within the kingdom.

Common male names are: Adrian, Alex, Andreas, Anselm, Arnold, Axel, Baldur,
Benjamin (Ben), Björn, Eckbert, Eduard, Erik, Erwin, Felix, Florentin
(Florian), Franz, Gisbert, Gregor, Gustaf, Heinrich, Helfried, Johannes
(Johann, Hannes), Karl, Klaus, Kilian, Lars, Leo, Lukas, Matthias,
Maximilian (Max), Nicklas (Nick), Oliver, Othmar, Patrick, Rafael, Reinhold,
Samuel, Sieghard, Sigismund, Torben, Valentin, Wolf

Common female names are: Abigail, Ada, Adelina (Lina, Adela), Alexandra (Alex,
Alexa), Amelie, Anna, Brigitte (Birgit), Daniela (Nela), Edit, Eleonora,
Elisabeth (Elisa, Elli, Lisa), Emma, Eva, Evelyn, Hanna, Helena, Ida, Ina,
Irene, Irma, Jana, Julia, Karla, Katarina (Katrin), Leah, Magdalena (Lena),
Margareta (Greta, Grete, Gretchen), Manuela, Mia, Ria, Rita, Roswita, Sara,
Sofia, Verena, Viola

\subsubsection{Culture}

The deepkin of Stenheim (and by extension the other races living there as
well), are predominantly atheistic. Only Forun and the other holy mothers have
a sizeable following within the mountain kingdom. The city mostly focuses on
mining and arcane research, and the people of Stenheim pride themselves for
being a centre for scientific and arcane learning.

Most people of the kingdom are considered humble, curious and known for their
love all things science and engineering. The deepkin have shared their passion
for golem construction, mechanical and civil engineering with the other races
that joined them. Almost all people in the kingdom enjoy luxuries that no
other kingdom can offer, such as indoor plumbing, arcane light fixtures and
cheap commodities due to early attempts at mass production.

The culture of Stenheim is known for being one of the most liberal and
advanced of all the city kingdoms. The people enjoy a wide variety of social,
economical freedoms, as well as a fair, stable and efficient state and legal
system.

\subsubsection{Rule}

The kingdom is lead by a patriarch or matriarch which is elected by council of
city elders, guild leaders, high ranking professors from the arcane academy,
as well as constabularies that are chosen by the general population through
votes. This ruler is then sworn in, and stays in power until his or her death,
abdication or until the council elects to vote for a new patriarch or
matriarch. Although not technically a queen or king, the ruler of the city is
deemed equal to a king or queen by the other city kingdoms and welcomed as
such.

More unusual is the fact that the kingdom is split into smaller districts,
each ruled by a constabulary. Although these local rulers report to the
matriarch or patriarch, they hold considerable power within their district,
and are even allowed to pen local laws. They are voted into office by the
people of their district, albeit the matriarch can remove a constabulary from
power.

The city's population and the majority of their rulers are against slavery,
and has also removed indentured servitude in favour of imprisonment. Convicted
criminals can still opt to reduce their sentence by mining for ore, or reduce
their sentence even further by mining for \nameref{sec:Everblack}. The kingdom
did not sign the \nameref{sec:Vonir Accord}, but most of their citizen are
well protected from slavery in other kingdoms as no foreign power wishes to
risk a diplomatic incident with Stenheim.

\subsubsection{Relations}

The kingdom holds good relations with the other city kingdoms, except for
Kesmar. Stenheim often accused the dwarven kingdom for secretly aiding their
enemies during past sieges and skirmishes. Most of surrounding dwarven clans
in the mountain hold the kingdom in contempt, seeing them as an imperialistic
force with no equal in power. Even though the kingdom does not aggressively
expand, the surrounding clans and tribes are pressured into joining the city
or face becoming irrelevant next to their neighbour.

Furthermore Stenheim is known for exporting both their advanced war machinery,
technology, ore and everblack to other nations. It is known for selling their
weapons and golems to anyone who are able to front the price.
