\section{History of the World}
\label{sec:History}

Proper recording of history started shortly before the foundation of the
first city kingdom of \nameref{sec:Fes al-Bashir}. The earliest scholars
were able to accurately reconstruct the earliest history with the help of
the Aurelis and the Dragons. These two races were advanced enough in the
early aeons of the humanoids of Aror, to accurately chronicle the history
of the core humanoid races.

The first race to settle Aror were the dragons, who found it uninhabited
of intelligent life, yet found that great and mighty beasts roamed the
planet. They opted to stay on the barren continent of \nameref{sec:Draigynus},
as to not disrupt the natural evolution of life on the planet. Their peaceful
life came to end, when the giants invaded Aror to wage war against the dragons,
and created intelligent monstrous creatures out of the beasts that roamed the
world. The giants engineered these monstrous races to be intelligent, and
aggressive in an attempt to create the perfect soldiers for their campaign
against the dragons.

According to the dragons, the \nameref{sec:Tynrikke} where elevated to
intelligence by the giants yet revolted against them. The Týn instead joined
the dragons in their battle for survival, and would be instrumental in
driving the giants from Aror.

While the war on the surface raged between the dragons and the giants,
the \nameref{sec:Ilians} became ever more intelligent and organised, resulting
in the creation of the great Ilian civilisation. Unlike the other intelligent
races at the time, who either came from other planes or were engineered, the
Ilians were the first intelligent life that was native to Aror.

\clearpage
\onecolumn
\begin{longtable}{@{\,}r <{\hskip 6pt} !{
  \color{LightSteelBlue3}
  \makebox[0pt]{\textbullet}
  \hskip -2.6pt
  \vrule width 1pt
  \hspace{\labelsep}
  }
  >{\raggedright\arraybackslash}p{11cm}
}
    %% Actual entries
    ca. GT:-800.000  & Dragons settle Aror. \\
    ca. GT:-600.000  & Giants first land on Aror to fight the dragons, and
                       populate the planet with engineered monstrous races \\
    ca. GT:-500.000  & The \nameref{sec:Tynrikke} build a great civilisation,
                       which lasts for roughly four thousand years, before it
                       falls for unknown reasons. Their temples, hallowed
                       shrines, and teleportation magic between Goltir and
                       Eilean Mor can still be found to this day. \\
    ca. GT:-480.000  & The \nameref{sec:Ilians} become intelligent and rapidly
                       develop, building a great civilisation beneath the
                       surface of Aror. \\
    ca. GT:-200.000  & The anatomically modern core humanoid races develop \\
    ca. GT:-60.000   & \nameref{sec:Second Ice Age} covers Aror, humanoid races
                       settle all continents \\
    ca. GT:-9.000    & Population boom on Aror, core humanoid races and
                       monstrous races struggle for resources. The so called
                       \nameref{sec:Aeon of Strife} begins. \\
    ca. GT:-8.700    & \nameref{sec:Druids} create the first \nameref{sec:Fey}
                       in secret.\\
    ca. GT:-8.300    & The great \nameref{sec:Schism} occurs, where a sizeable
                       number of core humanoid races flee beneath the surface,
                       to avoid the battles of the strife. \\
    ca. GT:-8.000    & \nameref{sec:Morana} creates \nameref{sec:Vampires},
                       leading to an event called the ``great betrayal''. \\
    GT:-7.633        & The great \nameref{sec:War in Heaven} begins between the
                       \nameref{sec:Aurelis} and the \nameref{sec:Scourge}. \\
    GT:-7.600        & Aurelis succeed in freeing some demons from the Scourge.
                       \nameref{sec:Devils} are born, and settle a new planet
                       called the ``layers of hell''. \\
    ca. GT:-7.000    & The great war in heaven is won by the Aurelis, leaving
                       most of their people dead, their culture destroyed, and
                       their planet in ruins. \\
    ca. GT:-3.000    & \hyperref{sec:Five Holy Orders} are founded. \\
    ca. GT:-2.200    & Armistice between monstrous and humanoid races, and the
                       call for a \hyperref[sec:First Crusade]{crusade} against
                       the ever growing fey threat became a reality. \\
    GT:-1400         & The deepkin invent the \nameref{sec:Everblack Golem},
                       creating the ultimate weapon against the Ilians. \\
    GT:-550          & \nameref{sec:Eigyr} is born on the continent of
                       \nameref{sec:Eilean Mor}. \\
    GT:-390          & Eigyr conquers all major monstrous cities, razing them,
                       and establishing her empire. This year marks the end of
                       the aeon of strife on \nameref{sec:Eilean Mor}. \\
    GT:0             & \nameref{sec:Fes al-Bashir} officially declares itself a
                       kingdom, marking the age of the city kingdoms. \\
    GT:24            & \nameref{sec:Aren Fel} is born. \\
    GT:339           & \nameref{sec:Hraglund} is recognised as a city kingdom
                       out of the remains of Eigyr's empire. \\
    GT:551           & \nameref{sec:Nen-Hilith} is recognised as a city state. \\
    GT:760           & \nameref{sec:Knight Order of Tavos} is founded in
                       Hraglund. \\
    GT:864           & The \nameref{sec:Third Crusade} begins, targeting the
                       witches of \nameref{sec:Walburga}. \\
    GT:984           & The baronies of \nameref{sec:Helmarnock} found a kingdom
                       under the banner of the noble lineage of Helm. \\
    GT:1148          & \nameref{sec:Forsby} wins a major battle against the
                       monstrous races, driving them almost completely from
                       their land. They become recognised as a city kingdom. \\
    GT:1200          & The \nameref{sec:Great Exodus} begins, as many dwarves,
                       elves, deepkin, and halflings return to the surface
                       after failing to secure peace in the depth against
                       the \nameref{sec:Ilians}. \\
    GT:1321          & The Knight Order of Tavos starts its \nameref{sec:Fourth
                       Crusade}, targeting Aren Fel. \\
    GT:1551          & \nameref{sec:Stenheim}, after fighting countless battles
                       against competing large dwarven clans, is recognised as a
                       city kingdom. \\
    GT:1849          & \nameref{sec:Norbury} fights for its independence against
                       Hraglund and wins, becoming a city kingdom. \\
    GT:2084          & \nameref{sec:Graham Balance} is born. \\
    GT:2992          & \nameref{sec:Kesmar} is recognised as a city kingdom. \\
    GT:3391          & \nameref{sec:Holy Crusade} begins, seeing fighting
                       between the forces of \nameref{sec:Silent Queen} and
                       \nameref{sec:Griannar}. \\
    GT:3408          & After countless dead on both sides, the holy crusade ends
                       at the siege of Hraglund. Church of Griannar is but
                       extinct on Aror. \\
    GT:3411 MI:0     & Griannar disappears, all his clergy lose their power. \\
    MI:4             & Silent Queen disappears, her power and throne as a deity
                       absorbed by her high-priestess \nameref{sec:Aria}. \\
    MI:263           & Vampires of Helmarnock create \nameref{sec:Umgeher}. \\
    MI:782           & The first \nameref{sec:Dragon Teleporter} is discovered
                       ushering in an unprecedented age of travel, trade and
                       cultural unity. \\
    MI:890           & \nameref{sec:Holy Church of Aleaste} splits away from the
                       main church of the \nameref{sec:Order}. \\
    MI:1213          & \nameref{sec:Esmayar} is sacked by the gnolls. \\
    MI:1260          & \nameref{sec:El-Fayam} is recognised as a city state. \\
    MI:1680          & \nameref{sec:Plague of Hraglund} almost wipes out
                       Hraglund, followed by devastating wars against the
                       weakened city kingdom two years later. \\
    MI:1918          & Giants return to continue their war against the dragons.
                       Elves and halflings join the war against the giants
                       invaders. \\
    MI:1920          & \nameref{sec:Nen-Hilith} falls to a siege by the giants.
                       The elves and halflings flee north to Goltir and found
                       \nameref{sec:Avenfjord}. \\
    MI:1938          & \nameref{sec:Morkan} is recognised as a new kingdom. \\
    MI:1952          & Giants of Farlar create the \nameref{sec:Diarim}. \\
    MI:2017          & Devils invade North Goltir, laying siege to the city
                       of \nameref{sec:Forsby}. \\
  %%\rowcolors{1}{white}{light-grey}
  \captionsetup{labelformat=empty,font={large,bf}}
  \caption{Historic Events of Aror}
\end{longtable}
\twocolumn
\clearpage

\subsection{Second Ice Age}
\label{sec:Second Ice Age}

Roughly sixty thousand years ago an ice age covered most of the world
of \emph{Aror} in vast sheets of ice and snow. Continents that were separated
by sea, where now suddenly accessible through thick sheets of ice. This
allowed the \textbf{four core humanoid races}, the
\hyperref[sec:Humans]{humans}, \hyperref[sec:Elves]{elves},
\hyperref[sec:Dwarves]{dwarves} and \hyperref[sec:Halflings]{halflings}
to migrate away from \nameref{sec:Arania} and settle the entire known
world. Although the humanoid races were successful in adapting to the new
lands and challenges, they had to face fierce opposition.

\subsection{Aeon of Strife}
\label{sec:Aeon of Strife}

When the humanoid races arrived in the other continents around a thousands of
years before the aeon of \emph{GT}, they found that they were already
inhabited by sentient races. \textbf{Monstrous races} such as ogres,
minotaurs, orcs, trolls, hobgoblins, gnolls, bugbears already called these
continents their home, alongside non-sentient monstrous species such as
hydras, manticores and wyverns. Through ancient stories of the dwarves, early
writings, ancient stone tablets, tales from the \hyperref[sec:Dragons]{dragons},
and even cave paintings, it was revealed that the humanoid ancestors were in a
constant state of conflict with these monstrous races. Wars, skirmishes, and
often the destruction of entire early villages and even cities was a common
occurrence in early history. This early time of constant fighting, turmoil and
wars against the sentient beast races is now referred to as the \emph{aeon of
  strife}.

The aeon saw the birth of many new races, such as
\hyperref[sec:Vampires]{vampires}, \hyperref[sec:Fey]{fey} and
\hyperref[sec:Lycanthropes]{lycanthropes}. It also saw a vast destruction of
nature, as both sides of the war cut down forests, dried swamps, and forever
corrupted landscapes and areas with dark and foul magic. The aeon of strife
lasted well into the aeon of \emph{GT}.

Even though the aeon of strife is now hundreds of years in the past, it is
still vividly remembered in both humanoid and monstrous cultures through
stories, song, and tradition.

\subsection{Schism}
\label{sec:Schism}

The ultimately successful survival strategy to deal with such a hostility
during the strife ingrained itself as the cultural core of the humanoid
races. Many dwarves went underground and organised themselves in strict
hierarchical clans and cities, that allowed them to optimise their economies to
the harsh realities and lack of resources of the depths. Some humans and elves
followed the dwarves underground but ultimately failed to replicate their
success. With a few notable exceptions, such as \nameref{sec:Stenheim}.
Although the \nameref{sec:Deepkin}, the underground dwelling cousins of the
humans, built large civilisations underground they were ultimately defeated by
the \nameref{sec:Ilians} of the depths and driven to the surface. The dark elves
instead relied on small clans, families and by being constantly on the move to
ensure the survival of their species.

Meanwhile on the surface elves and halflings sought to settle as far away from
the monstrous races as possible, leading them to the continent of \emph{South
Goltir} and \emph{Farlar}. Other elves settled in the frozen north and south,
becoming known as the \nameref{sec:Snow Elves}.

Humans on the other hand used their ingenuity and skill to build great
civilisations and cities that could potentially withstand the skirmishes and
sieges of the sentient monstrous races. They were not alone, as many elves
(now known as \nameref{sec:Wood Elves}), and some halflings and dwarves stayed
with them. Through many iterations over the course of thousands of years,
which resulted in countless destroyed and ransacked cities and fallen
civilisations, these humanoids have now achieved the unthinkable: dethrone the
monstrous races as the predominant species across all of Aror.

\subsection{Great Exodus}
\label{sec:Great Exodus}

Now many elves and halflings have joined the human effort of building large
centres of civilisation, enriching the predominantly human city kingdoms that
dot the world of \emph{Aror}. Their struggle against the sentient monstrous
races is far from over, especially in the central regions of the continents,
or from the still predominantly monstrous continent of \emph{Iâfandir}. The
majority of dwarves have remained underground, continuing their strict ways of
life as it has served them for aeons. A success that was not shared by the
dark elves and deepkin, who have mostly abandoned the deep and returned to the
surface

\subsection{War in Heaven}
\label{sec:War in Heaven}

The ``War in Heaven'' (also known as the ``great war in heaven'') started in
GT:-7633 (almost 12,000 years ago), when the \nameref{sec:Scourge} successfully
gained a foothold on the \nameref{sec:Aurelis} home world of Celestis. This war
raged for over six hundred years, killing countless of Aurelis, destroying their
culture, society and leaving half of their planet uninhabitable. During the war,
the Aurelis attempted to free some of the demons from the psionic slavery of the
\nameref{sec:Abyss}. These newly freed demons refused to aid the Aurelis, and
instead left to find themselves a new homeworld. These freed demons became known
as the ``pacru'i'' or \nameref{sec:Devils}. During the war, the Aurelis' king
\nameref{sec:Lor} made himself known to the people of Aror, in an effort to
recruit external help for his war.

\subsection{First City Kingdoms}

The tide of the aeon long war against the monstrous humanoids finally turned
in favour for the humanoid races with the foundation of the first city
kingdoms.  Vast, well defended, and strategically placed city nations, these
city kingdoms provided defence, and security for the people, society, culture,
and means of production so they could grow and flourish. The first city
kingdom to be founded was \nameref{sec:Fes al-Bashir}, and its success in the
battles during the aeon of strife, was soon copied across the world.  The
early years of what is now the the aeon of \emph{GT}, saw the formation of
many powerful nations, such as \nameref{sec:Hraglund}, \nameref{sec:Esmayar}
and \nameref{sec:Helmarnock}, which helped cement the humanoid victory and
conquest with brick and stone.

\subsection{Crusades}
\label{sec:Crusades}

Several holy knight orders and churches, for example the \nameref{sec:Knight
  Order of Tavos}, have started several crusades throughout history. Most of
these had devastating repercussions for the people of Aror, but also for the
knight orders themselves. Modern scholars agree that most of these crusades,
ran counter to their goal of making Aror safer, and instead brought chaos,
death and destruction upon the world.

\subsubsection{First Crusade}
\label{sec:First Crusade}

\nameref{sec:Fey} population grew to unprecedented heights around
\emph{GT:-2200}, effectively making them a third power in the strife. The fey
were numerous, well organised and supported by the druids, and thus easily
capable of threatening both monsters and humanoids with extinction. The early
decades of the war saw devastating losses for both monstrous and humanoid
sides, earning that aeon the name ``nature's wrath''. Seeing all civilised
life in jeopardy, many monstrous followers of the \nameref{sec:Three Kings}
called out for a cease fire between the monsters and humanoids. The humanoid
people largely agreed, and the \nameref{sec:Church of Light} and the
\nameref{sec:Third Order} called for a crusade against the fey, and their
creators the \nameref{sec:Druids}. The crusade lasted for over eighty years,
but was successful in driving both the druids and their creation, the fey, to
near extinction.

\subsubsection{Second Crusade}
\label{sec:Second Crusade}

\subsubsection{Third Crusade}
\label{sec:Third Crusade}

In \emph{GT:864} the Knight Order of Tavos officially declared war against the
witches of \nameref{sec:Walburga}. The witches were accused of necromancy,
evil sorcery, and colluding with \nameref{sec:Devils}. In hindsight this war
was called the ``third crusade'', and it marked the beginning of an era of
conflict against the knight order's many perceived enemies.

The witches of Walburga had already waned in power and influence since the
great betrayal, and were thus no match for the heavily armed and well trained
knights and paladins of the order. Many followers of the \nameref{sec:Old Ways}
that lived in the affected regions refused to aid the witches, while some
aided them passively by allowing the witches to hide in their towns and
cities. The Knight Order fought the witches in battles and skirmishes, but also
arrested many in nightly raids and surprise attacks. Those arrested where
trialled, sentenced, and then burnt at the stake. According to the vampires of
\nameref{sec:House deVar}, \nameref{sec:Morana} herself pleaded to her former
children to save the witches from certain destruction. A secret deal was truck
between Morana and the vampires of House de'Var, and the vampires began
defending the witches against the crusaders.

Although some witches were protected by the followers of the old way, the
\nameref{sec:Tynrikke}, and the vampires, the vast majority of them were
killed in battle or sentenced to death. Some covens of \nameref{sec:Walburga}
were completely wiped out, and many were spread across the
\nameref{sec:Dirgewood} and the \nameref{sec:Toralian Highlands}. The witches
are still recovering from this deadly disaster to this very day, struggling to
rebuild their covens and regaining the knowledge that was lost or destroyed
the knight order. The death toll is uncertain, but scholars agree that it
could be as high as four thousand.

\subsubsection{Fourth Crusade}
\label{sec:Fourth Crusade}

The very second crusade, which was officially announced by the Knight Order of
Tavos in \emph{GT:1321}, aimed to bring \nameref{sec:Aren Fel} to justice for
several crimes, including conspiracy, murder, and instigating wars.

During the crusade the Knight Order prosecuted, arrested and even tortured
many innocent women who were accused of being Aren Fel. Most of these were
deepkin women, whose ability to cast any form of unknown magic was deemed
reason enough to warrant an arrest. The crusade itself was condemned by the
\nameref{sec:Five Holy Orders}, as well as the \nameref{sec:Church of
  Light}. As evidence came to light that several of the accused but innocent
women died from the violence inflicted by the Church, the \nameref{sec:Third
  Order} began to openly oppose the knight order, prosecuting its members for
torture and murder. The crusade caused a massive backlash against the knight
order, and many lines of nobility fell from their status simply by being
linked to the crusade. Since the Undying Witch always changes bodies, and thus
appearance, she managed to evade the crusade for several decades before the
crusade was deemed a failure, and officially ended.

Aren Fel was never caught, yet the crusade, according to scholars of the
\nameref{sec:Second Order}, caused the death of over three-hundred innocent
women.
