\subsection{Yua'cata}
\label{sec:Yuacata}

Yua'cata is a vast rain forest on the main land of \nameref{sec:Karnak}. It is a
wild and savage place, untouched by civilisation. The rain forest surrounds the
vast fresh water lake of \emph{Mu'ut}.

Yua'cata is home to thousands of different species of animals, such as birds,
insects, reptilians as well as predatory felines and snakes. The warm climate
and the abundance of water and resources lead to a diverse and large biome.

\subsubsection{Mu'ut}
\label{sec:Muut}

\emph{Mu'ut} is a large fresh water lake in the centre of the continent of
Karnak. It is geologically active, and its warm water fuels thousands of
smaller and bigger rivers that flow in all directions towards the sea. Mu'ut
can be considered the heart of the Yua'cata rain forest, as its warm waters
fuel the tropical climate, rain and thus the vast rain forest of Yua'cata.

\subsubsection{Tribes}

The jungle is also inhabited by thousands of tribes of sentient monstrous and
humanoid races, including humans, \hyperref[sec:Wood Elves]{wood elves},
\hyperref[sec:Medusa]{medusa}, as well as lizardfolk and sahuagin. Most of
these are hunters and gathers, and often differ greatly in traditions, customs
and believes. There is one cultural element that many tribes share however: an
almost holy reverence of the lake of Mu'ut.

\subsubsection{Savage Elves}
\label{sec:Savage Elves}

The most notorious of the jungle tribes are the wood elven tribes of the
Xanarian river. Among other races these wood elves are often referred to as
\emph{savage elves}. They worship an ancient being called \nameref{sec:Xir}
who they believe sleeps beneath the surface of the holy rivers of Mu'ut. Xir
teaches that all unbelievers are impure, and can only be redeemed by feeding
them to him by drowning them in the river. These wood elves raid, pillage,
murder and sacrifice other sentient races they come across without mercy, as
in their eyes there is only one way for them to be redeemed in the eyes of
their lord.

The Xanarian tribes also practice cannibalism. They believe that eating their
own kind after death makes their deceased continue to live within them. They
rarely eat outsiders, as they believe their flesh to be corrupt and impure.
