\subsubsection{Alps}
\label{sec:Alps}

Alps are devious daemons that choose a small humanoid appearance with black
skin, glowing yellow eyes, and grotesque distorted faces. These daemons prefer
to possess humanoid creatures, especially those they deem weak in character,
or those chronically laden with negative emotions such as anger, hatred,
guilt, or depression. Alps prefer to remain perfectly hidden within their host
body of choice, but can be detected through soul sight, and various rituals of
the Old Ways.

These daemons cannot talk, and prefer to use communicate with their host
through horrific, and twisted dreams. Alps use these nightmares in an attempt
to teach their hosts of their past failures, or show them a road to confront
their past so that may move forward past their traumas. Alps are clearly
highly intelligent, but outside a host body they are limited to communicate
through primitive means, such as shrieks, grunts, and a cackled laughter.

\aren{The Doresh word for nightmare ``Alptraum'' traces its roots back to
  these little pests.}

It was long believed that they feed of these negative emotions, torturing the
host with their traumas for nourishment until the afflicted manages to confront,
and ultimately overcome their past failures. More recent research however has
suggested that they abhor the negative aura that tortured and troubled souls
give off, and simply wish to correct the source of tainted soul energy like one
would plug a hole in a leaking ship.

Regardless of their intent, Alps have always been closely associated with the
true goddess of \nameref{sec:Nyddwr}, as they force people to face their past.
While they never physically harm their hosts, many victims that fail the Alps'
tests were driven mad from the never ending psychological horrors and torture.

\begin{35e}{\Large{Alp}}
  \srditem{Size/Type}{Small Daemon}
  \srditem{Hit Dice}{2d12+2 (15 HP)}
  \srditem{Initiative}{+3}
  \srditem{Speed}{20 ft.}
  \srditem{Armour Class}{13 (+2 dexterity +1 size), 13 touch, 10
    flat footed
  }
  \srditem{BAB / Grapple}{+2/+2}
  \srditem{Attack}{Bite +2 melee (1d4)}
  \srditem{Full Attack}{Bite +2 melee (1d4)}
  \srditem{Space/Reach}{5 ft./5 ft.}
  \srditem{Special Qualities}{Daemon traits, Trip (Ex), Selective Presence
    (Ex), Harbingers of Death (Ex)
  }
  \srditem{Saves}{Fort +1, Ref +6, Will +4}
  \srditem{Abilities}{Str 10, Dex 16, Con 12, Int 13, Wis 13, Cha 16}
  \srditem{Skills}{Bluff (10), Intimidate (10), Listen (6), Sense Motive (6),
    Spot (6)}
  \srditem{Feats}{Persuasive, Run}
  \srditem{Environment}{Any}
  \srditem{Organisation}{Solitary}
  \srditem{Challenge Rating}{2}
  \srditem{Treasure}{None}
  \srditem{Alignment}{Chaotic Neutral}
  \srditem{Advancement}{None}
  \srditem{Selective Presence (Ex)}{An Alp can, at will, opt to appear
    only to those it wishes. This ability functions like a continuous
    combination of \emph{Greater Invisibility}, and \emph{Pass without Trace},
    but is a soul-based ability. Not even \emph{True Seeing} can thus reveal
    the presence of the hound. \emph{Soul Sight} will still reveal the presence
    of the Hound's soul, allowing a soul caster to spot a hidden Alp.
  }
  \srditem{Vivid Dreamers (Ex)}{An Alp can create an imaginary dreamscape
    within the hosts mind once the host is asleep. This imaginary dreamscape is
    semi-real, and the Alp can choose to move minor things from the dreamscape
    into reality once the host wakes up, such as small cuts or bruises, create
    or destroy small items (up to half a kg or 1 lbs.), simple drawings or
    writings, etc.
  }
\end{35e}
