\subsection{Aurelis}
\label{sec:Aurelis}

The Aurelis are an extra planar species of winged humanoids, native to the
planet of Celestis.

\subsubsection{Appearance}

They often have pale white, light blue or light red skin, long white or blond
hair, and large feathered wings. Their wings often match their hair colour,
and allow them to both fly and glide through the air. Aurelis are technically
immortal (but not invulnerable), and can thus become extraordinarily powerful
as they potentially have all eternity to train, learn and hone their
skills. Aurelis speak their own language called \emph{ralis}, with their own
alphabet.

Their ability to fly also makes them lighter in build than most other humanoid
races. Aurelis have hollow bones, and most have a smaller stature (most do not
reach 1.70 cm) and are generally weaker than other humanoids of the same
stature. Their frail nature has driven them to become expert armour smiths,
capable of producing decent armour that is still light enough to allow them to
fly. Warriors of the Aurelis often forgo light armour, in favour of heavy
armour to protect them against attacks, but are then reduced to gliding.

The common folk of Aurelis are between 1.60 and 1.70 in height, while the
older, and more powerful of their kind - known as Paragons - are capable of
growing to tremendous heights (up to five metres). With their overly large
wingspans to support their width, these large Aurelis make a awe inspiring
sight to behold.

\subsubsection{Culture}

Aurelis culture heavily favours the individual, individual rights as well as
a peaceful co-existence among each other. There is a focus for allowing all
avenues of expression, and are thus supporters of both the arts and sciences
in equal measures. Aurelis culture also heavily relies on ancestors worship,
as they meticulously catalogue the achievements of those that lived before,
and use their lives as an example to inspire the young.

The average Aurelis are jovial, helpful and loving in nature, but as with most
races, outliers and exceptions exist. This does not mean that they are
incapable of battle and war. Their elite warriors - called Paragons - have
their own rituals, long standing history and traditions in the art of battle,
and will confront and destroy anyone and anything that would threaten
Celestis.

\subsubsection{Civilisation}

Aurelis are builders of great civilisations, cities and are expert arcane and
divine craftsmen. They are responsible for creating many powerful arcane and
divine artefacts that mad their way to Aror. Their societies are centred
around the concepts of liberty, peace, individuality, freedom as well as
aiding and helping others. Aurelis are still lead by one high king or queen,
who rules mostly symbolically while an elected council runs the society.

The current patriarch of Aurelis is called \nameref{sec:Lor}. Their current
and all past patriarchs and matriarchs are also worshipped as gods in ancestor
worship, and serve as cultural icons and role models. Together they are
powerful enough to grand the clerics and priests of Aurelis with divine power.

\subsubsection{Celestis}
\label{sec:Celestis}

They originally hailed from the plane of Celestis, a beautiful continental
planet with lush forests, tall mountains and vast seas. But their home was
invaded by the \hyperref[sec:Scourge]{scourge} of the \nameref{sec:Abyss}
several aeons ago. The resulting war lasted for centuries, and although the
Aurelis were victorious against the scourge, their planet was destroyed and
polluted. It is now a global desolate wasteland, that is being rebuilt by the
surviving Aurelis population.

\subsubsection{Devils}

During the war against the scourge of the Abyss the Aurelis attempted to break
the demons psionic bond with their creator entity. They succeeded, and gave
those demons freedom with the hope that they'd turn against the scourge that
enslaved them. Instead they retreated from Aurelis to create their own
societies, and are now known as the \hyperref[sec:Devils]{devils}.

\begin{35e}{Aurelis}
  The Aurelis combine the angels and archons of D\&D into one group. All in all
  their society can be considered \emph{neutral good}, but the Aurelis may have
  any good alignment.
\end{35e}
