\subsubsection{Black Hounds}
\label{sec:Black Hounds}

Black Hounds are daemons that appear as hounds, dogs, or wolves with black
fur, glowing red eyes, and often a translucent black fog, or hue surrounding
their bodies. They are an integral part of the \nameref{sec:Old Ways}, where
they are regarded as servants of \hyperref[sec:Morana]{lady death}. Black
Hounds appear to those close to death, and those who pray for release through
death.

These harbingers of death appear all across Aror, and symbolise death in many
cultures around the planet. ``Whistling for the hound'' has thus become an
idiom across Aror for inviting death into one's life. Like wise ``defeating
the hound'' has become an idiom for defeating, or narrowly escaping death.

They appear to all those who profess a sincere wish for death, especially
those that are beyond a cure, and would needlessly suffer at the hands of
their terminal disease, or fatal wounds. Black hounds have the ability to
remain invisible to all but a select few individuals at any given time, and
use this ability to appear only to those who have called them should a crowd
be present. Black hounds are intelligent, and can understand human language,
but never speak. They will never kill anyone out of malice, they do not judge
the living, and only kill those that explicitly ask to be released. The hounds
might also appear, and give the dying comfort so that they may not draw their
last breath alone.

\begin{35e}{Black Hounds}
  Black Hounds are intelligent dog-like daemons that are \emph{neutral} in
  alignment. They can be reasoned with, and may even become companions of
  the living.
\end{35e}
