\subsection{Deepkin}
\label{sec:Deepkin}

\aren{I had the misfortune of seeing my people's decline with my own eyes.
I was powerless, and unable to stop it. We are but a shadow of our former
selves...}

\graham{But still you live. And once the time is right, you may reclaim what
once was.}

The \emph{deepkin} are the cavern dwelling cousins of humans. They are capable
of seeing in the dark (albeit without perceiving colour), and often have white
pale skin, red to brownish hair, and either red, green, blue or yellow eyes.

Deepkin society is one of the older societies on \emph{Aror}, with a long
standing history in the arcane arts, building magnificent underground cities,
libraries and workshops. Ancient deepkin were master arcane smiths, golem
constructors, inventor of many magic based constructs and technology still
used today.

The ancient deepkin had their dominance challenged by the other races of the
deep, namely the dwarves, dark elves, and a now almost extinct species called
the \nameref{sec:Ilians}. Hundreds of years of conflicts lead to the decline
of most of their impressive civilisations, with one exception. Instead of
perishing however, most of them fled to the surface, where they were warmly
received by their surface cousins. Nowadays deepkin culture is but a shadow of
what it was, although they still try to reclaim what was once theirs with
expeditions into the deep. Albeit they were well known city and kingdom
builders, only one deepkin settlement rose to the rank of a formidable city
kingdom: \emph{Stenheim}.

Although deepkin are treated as their own race, they are still capable of
producing viable offspring with normal humans. The race of the offspring is
always that of the mother, due to the dominant genetic traits of the deepkin.

\begin{35e}{Deepkin Traits}
  \hyperref[sec:Speak Language]{Doresh} is the natural language of the
  Deepkin, and is equivalent to \emph{Undercommon}.

  \begin{itemize}[noitemsep]
    \item Medium: as medium creatures, \emph{Deepkin} have no special bonuses or
    penalties due to their size.
    \item \emph{Deepkin} base land speed is 30 ft.
    \item For all manners regarding racial restrictions or classifications
    \emph{Deepkin} count as humans.
    \item Dark vision out to 120 feet, but colour blind as a result.
    \item Bonus Feat: Just as their human cousins, \emph{Deepkin} can choose a
    bonus feat at first level.
    \item Automatic languages: Doresh, Teranim. Bonus Languages: Any (except
      secret languages)
    \item Favoured Class: Any. When determining whether a multi class takes an
    experience point penalty, his or her highest-level class does not count.
  \end{itemize}
\end{35e}
