\subsection{Demons}
\label{sec:Demons}

Demons are the hellish abominations spawned by the \nameref{sec:Scourge} on
the plane called the \nameref{sec:Abyss}. Since the scourge of the abyss had
ample time to absorb a variety of species, including humanoids, animals, giants,
and even dragons, it is capable of creating a wide variety of different species
and creatures.

Demons serve a wide variety of functions in the abyss, but the most important
are the acquisition of new food in the form of biological matter, biological
blueprints, and the defence of the abyss itself. Many demons are intelligent,
but do not have their own free will, as the scourge of the abyss controls them
even across the vast distances of different planes. All demons have inherent
psionic abilities, which they use in combat and to communicate with their host
scourge.

The scourge of the abyss is capable of sending its demons to other planes
through psionic teleportation. It does so regularly to scout new locations for
starting a new colony, to send out hunting parties, and to fight its enemies.
The scourge of the abyss also grants spell-like abilities to its demons, so
that make them more deadly during fights, or by granting them special
abilities such as teleportation.

\emph{Dretches} are small, horribly deformed vaguely humanoid creatures that
lump about the abyss. They are the scourge's eyes and ears, allowing it to
see what is happening on its surface. It also uses the dretches as a first
line of defence, trying to attack any intruders by spawning swarms of
Dretches. Dretches are often horribly disfigured, with an odd number of legs
of varying lengths and body features that are out of proportion to the rest of
its physique. \emph{Quasits} are dretches with wings that the scourge uses as
winged scouts.

\emph{Babau} are vaguely humanoid creatures, with sharp teeth and claws that
are swift and quick hunters that the scourge uses to hunt down and kill
prey. Babau then take the prey back to the scourge so that they can be
devoured and eaten. They work together with \emph{vrocks} which are winged
vulture like creatures that roam the skies of the abyss looking down for prey.

The \emph{succubus} is a female humanoid creature, capable of mammalian
reproduction that the scourge spawned for the sole purpose of collecting new
biological blueprints. The \emph{incubus} does the same, but has male
reproductive organs instead. The scourge sends these out to other planes
so that they may mate and reproduce with other humanoid creatures. They
then return with their offspring to add them to the scourges ever growing
library of biological blueprints. Since the scourge has no concept of beauty,
succubi and incubi are often horrendously deformed and disfigured, and must
thus use violence to achieve their goals.

A \emph{Tjort} is an abomination with a tail, goat legs, and a male humanoid
upper torso.  With its raw and brutal strength it destroys anything that
stands in its way, and is used by the scourge mainly as a first line of
defence, or shock attack trooper. With its goat-like legs it is a capable
jumper, climber as well as sprinter. An \emph{Onoskelis} is similar in
appearance and function, but has a female upper and lower torso, goat like
legs for climbing and jumping, and mammalian reproductive organs. Both have a
huge mouth with sharp teeth they use as weapons. Both the Tjort and the
Onoskelis are blind, and thus hunt by sound, scent and by feeling vibrations
in the scourge's surface.

\emph{Bebilith} are spider like creatures that the scourge spawns as advanced
scouts, to kill stray demons or that have served their purpose. The bebilith
is also responsible for hunting other life forms, and taking them back to the
abyss. The scourge also spawns a bigger version, called the \emph{retriever}
which main purpose is to hunt and kill pray on different planes, alongside
recapturing stray demons. These spiders will capture creatures on other planes,
and simply send them to the abyss. There, other daemons, such as succubi,
babau and vrocks do the actual killing, so that the scourge may consume them.

As a form of self reproduction it spawns \emph{hezrous} and \emph{nalfeshnees}
whose sole purpose is to carry a scourge seed to other planes and planting
it there. These creatures are capable of defending themselves and the seed
by being capable fighters and by leading lesser demons to protect them. Once
these creatures have found a good spot to plant the scourge seed, they will
lie down, die and serve as nourishment for the new scourge colony.

Ever since the scourge of the abyss came under attack by powerful creatures,
such as \nameref{sec:Aurelis} and \nameref{sec:Devils}, it has begun spawning
huge and powerful demons of its own to defend itself. One of these is the
\emph{glabrezu}, with bone scales for natural armour and sharp bone like
scissors as weapons. Another is the \emph{marilith} a hybrid of a snake and
a female upper torso with six arms in which it wields bone weapons to fight
any intruders that may harm the scourge. The most powerful daemon is called
\emph{balor}, a large hulking beast that combines all the most deadly and
dangerous abilities the scourge in one hellish abomination.

\begin{35e}{Demons}
  All demons are \emph{chaotic evil}, but have no free will. They
  have no \emph{intelligence} score, but their \emph{wisdom} score to allows
  them to follow the instinct the scourge gives them. Without orders or direct
  link they are savage, animistic creatures attacking anyone, even their own
  kind. Even though they are not intelligent, the fact that a chaotic evil
  entity controls them, makes them chaotic evil.

  The scourge, and its demons do not make deals, and will not negotiate.
\end{35e}
