\subsection{Devils}
\label{sec:Devils}

Devils, or ``pacru'i'' (draconic for ``devil'' or ``evil spirit''), are a race
of monstrous creatures that descent from the original
\hyperref[sec:Demons]{demons} that attacked \nameref{sec:Aurelis}. The Aurelis
freed some of the demons from their psionic overlord the \nameref{sec:Scourge}
of the Abyss, giving them their own will and freedom. Since most of them can
no longer communicate through the psionic might of the scourge, devil's have
developed their own language called ``Aranai''.

After refusing to aid the Aurelis in their war, the devils have since
retreated to their own planet called \nameref{sec:Hell}. There they began to
establish their own society. Within devil society the most powerful and strong
rule, and the weaker devils are mercilessly oppressed through violence and
terror. Devils live in a strict hierarchy of power and must obey their superiors
without question, or fear being charged, trialled, and then face a punishment
that befits the crime. The tyrannical nature of devil society is often
presented as a negative example on how to structure a society, as it rewards
the ruthlessness, while suppressing and stifling skill and talent.

Because of the process that freed them from the enslavement of the scourge,
they have lost all their psionic powers, and now rely on arcane magic for
their technology and sciences. Since they are the youngest of the races, they
often offer their services through deals to other races in exchange for
magical artefacts or knowledge. Devils are known to be devious, intelligent,
but often quite blunt and honest in their dealings. Their expertise in crafting
\nameref{sec:Implants} infused with arcane energy is second to none, and they
use these implants to protect themselves from the scourge, enhance their
combat capabilities, as well as a currency for trade, and barter.

Nevertheless the devils have had ample time to tinker with their own
physiology. While some devils still remain similar to their original demon
form (such as succubi), while some have been changed drastically. The scourge
seed carriers have been exterminated, and new devils have been breed or
engineered to complement the legions of hell, such as the
\hyperref[sec:Tieflings]{tieflings}. They also bolster their ranks with
corrupted creatures of other realms, for example \emph{erinyes} which are
corrupted, broken or brainwashed \nameref{sec:Aurelis}. The devils further
changed themselves physiologically to be resistant to heat and direct contact
to fire. In their society fire holds an important cultural and ideological
significance, as the scourge of the Abyss - their dreaded enemy - is mortally
afraid of it.

Since the devils are the descendants of the various creatures that the Scourge
produced to invade Aurelis, there exists a wide variety of types of devils,
with a plethora of sub races. Some have a humanoid figure, while others are
mere beasts. And while some are intelligent, others are truly nothing more
than beasts. Even though no devil is truly like the next, there are some
distinct groups of devils that share similar physique, traits, and
characteristics.

\subsubsecton{Succubi and Incubi}

Among the most intelligent, and cunning are the succubi and incubi. They
descend from the Onoskelis, and Tjorts who are among the Scourge's most
intelligent, cunning, and long-lived creations. An incubus or succubus can
become up to 600 Arorian years old. Although their demonic ancestors used
their cunning to hunt and stalk prey, the succubi and incubi have used their
gifts to move themselves into positions of power within the devil society.  As
with many devils, they come in varying shades of skin, eye, and hair colours
(often featuring multiple colours at once), and although their appearance is
always vaguely humanoid their bodily shapes can vary significantly. Almost all
them have horns, and the vast majority also retain the goat hoofs of their
ancestors. Many succubi and incubi are winged, but most of them are restricted
to gliding instead of being able to fly. They can be found in most
stratospheres of demon society, from the lowly worker and soldier, all the way
up to being the right hand of Baphomet himself.

\begin{35e}{Succubus}
  The following traits apply to a succubus (female), as well as to the incubus
  (male):
  \begin{itemize}[noitemsep]
  \item Succubus and incubus are medium monstrous humanoids (or outsiders), with
    a speed of 30 ft.
  \item They gain a +4 bonus to Intelligence, and Charisma, and +2 bonus to
    wisdom, but take a -2 penalty to Strength and Constitution.
  \item Some have wings, which gives them a 30 ft. speed fly (good), as long
    as they wear light armour or just clothing. This bumps their level adjustment
    to +2.
  \item Succubus and Incubi have no preferred class.
  \item Automatic Languages: Aranai, Teranim
  \item Alignment: Any
  \item Level Adjustment: +1 (+2 if they have wings)
  \end{itemize}
\end{35e}

\subsubsection{Baphomet}
\label{sec:Baphomet}

The layers of hell are ruled by a devil called \emph{Baphomet}. It is a devil
of unknown pedigree, having the lower torso of a male humanoid, the upper torso
of a female humanoid, and the head of a goat with two mighty horns. On its
forehead rests a third eye.

Baphomet is extremely intelligent, and an exceptionally powerful psyker. Many
believe that his power is only second to the \nameref{sec:Scourge} itself. The
dogma of the church of Baphomet state that the early years of the layers were
of chaos, fear, and tumult. The devils were afraid that of the scourge's many
attempts to invade their home to enslave its wayward children once more. The
layers had no structure, no order, and devil fought devil in an attempt assert
dominance, and to gain power over the newly formed nation. Within this chaos
Baphomet simply sat down on the floor, and began to meditate. In its
meditative trance Baphomet used its psionic powers to warn the devils of
impending scourge incursions, and telepathically coordinated the devil's
defences. Baphomets brought order, structure, and above all, security and
stability to the layers.

And just as Baphomet ruled then, he rules now. Baphomet still sits in the
deepest layers of \nameref{sec:Hell}, called the sanctum, and meditates to
this day. She watches over the scourge's activities and her realm both, and
leads the latter by telepathically guiding the devils. Baphomets word is
considered law, and his teachings became dogma for an entire church and
religion has formed to worship him. Baphomet is served by an ever growing
cadre of devil priests, warriors, and aids who carry out her will, both within
and beyond the layers of hell.

In recent centuries Baphomet's power and influence are waning, as the magical
implants that block the scourge's power have become widespread and more
effective. Baphomet is still considered a Machiavellian tactician without
peer, and his psionic powers are without equal within the layers.

\graham{Aren and Baphomet should get along fabulously.}

\begin{35e}
  Baphomet is considered \emph{lawful evil}, and can be worshipped as a
  deity by devils, where its domains are Strength, War, Knowledge and
  Tyranny. Baphomet does not make deals with non-devils, and does not
  accept them as followers.
\end{35e}

\subsubsection{Lilith}

\nameref{sec:Lilith}, often called the \emph{scarlet whore}, rules over the
\nameref{sec:Hells Surface}. She rules over several legions of devils, and
fallen \hyperref[sec:Aurelis]{aurelis} that are called \emph{erinyes}. She is
only interested in striking deals with powerful mortals, and will thus tempt
kings, lords, arch mages and rich business owners. Lilith has converted parts
of the surface into a den of luxury, and debauchery for that very purpose.
Lilith has a female succubus called \emph{Eris} as a familiar, and closest
ally. Lilith rarely speaks to anyone directly, instead sending her succubi and
incubi to make deals. Due to her rule over the surface of hell, she is also
partially responsible for defending the layers of hell from outside
attacks. Along with Belial she is one of the most powerful generals that rule
the layers of hell.

\subsubsection{Asmoday}
\label{sec:Asmoday}

\emph{Asmoday} is the hellish treasurer, and rules over a layer of hell aptly
named the \nameref{sec:Treasury}. He is responsible for retrieving,
cataloguing and studying arcane artefacts for their power. He does not deal
with mortals, and prefers to outsource the retrieval of artefacts to other
generals instead. It is believed that the vault of Asmoday contains untold
treasures and artefacts of immense power. He is an immortal tiefling himself,
and the first born of Lilith. Asmoday himself is mostly interested in
procuring, studying and creating artefacts to further the military might of
the layers of hell. Rumours persist that Asmoday has been tasked by Baphomet
himself to procure arcane technology that shields the layers of hell from
extra-planar teleportation, and thus from demonic invasion. Asmoday has two
apprentices: Forneus and Ishtar. Asmoday is also responsible for inventing the
\hyperref[sec:Implants]{arcane and divine implants} that devils use to modify
their bodies and abilities.

\subsubsection{Forneus}

His first apprentice is another powerful tiefling called
\nameref{sec:Forneus}, who uses the knowledge that he gained from Asmoday to
strike deals with mortals. He prides himself in making fair deals, and is very
well know to be true to his word. Forneus is also the patron of arcane
research among mortals, as well as devils and oversees various research
projects and the spread of arcane literacy among devils.

\subsubsection{Ishtar}

The other is a female wingless succubus called \nameref{sec:Ishtar} (or
\emph{Inanna}). She is mainly responsible for using the knowledge gained by
Asmoday to free other demons from the scourge's influence. She is also
responsible for returning magical powers that were lost when the telepathic
link to the scourge was broken by surgically implanting devils with arcane
artefacts.  Ishtar further performs plastic surgery to repair bodily defects
of freed demons, as the scourge cared little about proper bodily proportion or
a sense of beauty. She is also an apt healer, surgeon and promotes and
furthers medical research.

\subsubsection{Belial}
\label{sec:Belial}

\emph{Belial} is the main commander of the armies of hell, and ruler of the
\nameref{sec:Forest}. As a horned devil and the left hand of Baphomet, he
outranks and commands all the lesser forces of hell, such as the armies of
bearded, chain and bone devils, as well as several legions of orthons. He is
responsible for the defence of hell, as well as fighting the layers many
enemies, such as the \nameref{sec:Aurelis} and the \nameref{sec:Demons}.

\subsubsection{Runemaster}

The \nameref{sec:Runemaster} is a \emph{remmanon} (a large, horned, humanoid
devil) that gives out power in the form of soul magic runes in exchange for
worship. He does not command any legions of hell, but has a high standing due
to his skill in making deals with mortals. His deals are further detailed in
another section of this book.

\subsubsection{Beleth}
\label{sec:Beleth}

\nameref{sec:monster:Beleth} is a succubus that prefers to use a female
humanoid form. She is responsible for striking deals with mortals, and is
known for being cunning, intelligent, ruthless but also fair and honest. She
strikes deals with mortals for powerful artefacts and knowledge, and offers
the services of hell in exchange. She, and her legions of succubi and incubi
negotiators also offer services as neutral arbitrators, councillors and
lawyers. As Baphomets personal aide, right hand woman, and spokesperson she is
considered the most powerful among all generals. Beleth enjoys providing legal
council to evil mortals that have been caught by the authorities. She exploits
their precarious situation to strike deals, but she also enjoys defeating the
forces of justice in legal proceedings. Beleth rarely fights physically,
preferring to use guile, cunning, and a silver tongue to win battles.

\begin{35e}{Devils}
  Devil society is \emph{lawful evil} as a whole, but devils may be of any
  alignment. Succubus and incubi, also exist among devils, as all devils are
  mere descendants of demons.
\end{35e}
