\subsection{Diarim}
\label{sec:Diarim}

\aren{The expression ``explaining freedom to a Diarim'' has become ingrained
  in many cultures as a metaphor for a fruitless labour.}

The \emph{Diarim} are a race of humanoid creatures that were bred for specific
tasks by the the giants living on the continent of \nameref{sec:Farlar}. They
are the youngest of the races on \emph{Aror}, and are a mixture of various
other humanoid races.

Diarim come in in as many shapes and sizes as the giants had uses and tasks
for their engineered slave race. But most share a common set of features: the
light, fair skin (almost white) of the \hyperref[sec:Deepkin]{Deepkin}, blue
hair of the \hyperref[sec:Snow Elves]{snow elves}, and an ingrained sense of
duty and loyalty to strict hierarchies from the dwarves. Almost all have blue
tribal tattoos all over their body, which identify the current and past owners
of the individual diarim. Diarim live up to 50 years, with many not able capable
of living past 30.

Very few diarim ever escape the slavery of their masters. The biological
engineering, and an ingrained culture of servitude and strong sense of
community keeps them complacent and confined within the giant culture. Diarim
were engineered to serve, do heavy labour and die as warriors on battlefields,
and thus often only strife in societies strongly leaning towards
collectivism. Diarim also all have a strong sense of order ingrained in them,
and they are often psychologically compelled to bring order into chaos,
reorganise, optimise or simply clean spaces they deem dirty, filthy or to be
in disarray. Most diarim have no names. They never refer to themselves with
names, and are only being given a names by the giants if they have
distinguished themselves, either through heroic deeds, or through crimes.

The most common variant are labourers, small but stout breed, that was created
by introducing more dwarven heritage into the diarim. They excel at physical
labour, such as mining and construction. Siegers were bread with monstrous
races, often even giants, and are used as front line soldiers, gladiators and
shock troops. They are larger than any other diarim, and often also serve as
overseers over other Diarim. Exciters were bred and selected for their beauty,
and are priced possessions to be traded and gifted to other giants. Their
primary role is to entertain their overlords through song, dance and company.
Exciters are also diplomats to other humanoid or monstrous nations and parties.

In the recent decades more and more diarim have escaped the continent of
Farlar and joined the other humanoid races. The giants had to learn that you
cannot suppress the curiosity, love for wandering and freedom for long when
you create a species based on humans, halflings and elves.

\begin{35e}{Diarim Traits}
  \textbf{Diarim Traits (EX)}:
  \begin{itemize}[noitemsep]
    \item Medium: as medium creatures, diarim have no special bonuses or
    penalties due to their size.
    \item A diarim's base land speed is 30 ft.
    \item \textbf{Weak Will (EX)}: All diarim have a -2 penalty to will
    saves against charms and similar effects.
    \item Automatic languages: Giant, Teranim
    \item Favoured Class: Any. When determining whether a multi class takes an
    experience point penalty, his or her highest-level class does not count.
  \end{itemize}

  \textbf{Sieger Traits (EX)}: the following traits are in \emph{addition} to
  the diarim traits, except when noted otherwise.
  \begin{itemize}[noitemsep]
    \item Large size. -1 penalty to Armour Class, -1 penalty on attack rolls,
    -4 penalty on Hide checks, +4 bonus on grapple checks, lifting and
    carrying limits double those of Medium characters.
    \item Space/Reach: 10 feet/5 feet
    \item +8 Strength, -2 Intelligence, -2 Charisma, -2 Wisdom
    \item Favoured Class: Barbarian
    \item Level Adjustment: +1
  \end{itemize}

  \textbf{Exciter Traits (EX)}: the following traits are in \emph{addition} to
  the diarim traits, except when noted otherwise.
  \begin{itemize}[noitemsep]
    \item -2 Strength, -2 Constitution, +4 Charisma
    \item Favoured Class: Bard, Sorcerer
  \end{itemize}
\end{35e}
