\subsection{Dwarves}
\label{sec:Dwarves}

\emph{Dwarves} are natural fighters, miners and smiths. Among all of the races
they are the most reclusive of all. Dwarves usually stand between 1.2 and 1.4
metres high, but are on average almost has heavy as humans. They often live
up to 250 years. Their skin is usually tan brown, their skin ranges from brown
to black, and they often have brown eyes to match. For most male dwarves the
beard is a symbol of status, and often stands as a symbol for that particular
dwarves caste within the clan. Female dwarves do the same, but with their
head hair.

\subsubsection*{Dwarven Culture}

They hardly join other cultures, and prefer to continue to live like their
ancestors did. \emph{Dwarves} organise themselves into huge clans or families
and live in deep caverns or mountains in a strict caste society. Those that do
not fit into these strict frameworks of societies are cast out, and then look
for other realms to live. Ever since the deep have become ever more dangerous
many smaller dwarven clans have fled the surface near human or elven
settlements, while others have seemingly integrated into the large city
kingdoms. Offering their expertise on trade and smithing to the other races.

Dwarves speak their own language called \emph{Rutari} with its own alphabet of
the same name.

\subsubsection*{Caste System}

Most dwarven clans strictly enforce their caste society to maintain order and
control within their societies. Anyone who does not fit within this system is
met with suspicion, contempt or exclusion and exile at the worst. The lowest
of the caste are slaves, which are drawn from the pool of criminals among the
dwarves, as well as from the other races that live within the dwarven society.
Other races, such as humans, elves, or even \emph{gnomes}, often have no chance
to advance out of the slave caste. Most dwarven clans however allow visitors
into their strongholds.

\begin{35e}{Dwarf Traits}
  \begin{itemize}[noitemsep]
    \item Medium: As Medium creatures, dwarves have no special bonuses or
      penalties due to their size.
    \item Dwarf base land speed is 20 feet. However, dwarves can move at this
      speed even when wearing medium or heavy armor or when carrying a medium or
      heavy load (unlike other creatures, whose speed is reduced in such
      situations).
    \item Dwarves are sturdy and hardy, and thus have a +2 racial bonus to
      constitution.
    \item Stability: A dwarf gains a +4 bonus on ability checks made to resist
      being bull rushed or tripped when standing on the ground (but not when
      climbing, flying, riding, or otherwise not standing firmly on the
      ground).
    \item Languages: Rutari, Teranim. Bonus Languages: Any (except secret
      languages)
    \item Favoured Class: Any. When determining whether a multi class takes an
          experience point penalty, his or her highest-level class does not
          count.
  \end{itemize}
\end{35e}
