\subsubsection{Fey}
\label{sec:Fey}

Fey are magical and evil forest spirits that were created by the earliest druids
to protect nature from destruction. During the \nameref{sec:Aeon of Strife},
both monstrous and humanoid culture uprooted forests, cleared grassland, dried
marshland or outright destroyed or corrupted nature to fuel their war
machinery and ever growing populations.

Druids, from both sides of the war, desperate to preserve nature created
forest spirits that should serve as protectors to nature. But after the druids
realised that the gentle spirits they had created proofed ineffective in
deterring the humanoid and monstrous loggers, they used necromancy to corrupt
these spirits into evil and sadistic creatures.

The fey are now universally hated and feared, and are often the cause for
great disasters, tragedies and destruction in both humanoid and monstrous
villages and communities. Their madness has clouded their judgement, and fey
attack anyone who ventures into their forests, even druids.

The most common fey are \emph{red caps}, small vicious and sadistic
human-like creatures that hunt and murder for nourishment.

\emph{Dryads} attack loggers and travellers that seek the shade of the tree
they are meant to protect. They feast upon living flesh, and sacrifice all
those they catch to the very tree they inhabit.

\emph{Nymphs} and \emph{Irrlichter} seek to lure people into a marshy death by
luring them into the forest with illusions.

\emph{Satyrs} were made to emulate the tribal patterns of the humanoid and
monstrous races and build their own villages. From there, they venture forth
to raid and pillage other villages and towns. They are capable of forging
steel, and are expert hunters and trackers. They are often aided by evil
\emph{sprites} and \emph{pixies}, that support the satyrs with their inherent
magical abilities.

\begin{35e}{Fey}
  Everblack fey do not vanish upon death, they simply die like any other
  mortal creature. All fey that are \emph{good}, move their alignment towards
  \emph{evil}. Most of them either serve druids unwillingly, or roam the
  forests, plains and mountains seeking wreak havoc on the monstrous and
  humanoid creatures alike.

  An \emph{Irrlicht} has the same statistics as a will-o-wisp, but are of
  type \emph{Fey} instead.
\end{35e}
