\subsubsection{Gargoyles}
\label{sec:Gargoyles}

Gargoyles are justice daemons closely associated with the \nameref{sec:Order}.
To summon a Gargoyle one must carve a near human figure out of stone or wood,
and then give it live through an ancient soul magic
\hyperref[sec:Rituals]{ritual}. If the ritual is successful then the inanimate
statue will come to live, and either serve as a judge in disputes, or will
answer questions regarding law and order. Once its task has been fulfilled it
will turn into a lifeless statue again. They are an integral part of justice
in many lands across Aror, usually summoned to be a neutral arbiter in cases
where no clear fault or no clear perpetrator can be established.

If it is asked to serve as arbiter the gargoyle will require the agreement of
both parties that they accept the daemons judgement. If both parties agree,
then the daemons judgement is binding under the threat of violence. The daemon
will then hear both sides of the case, allowing for evidence and witnesses to
be presented before making its final verdict. Judgements passed by gargoyles
are notorious for being equally detrimental for both parties involved. For
example, a gargoyle was once arbiter in a custody dispute where apparently all
involved used lies and deceit to decry one another as unfit parents. Instead of
choosing one of the parties involved, the daemon sent the child to distant
relative instead, claiming that any parent willing to use deceit would make an
improper role model. In another case a gargoyle was conjured to settle a
dispute between two barons who both claimed ownership over a fertile strip of
land. Instead of choosing one party over the other, the gargoyle decided to
return the land to nature. The daemon then requested to be moved there as a
statue, and attacked everyone who dared to work the land illegally. Gargoyles
understand the concept of innocence (i.e. innocent until proven guilty), and
are take local differences in penal codes and law into consideration when
passing judgement.

Once a gargoyle has served its purpose, it will often ask to be destroyed so
that its soul may return the \hyperref[sec:Soul Well]{soul well}. But sometimes
it will request to remain intact, often to uphold a ruling it has made. Some
Gargoyles guard certain areas, items, or structures to this day, even though
the ruling surrounding this guardianship has long since been forgotten.

\begin{35e}{Gargoyle}
  A gargoyle is always some variation of \emph{lawful}, but most are
  \emph{lawful neutral}. They change their type to daemon, gain a +5 bonus to
  wisdom, and gain three new spell like abilities: \emph{Detect Alignment},
  \emph{Zone of Truth}, and \emph{Detect Thoughts}. Its main casting ability
  for these spell like abilities is wisdom.
\end{35e}
