\subsection{Giants}
\label{sec:Giants}

\aren{The most deadly force allowed to roam free on Aror.}

Giants are humanoid-like species that combine great strength, size, intellect
with a vicious mentality for conquering that allow them to destroy anything and
anyone that gets in their way.

Not native to Aror itself, the giants arrived in \emph{MI:1920} to the continent
of \nameref{sec:Farlar} from an unknown plane. Giants share a bloody and violent
history on other planes with \nameref{sec:Dragons}, and have thus invaded the
world in an attempt to destroy the dragon clan that has settled on
\nameref{sec:Draigynus}.

Aeons ago large clan of dragons once ruled the native home plane of the
giants, subjugating, controlling and oppressing the giants. The dragons used
the giants as soldiers in a war against daemons, and as menial labourers to
create powerful arcane artefacts and defences. The giants rebelled, killing
most of their dragon overlords, and shifting their own newly formed society
towards war, violence and a deeply ingrained hatred towards the dragons. Their
home was destroyed in the violent revolution, and now the giants roam the
habitable planes in an endless conquest to make the dragons pay for their
misdeeds.

To them it no longer matters whether a dragon was actually involved in the
subjugation of their own race. Stopping history from repeating itself by all
means necessary has become a cultural and societal obligation.

They have a reputation for being strong, violent, and highly intelligent.
Giants are expert tacticians, warriors and wielders of the arcane arts. They
rival the dragons themselves in expertise on crafting and creating arcane
weaponry, machinery and artefacts. Although an individual giant is no match
for an adult dragon, they make up their individual weakness with careful
planning and preparation in their assaults.

Although several species of giants exist (such as the shorter fire giants, or
the taller storm giants) these differences are overlooked within giant society.
They are united by two main causes: conquering new lands, and defeating their
old enemies the dragons.

Giants are expert arcane wielders, are known to be the creators of several
sentient species such as the \nameref{sec:Diarim}. Early history alludes to
the possibility that the giants arrived on Aror aeons ago in their search for
dragons, but found none. Nevertheless they settled the continents of
\nameref{sec:Eilean Mor} and \nameref{sec:Iafandir}, and were responsible for
creating some of the monstrous humanoid species such as trolls and ogres.

The giants that arrived on \nameref{sec:Farlar} were responsible for the
destruction of \emph{Nen-Hilith} the city of the elves and halfings. They are
slavers, warriors but fight only those that would join their war on the side
of the dragons.

\begin{35e}{Giants}
  All giant races (except for hill giants) gain +4 intelligence, and prefer to
  become fighters and wizards. Overall their society could be considered
  \emph{chaotic neutral} as they will consider any method viable that aids them
  in their war.
\end{35e}
