\subsection{Gnolls}
\label{sec:Gnolls}

\emph{Gnolls} are a monstrous race, half-humanoid, half-hyena, that live in the
deserts of \nameref{sec:Arania}, and \nameref{sec:Goban}.

Gnolls are deeply spiritual folk, often following either an evil interpretation
of \nameref{sec:Forun}, which they call \emph{Wa'het}. Gnolls are often lead by
the wises high priestess of the tribe. They believe that the fires that Wa'het
sends are meant to test, scar, challenge and destroy those that are either too
corrupt or too weak to face her face trials. Thus most gnoll tribes hold
failure, cowardice and weakness as grave sins. They respect those that hold
wisdom, tradition and braveness as virtues.

Even though gnolls are nomadic by nature, they are the only monstrous race to
hold a city that rivals the great city kingdoms of Aror. In \emph{MI:1213} the
city kingdom of \nameref{sec:Esmayar} fell to gnoll raiders, and has sinced
flourished as a gnoll kingdom.

Smaller packs of gnolls, lead by a high priestess still roam the vast deserts,
where they often avoid direct conflict with the other races. The nomadic gnolls
avoid senseless slaughter and war, only taking what they absolutely require
to survive. Since this stands in stark contrast with the gnolls that raided
the city kingdom of Esmayar, scholars are still debating to this day what
motivated them to raid the city.

\begin{35e}{Gnolls}
  The gnolls of Esmayar have established a brutal tyranny and slaving nation
  that is considered \emph{lawful evil}.

  Nomadic gnolls are often considered \emph{chaotic neutral}, living free and
  unbound in the vast deserts. They might raid villages and other nomads, or
  might parley and trade in peace.
\end{35e}
