\subsection{Gorgons}
\label{sec:Gorgons}

\emph{Gorgons} are a half-breed between any of the three medusa races, and a
humanoid father. Since medusa have no males, they must rely on other monstrous
or humanoid races to reproduce. Even though most of the time the result is a
pure-breed medusa, the union between humanoids and medusa may also spawn a
half-breed.

Much like their mothers' race, gorgons are a female-only species. They
inherit their humanoid appearance - such as physique, build, skin, hair or eye
colour - from their father, but gain certain traits from their mothers. Just
like medusas, gorgons have small snakes instead of hair. Areas where the skin
on humanoids is harder and tougher - like on the elbows and knees - Gorgons
have patches of reptile scales instead. From afar a gorgon passes as normal
humanoid female. Many gorgons hide their ``hair'' with clothing or even
disguise spells to pass as humanoids.

They inherit the ability to turn people into stone from their mothers, but
the power of the effect is weaker. Still gorgons must actively avoid looking
other people in the eyes or risk turning them to stone permanently. Any other
special traits (such as wings, another set of arms etc.) are not passed down
to Gorgons.

There are two main variants of Gorgons: The most common variant has the heads
of snakes as hair, while the others have the tails of snakes as hair. The
snakes and the gorgon live in a symbiosis together, and a Gorgon can feel,
sense, and hurt as if the snakes were limbs. Those gorgons with snake heads
can also perceive the world through the eyes of the snakes. They do not
directly see through the eyes of their snakes, but the snakes make them
indirectly aware of their surroundings. A snake's bite is not venomous, and
they also reflect the gorgons mood and feelings. Anyone who knows a gorgon
well can deduce the mood from the snakes' behaviour, even if she tries to hide
it her true feelings. Those gorgons with snake tails have fine motor control
over their ``hair'', and can use them to carry, use and manipulate light
objects on a fine scale.

Gorgons almost always leave medusa society, and try to integrate into the
societies of the father's side. They then often attempt to fit in with the
societies of humanoids, but are met there with superstition and fear. Many
gorgons grow up in humanoid societies, and thus share many aspects, values and
traits of the culture they grew up in. Generally gorgons are known to be kind,
adventurous, open minded, as well as excellent scholars, bards and wielders of
the arcane arts. Still many societies do not allow Gorgons, or only those that
cover their eyes, out of fear of the damage they might inflict on others.

\aren{No one can be blamed really, since it is a humanoid instinct to look
  each other into the eyes.}
\graham{True, but still a lot of damage is done if someone's turned to stone
  in a position that is unbalanced, and causes the statue to fall over.}

\begin{35e}{Gorgon Traits}
  Gorgons speak Teranim, and whatever additional languages their culture and
  background provides.

  \begin{itemize}[noitemsep]
    \item Medium: As Medium creatures, Gorgons have no special bonuses or
      penalties due to their size.
    \item Medusa Heritage (EX): Gorgons are a female only species.
    \item Gorgons inherit their beauty and expressive personality from their
      mothers, giving them a +2 bonus to charisma.
    \item Snake Vision (EX): A gorgon with snake heads as hair can perceive
      the world even if it has been blinded. She can see and detect shapes,
      movement as well as smaller details giving her \emph{Blindsense (30
        ft.)}.
    %% Mirdon would be proud
    \item Snake Hands (EX): A gorgon with snake tails as hair can use their
      hair as an extra limb to wield, manipulate, or use small objects, such
      as wands, light weapons, or other smaller items. These snakes can also
      be used for somatic components of spells. All snakes together are
      required for these tasks, and thus the entire ``hair'' counts as one
      limb.
    \item Petrifying Gaze (SU): Turn to stone permanently, 30 feet, Fortitude
      DC 12 negates. The save DC is Charisma-based.
    \item Level Adjustment: +1
  \end{itemize}
\end{35e}
