\subsection{Halflings}
\label{sec:Halflings}

Halflings are small, often barely reaching one metre. What they lack in
strength and constitution, they make up dexterity and curiosity.

Most of the halflings are nomads, who travel across the lands in search for
places to explore and discover. If you think you have found a secluded spot on
\emph{Aror}, where no one else had sat foot before, you can be sure it is
already named after an halfling explorer. They travel in small families, and
in exchange for money or lodging, they offer their services to any small town
they come across on their travels. Halflings are curious, adventurous and
often find themselves exploring the depths and other inhospitable places of
\emph{Aror}.

A huge group of halfling families once decided to start another adventure:
their own kingdom. They settled down near an elven kingdom and named their new
kingdom \emph{Brèagha Hilith}. After decades of peaceful coexistence between
the two races, they finally decided to tear down the last barriers and simply
merge the two kingdoms into a new one: \nameref{sec:Nen-Hilith}. It became a
shining beacon of civilisation, artistry and stability under the known city
kingdoms of \emph{Aror}.

\aren{Until a few giants stepped on it...}

\begin{35e}{Halfling Traits}
  \begin{itemize}[noitemsep]
    \item Halflings have a +2 racial bonus to dexterity.
    \item Small: As a Small creature, a halfling gains a +1 size bonus to
    Armor Class, a +1 size bonus on attack rolls, and a +4 size bonus on Hide
    checks, but she uses smaller weapons than humans use, and her lifting and
    carrying limits are three-quarters of those of a Medium character.
    \item Halfling base land speed is 20 feet.
    \item Automatic Languages: Taavid, Teranim. Bonus languages: Any
    (except secret languages)
    \item Favoured Class: Any. When determining whether a multi class takes an
          experience point penalty, his or her highest-level class does not
          count.
  \end{itemize}
\end{35e}
