\subsection{Half-Elves}
\label{sec:Half-Elves}

The union of an \hyperref[sec:Elves]{elven} father and a
\hyperref[sec:Dwarves]{dwarven} mother produces a half breed called
\emph{half-elves}. They inherit their slender appearance from their elven
heritage, often looking beautiful, gracious and fair, and combine the
longevity of their elven and dwarven heritage to live up to 200 years. They
are well accepted by most cities and towns of the humanoid races, and often
use their elven appearance to take up jobs as entertainers, diplomats, traders
and bankers. They are known to be hard working, conscientious, intelligent and
crafty. Highly favourable traits they have gained from their dwarven
heritage. Much like with muls, the pregnancy of a half-elf can be dangerous
for the dwarven mother, sometimes leading to complications during birth. But
unlike muls, half-elves are not sterile as long as they reproduce with other
half elves.

Since very few half elves are ever born at any given time, a small but highly
dedicated community of half elves have arisen in most larger centres of
civilisation. These communities often aid and support any born half elf, even
though they rarely face any difficulties to begin with. Since the half elves
are born so rarely, and their trait is non-dominant (meaning that only the
union of two half elves produces another half elf), these communities openly
encourage marriage among their members to grow the community and the species
as a whole.

\begin{35e}{Half-Elf traits}
  The following items are in addition to the base 3.5e half-elf traits, as
  described in the d20 SRD.
  \begin{itemize}[noitemsep]
  \item Having gained the natural beauty and fairness of the elven heritage,
    they gain a +2 racial bonus to Charisma.
  \item They have inherited the craftiness of their elven parents and thus
    may select an additional \hyperref[sec:Background Feats]{background feat}
    at level 1.
  \end{itemize}
\end{35e}
