\subsection{Hobgoblins}
\label{sec:Hobgoblins}

\textbf{Hobgoblins} are among the most advanced of the monstrous races,
building small towns, fortified villages and even cities. They have a strict
society, culture and traditions that date back several hundred years.
To a hobgoblin personal honour is very important, and are in that regard very
similar to the \nameref{sec:Tynrikke}.

Hobgoblins are often lead by a warrior priest, who follow the
\nameref{sec:Three Kings}. Especially \emph{Karor} is considered the patron of
hobgoblins, as he sees his ideals and values played out within most hobgoblin
cities and baronies.

They are among the most warring tribes on Aror. Although they are engineers of
large societies and cities, they are also civilisation's greatest enemy. They
often besiege, raid, or outright destroy other civilisations to gain slaves,
food or resources vital for their own survival.

Hobgoblins are also notorious slavers and traders. And are known to trade
with both monstrous and humanoid races. They are well received as trading
partners, as their culture settled around personal honour forbids them from
breaking oaths and contracts. This means that hobgoblins are less likely to
walk back on any agreements that were made beforehand, compared to other races.

Smaller bands of hobgoblins often offer their services as mercenaries to other
races. Their services not cheap, but their loyalty, extensive military
training, and bravery have gained them a well deserved reputation as some of
the finest mercenaries and soldiers. So much so, that a group of hobgoblins
serves as the royal guard in \nameref{sec:Hraglund}.

Engineers of larger hobgoblin cities are famous for their complex, effective
but very expensive siege engines. These siege engines are either used by the
hobgoblins themselves to raid other tribes, or sold to other warring nations
and kingdoms.

\begin{35e}{Hobgoblin}
  Most Hobgoblin cultures will tend toward a \emph{lawful} alignment.
  Some, especially those that follow Karor's word to the letter, form
  tyrannical, duty and tradition bound societies that could be considered
  \emph{lawful evil}.
\end{35e}
