\subsection{Humans}
\label{sec:Humans}

\emph{Humans} are one of the most ancient humanoid races of \emph{Aror}, and
also the dominant race of the planet. Human artefacts have been found dating
back hundreds of thousands of years, far beyond the history of any other
humanoid species. There are two separate ``races'' of humans: those inhabiting
the southern part of the hemisphere who usually have darker skin, and the
``northerners'' who usually have fair skin. This distinction is superficial
only. Apart from the tone in skin colour, there is no other biological
difference between the various human tribes and civilisations. Humans live up
to 80 years, and are known for being statesmen, diplomats, farmers,
adventurers, explorers and scientists.

\subsubsection*{Language}

Humans speak \emph{Teranim}, either as their primary language, or as their
secondary language together with their local language. \emph{Teranim} has
become the de-facto language of \emph{Aror} and is usually spoken almost
everywhere, even among the beast races. \emph{Teranim} is written in its own
alphabet of the same name. \emph{Old Teranim} and \emph{Ancient Teranim} exist,
spoken by the ancient humans, and are the root of most other languages and
various local dialects. Although \emph{ancient teranim} is no longer actively
spoken, various books, poems, stories and songs still exist in that language.

Humans living in the southern hemisphere often speak a language that is
stuck halfway between old and new \emph{Teranim}, called \emph{Kalest}. While
the people of \emph{Forsby} (and surrounding regions) have their own distinct
dialect, which can be so hard to understand that it has received its own
classification and name: \emph{Reatham}.

Albeit many local dialects exist, almost all humans, and the other races
living with them are capable of speaking \emph{Teranim}. It is, after all,
the official language of many governments, the language that is printed and
used in official capacity as well as in inter-kingdom cultural exchange and
trade.

\begin{35e}{Common in Aror}
  The language of \emph{Teranim} is equal to \emph{Common} of D\&D. See also
  the \nameref{sec:Speak Language} section for a list of available languages
  and their alphabet.
\end{35e}

\subsubsection*{Human Lands}

Humans can be found everywhere on Aror. But history indicates that they
originated on the southern continent of \emph{Arania}, and migrated to all
other continents during the last ice age tens of thousands of years
ago. Wherever humans settle they build villages, cities, and large kingdoms
and often become the dominant culture and social structure. Human kingdoms
have often endured for thousands of years, and have bested many difficulties
that had driven other societies to ruin. The ingenuity of the humans, their
stubborn attitude and their uncanny ability to adapt to any difficulty makes
them the dominant race of \emph{Aror}.

\subsubsection*{Human Culture}

Like most races, humans have no inherent global culture, tradition or customs.
Instead their believes and customs are ever evolving, and specific to the
realm they live in. But there is one trait that the average human has: ingenuity
in the face of adversity. No other species has managed to settle every corner
of the world and endure, and even build lasting civilisations out of the
hostile environment they found themselves in.

\begin{35e}{Human Traits}
  \begin{itemize}[noitemsep]
  \item Medium: As Medium creatures, humans have no special bonuses or
    penalties due to their size.
  \item Human base land speed is 30 feet.
  \item 1 extra feat at 1st level.
  \item 4 extra skill points at 1st level and 1 extra skill point at each
    additional level.
  \item Automatic Language: Teranim. Bonus Languages: Any (other than secret
    languages).
  \item Favoured Class: Any. When determining whether a multiclass human takes
    an experience point penalty, his or her highest-level class does not count.
  \end{itemize}
\end{35e}
