\subsubsection{Hunters}
\label{sec:Hunters}

Hunters are large humanoid-shaped daemons, specialising in tracking down
other living beings. Their bodies and limbs are slender, and their head is the
skull of a deer. Nobody has seen a hunter's true face, and some believe that
it does not have one to begin with. The hunter does have glowing red eyes,
that allow it to see in the dark, and it also has a keen sense of smell and
excellent hearing. Hunters often decorate these skulls with ornaments,
feathers, jewellery, or small beads. A hunter can vary their height, shrinking
down to the size of a halfling, or grow to the size of an ogre at a moments
notice.

These daemons specialise in tracking, and hunting down intelligent prey. They
can be summoned with a ritual of the \nameref{sec:Old Ways}, upon which it
demands a small offering (jewellery, or an hand-made ornament) as well as
information about the target it is supposed to hunt down. Hunter's do care why
it is hunting its target, and the hunt must be sanctioned by local laws or
traditions. Hunters are often summoned to hunt down and track fleeing
criminals, escaped slaves or prisoners. \emph{sec:Gargoyles} are capable of
summoning hunters to track down sentenced criminals that try to run from
justice.

Many have described the Hunter to be a gentle spirit, only becoming violent if
violence is brought against it or its target. A hunter has no intention to
harm its target, and simply wishes to return the target to its summoner. Thus
they are often summoned to track people who have disappeared, such as those
lost in the forest, or children that did not return home. As a testament to
its good nature, it will search for missing children without asking for
payment.

\aren{My mother often threatened to send a hunter after me if I am not home
  by sundown.}

Even though the Hunter is an excellent tracker, hunter, and woodsman it does
not always find its target. In such a case the hunter will return to its
summoner, offering one of its skull ornaments as an apology.

Nevertheless its hunting prowess is fabled among many humanoid and monstrous
tribes. Many hunters, foresters, wayfinders and trackers mimic the look of the
fabled daemon, wearing their own head ornaments made out of deer skulls or
antlers. An entire guild of slave hunters is named after the fabled creature,
and the guild even sports a deer skull in their banners and ornaments.

\begin{35e}{\Large{Hunter}}
  \srditem{Size/Type}{Large Daemon (Humanoid)}
  \srditem{Hit Dice}{6d10+13 (51 HP)}
  \srditem{Initiative}{+8}
  \srditem{Speed}{40 ft.}
  \srditem{Armour Class}{17 (-1 size, +4 dex, +4 natural), touch 13,
    flat-footed 13}
  \srditem{BAB/Grapple}{+6 / +18}
  \srditem{Attack}{+11 Slam 1d8+5}
  \srditem{Full Attack}{+11 Slam 1d8+5 / +6 Slam 1d8+5}
  \srditem{Space/Reach}{10 ft./5 ft.}
  \srditem{Special Attacks}{-}
  \srditem{Special Qualities}{Immunity to petrifaction, Manifest Body (Ex),
    Spirit Form (Ex), Humanoid Form (Ex), Change Size (Su), Track (Ex),
    Dark Vision (120 ft.)
  }
  \srditem{Change Size (Su)}{
    The Hunter can change its size between small, medium, and large at will.
    This works just like a permanent ``Reduce Person'' spell.
  }
  \srditem{Saves}{Fort +5, Reflex +9, Will +10}
  \srditem{Abilities}{Str 20, Dex 18, Con 16, Int 10, Wis 20, Cha 8}
  \srditem{Skills}{Listen +16, Search +9, Spot +16, Survival +14}
  \srditem{Feats}{Improved Initiative, Improved Grapple, Alertness}
  \srditem{Environment}{Forests}
  \srditem{Organisation}{Solitary, pair, squad (3-5)}
  \srditem{Challenge Rating}{6}
  \srditem{Treasure}{-}
  \srditem{Alignment}{Often chaotic good}
  \srditem{Advancement}{By character class (Ranger)}
  \srditem{Level Adjustment}{-}
\end{35e}
