\subsection{Monstrous Races}
\label{sec:Monstrous Races}

\aren{For a long time I considered an honorable and noble ogre named
  Gor'esch'tar my best friend. Mothers' bless his kind soul.}

When the four core humanoid races set forth from the continent of
\nameref{sec:Arania} to settle the world, they found it already inhabited
by many different monstrous races. Some of which are sentient, others even
built civilisations such as towns or cities, while others are mere beasts
and animals. Monstrous races can be found on all of Aror, but are rarer on
\nameref{sec:Eilean Mor} as they have been pushed back by the humanoid races
on that continent for hundreds of years.

\subsubsection{Two Fronts}

Much like with humanoids, you will find members of the monstrous races from
all walks of life, holding many different believes, exhibiting all kinds of
attitudes, and perhaps even sharing the very same dreams and hopes that you do
as well. The only constant on Aror is the centuries old feud between monstrous
and humanoid races that finds its roots in the \nameref{sec:Aeon of
  Strife}. It has sown hatred, distrust, animosity and cost thousands, if not
millions of lives on both sides.

Even after the aeon of strife had ended, many beast races continued to raid
human settlements, entrenching the divide between the two deeper and deeper.
Hobgoblins, ogres, trolls and bugbears often sail south from the shores of
\nameref{sec:Iafandir} towards \nameref{sec:Eilean Mor}, raiding the coastal
villages and baronies for wealth, food, artefacts and slaves. This in turn
gave rise to warring nations such as \nameref{sec:Norbury} or
\nameref{sec:Morkan}, adding fuel to the hatred between the two factions.

This is often precipitated by the ever expanding humanoid settlements, who
encroach on land already inhabited by monstrous tribes and villages. Since the
city kingdoms, baronies and lordships often wield bigger military might, they
sometimes forcefully remove, exile or even kill monstrous tribes to continue
their expansion.

\subsubsection{Cultures}

Among the other great and advanced monstrous races belong \textbf{hobgoblins},
\textbf{ogres}, \textbf{bugbears}, \textbf{trolls}, \textbf{gnolls},
\textbf{goblins}, \textbf{kobolds}, \textbf{lizard folk}, \textbf{harpies}
and \textbf{medusa}.

\textbf{Hobgoblins} are among the most advanced of the monstrous races,
building small towns, fortified villages and even cities. They have a strict
society, culture and traditions that date back several hundred years. Hobgoblins
are often lead by a warrior priest, who follow the \nameref{sec:Three Kings},
and are among the most warring tribes on Aror. Although they are engineers of
large societies and cities, they are also civilisation's greatest enemy. They
often besiege, raid, or outright destroy other civilisations to gain slaves,
food or resources vital for their own survival. Some hobgoblin tribes trade
with other monstrous races, and some even trade with humanoid races.

Although the ogres are superior in terms of bodily strength and size, they
often live in smaller clans. Ogres often follow an aspect of
\nameref{sec:Marwaid}, and remain hunters and gatherers. Although primitive
in ways, ogres are among the most peaceful of the monstrous races and abhor
slavery. Ogres are, like most monstrous races, suspicious of humanoids and
other monstrous races, but prefer to talk, trade and live peacefully with
others.

Gnolls can mostly be found on \nameref{sec:Arania} as well as the southern
part of \nameref{sec:Goltir}. They are deeply spiritual people following an
ancient belief system that worships evil aspects of \nameref{sec:Forun} such
as conflagration, chaos and destruction. They have their own large kingdom on
Arania, called \nameref{sec:Esmayar}. Much like hogoblins, gnolls are slavers
and raiders, but are known to build, farm and even trade with humanoids and
other monstrous races.

Bugbears also build smaller clans or perhaps towns, and prefer to hide, hunt
and steal from other races over enganging in direct conflict. Many other
monstrous races, and sometimes even humanoids, hire bugbears as mercenaries,
spies, soldiers or guards. Bugbears have a reputation for being honourable,
and true to their word.

Much like the hobgoblins, Medusa are builders of great civilisations. They are
a highly xenophobic, and warring, as well as fierce raiders and slavers. As
there are no male medusa, they have to abduct and enslave males from other
monstrous or humanoid races to reproduce. Most of the time this union breeds
pure female medusa, but rarely it also produces a half-race called
\nameref{sec:Gorgons}. These gorgons are then cast out out as impure from
Medusa society. Medusa are excellent witches and sorceress, and have been
building large and grandious cities and places of arcane study for centuries.

Harpies often live high up in mountains, such as the \nameref{sec:Great Divide}
or the \nameref{sec:Cnamh Mountains}, where they are known to pray on anyone
foolish enough to wander into their territory. Harpies live a primitive hunter
and gather live, but are renowned for their excellent marksmanship and hunting
prowess, but prefer not to come into contact with other species.

\begin{35e}{Monstrous Races}
  Most monstrous races do not have a fixed alignment, although certain
  cultures tend towards certain alignments. For example most bugbear clans
  tend to be lawful neutral, while their counterparts the hobgoblins are most
  likely to be lawful evil. Ogres are often even good or neutral, compared to
  gnoll who often are neutral, or even chaotic evil.

  Those races not described here follow the lore of the SRD.
\end{35e}
