\subsection{Mul}
\label{sec:Mul}

A \emph{mul} is the offspring of a female dwarf and either an male deepkin or
a human male. Muls are between two and two and half metre tall, and combine
the tall statures of their human or deepkin fathers, with the physique and
strength of their dwarven mothers. Muls have superior flexibility, and
stature, and combine that with incredible strength and endurance. Muls are
often born without hair, and often inherit their more graceful facial features
from their father's side which stands in stark contrast with their
overwhelmingly muscled body.

Muls live up to eighty years, and often have fair to copper skin. Those few
hairs that they do grow is often brown or hazel. Their eye colour ranges from
blue, green to red.

Most muls are so immense in size as an infant that they often cause lethal
complications to their dwarven mother during child-birth. Most city states, as
well as most physicians and priests thus openly discourage a matrimony between
female dwarves and male humans. But unlike the \nameref{sec:Half-Orcs} who
share a similar fate, Muls are not sterile. The traits of a mul are not
dominant however, so only a mul-mul union produces another mul child.

Muls integrate into the predominantly humanoid culture rather well. Even though
they are quite rare, they are still well received in most city kingdoms. They
make excellent warriors, workers, as well as wayfaerers and hunters.

\begin{35e}{Mul Traits}
  \begin{itemize}[noitemsep]
  \item Their dwarven blood makes it easier for muls to gain and maintain
    muscles and thus have +2 racial bonus to Strength and Constitution.
  \item Medium: As Medium creatures, muls have no special bonuses or penalties
    due to their size.
  \item Overwhelming Physique (Ex): Muls gain a +4 racial bonus to saves against
    any effect that would render them \emph{dazed} or \emph{stunned}.
  \item Perfect Health (Ex): Muls automatically gain the feat \emph{Endurance}
    at first level.
  \item Mul base land speed is 30 feet.
  \item Automatic Languages: Teranim, Rutari. Bonus Languages: Any (except
    secret languages)
  \item Favoured Class: Any. When determining whether a multi class takes an
    experience point penalty, his or her highest-level class does not count.
  \end{itemize}
\end{35e}
