\subsection{Orcs}
\label{sec:Orcs}

Orcs are a green-skinned, near-humanoid monstrous and intelligent species,
mostly inhabiting cold, and temperate climates of \nameref{sec:Goltir},
\nameref{sec:Eilean Mor} and \nameref{sec:Iafandir}. The average orc is almost
as large as a high elf, ranging from two metres, to two metres and fifty
centimetres in height. Their skin ranges from various hues of green, to
various shades of grey, and their biggest features are oversized canine teeth
which more closely resemble tusks. Out of all the monstrous races the Orcs are
shortest lived, with an average life span of about forty years. Both sexes of
orc have incredible body strength, and use their muscular bodies to become
fierce warriors, as well as excellent smiths and artisans.

Out of all the monstrous races the orcs are among the most violent. Their short
live spans, paired with immense fighting prowess and strength often predisposes
them to aa life of hired soldiers, raiders, and warriors. Orc culture is
centred around the family, with many families living together in small tribes.
These families are blind towards race, and orcs are known to adopt foundlings
of other races and raising them as their own.

Orc technology is lacking compared to the other races, and that which they
cannot make themselves they often trade, steal, or outright raid from more
developed neighbours. Tribes are usually led by the eldest orc in the family,
who is then called ``patriarch'' or ``matriarch'', and have a shaman who is
the spiritual leader of the tribe. Orcs often worship either an aspect of
\nameref{sec:Marwaid}, or \nameref{sec:Morana}, while more warring tribes
worship the \nameref{sec:Three Kings}.
