\subsection{Scourge}
\label{sec:Scourge}

The xalnita (invalid draconic combination of ``xalni'' and ``gunta'' meaning
``panicked by invasion''), often called the scourge, is an extra planar and
psionic life form whose sole purpose is to grow and expand. It takes the shape
of a five centimetre thick, red and rough flesh that is warm to the touch. The
scourge can grow indefinitely, and can range from the size of a small patch a
few square metres to covering entire cave systems, areas, or even entire
planets.

\subsubsection{Appearance}

The scourge itself is a thin layer of red flesh and skin that slowly grows
over all surfaces and is perhaps a few centimetres thick. The thin layer
is ever pulsing and vibrating, and it is warm to the touch. It is strewn with
red and blue veins which transport important liquids and nutrients from one
corner of the scourge to the other. It grows over stone floors, clings to cave
walls and will cover ceilings and soft dirt. Once it has absorbed knowledge
about other living materials such as bone or cartilage it will incorporate
these elements into its own design. The scourge has been known to use
bone-like material to create bridges, uphold and support walls, or make
ladders and stairs so that its spawn can best natural barriers. This gives
the scourge a grotesque appearance of a living cave or a forest of flesh and
bone, where all trees are actually one interconnected creature.

The size of a scourge ranches from very small (perhaps a few square metres in
size), to moderate (covering small caves), big (big caves or a square kilometre
of forest), extreme (covering entire areas) to overwhelming covering entire
planets.

Bigger scourge growths (such as the one in the abyss) are capable of producing
complex geographical features. It will produce forests, vast cavern networks,
reroute rivers and create artificial lakes. The scourge can spawn organs such
as eyes or ears within on its surface to better observe its surroundings. It
might also spawn maws of sharp teeth and jaws to grind down food for easier
digestion.

\begin{table*}[!htb]
  \captionsetup{labelformat=empty,font={large,bf},position=top}
  \caption{Scourge Sizes}
  \rowcolors{1}{white}{light-grey}
  \begin{tabular}{l l l l l}
    \textbf{Size} & \textbf{Area}             & \textbf{DC} & \textbf{Psionic Range} & \textbf{Max demon HD} \\
    Tiny          & Several square metres     & 10          & Very close             & - \\
    Small         & Hundreds of sqms          & 13          & Few metres             & - \\
    Medium        & Several thousand sqms     & 16          & Few hundred metres     & HD 2 \\
    Large         & Several hectares          & 20          & Few kilometres         & HD 6 \\
    Huge          & Several square kms        & 25          & Several hundred kms    & HD 11 \\
    Gargantuan    & Thousands of square kms   & 30          & Several thousand kms   & HD 16 \\
    Colossal      & Continents                & 35          & Across planes          & HD 20 \\
    Epic          & Planes                    & 40          & Across planes          & HD 30 \\
  \end{tabular}
\end{table*}

\begin{35e}{Size}
  A scourge growth has 30 hit points per ten square metre (30 hp per square
  feet), and a DR of 10/-. The scourge is further resistant to acid and
  electricity (DR 10), but has a weakness to fire, and cold.
\end{35e}

\subsubsection{Nourishment}

The scourge feasts on different forms of energy (such as warmth), as well as
organic matter which it digests and absorbs. To do so it grows over any
organic material that lands upon it surface and begins to slowly digest and
devour it. The scourge can absorb and devour anything soft, and organic such as
water, flesh, bone, skin, hair, plants, wood, soft fertile dirt, and even some
softer composite organic materials like cloth or leather. It cannot devour
stronger compounds such as rocks, certain crystals, glass, iron or steel. It
requires roughly thirty minutes to absorb 10 kg of organic material. Creatures
walking on the scourge must not fear being absorbed, as the scourge itself
grows to slowly. But if a creature is incapacitated or sleeping on the
surface, the scourge will have enough time to grow over, pin it in place and
then slowly eat it.

It can further absorb warmth and heat, and use that energy directly to feed
and nourish itself. It has a strong aversion to cold, which slows it down,
and makes it go into hibernation. The scourge loathes fire, and will actively
retreat growth from fire sources.

\subsubsection{Intelligence}

The scourge is driven by finding new food, which in turn helps it to grow and
expand. Anything organic is considered food, irregardless on whether that food
is alive, intelligent, struggling, feeling pain or if it is already dead
biological matter. Most scholars agree that the scourge has no concept of
mercy or pain and simply lives to devour.

Its most devious ability is to learn from any organic material it absorbs. The
scourge then puts these new abilities to use to find more nourishment and
biological matter. For example once it has absorbed plants it might grow
leaves or even forests in the sun to nourish itself, or once it has absorbed a
predator it might spawn its own predator to hunt and kill other life
forms. The more material it absorbs, the better it begins to understand the
creatures it attempts to copy. So an important secondary goal for the scourge
is to find new genetic material to absorb.

The intelligence of the scourge increases with each absorbed biological
sample, as it learns about new tools, their weaknesses, and how to best put
them to use for its own needs. Its intelligence is also directly proportional
to its size, as it must grow to be able to store the information it absorbs.

Small patches of scourge that are split from the main growth are disconnected
from the vast absorbed knowledge, and must either reconnect, or learn
everything a new. This also holds true when the scourge attempts to colonise
a new plane by spawning a new clone of itself.

Large scourges, that have absorbed related knowledge, are capable of building
structures such as towers, houses, castles, fortifications, traps and even
teleporters that can bring their spawn to different realms and planes.

\begin{35e}{Intelligence}
  The scourge is highly intelligent, has no feelings, and simply lives to
  acquire food and biological blueprints by all means necessary. It is therefore
  considered \emph{chaotic evil}.
\end{35e}

\subsubsection{Powers and abilities}

Without any additional absorbed knowledge it can only perceive what happens
directly on its surface. In such a reduced state it must prey on immobile life
forms such as plants or mushrooms, and must rely on chance that another life
form dies on its surface.

But from the very start the scourge has psionic powers, and these powers grow
in proportion with its size. At a smaller size it may only communicate with
other psionic creatures that are either very close or are in direct contact
with the surface. But as it grows it may cast its psionic will and powers
across vast distances, and in case of the abyss, even across the boundaries of
planes. The scourge never speaks telepathically, but instead attempts to
control any creature it connects with telepathically through the transmission
of basic instincts and desires.

\begin{35e}{Power}
  Any psionic creature that attempts to make contact with the scourge must
  succeed a will save or be subject to the \emph{Dominate, Psionic} spell
  cast by the scourge that lasts 1d4+1 hours. The DC for the will save is
  listed in the table of scourge sizes. The scourge uses its psionic range (as
  listed in the table) to remotely control and guide its spawn.

  Without having absorbed knowledge about sensory organs, the scourge has
  only \emph{Blindsense (30 ft.)}.
\end{35e}

\subsubsection{Spawns}
\label{sec:Spawns}

Once a scourge has learned enough about other biological lifeforms it begins
to spawn its own creatures. The scourge will grow large, oval, fleshy spawn
pods, which will produce various creatures modelled after those that it has
absorbed. However the spawn that the scourge produce are often horrible
mockeries of the original. Those creatures are often spawned with horrible
deformities, with severe disabilities, body parts of wrong proportions or
mixture of several features of different species together. These creatures are
often just barely capable of performing the tasks that the scourge designed
them to do. The scourge cares little, and it will reabsorb and spawn new
variations in an attempt to improve the design.

These creatures are telepathically linked to host scourge, so that the scourge
can see, hear or act through them. The creatures its spawns perform a wide
variety of tasks, such as scouting new areas, defend the scourge, directly
hunt for food, or process the food that has already been captured. Spawn that
are created by the planet spanning scourge in the \nameref{sec:Abyss} are
called \hyperref[sec:Demons]{demons}.
