\subsection{Tieflings}
\label{sec:Tieflings}

The tieflings are a humanoid-like species engineered by the
\hyperref[sec:Devils]{devils} that inhabit the layers of hell. Most tieflings
are considered devils, but are listed here as they were specifically designed
by the devils as workers, soldiers, and servants. They inhabit all layers of
hell, and some fled to Aror to escape a life of servitude, forced labour and
death in the wars they were supposed to fight.

There is a common misconception that tieflings are the children of succubi or
erinyes, and a humanoid creature, but such a union would simply result in
another erinye or succubi being born. The original tieflings were bred by the
fiendish breed masters, and were engineered through arcane and scientific
machinations, while all modern tieflings are born to tiefling mothers.

Many tieflings share a largely humanoid physique, and often have a wide mix of
other more hellish features, such as tails, wings, horns, oversized and
protruding teeth, a wide palette of skin colours (ranging from red, to blue
and even light hues of green), perhaps even several skin colours at once, and
some tieflings have sharp, distinct eyes that resemble the eyes of a reptile.

Tieflings usually inhabit the layers of hell, but a large population of them
also hides among the humanoids in the large city kingdoms. There they lived
in hiding, but in relative peace. In the aftermath of the \hyperref[sec:Devil
  Siege]{devil siege of Forsby} many tieflings were either exiled, driven
away, or even outright sentenced and convicted for being supposed spies and
agents of the devils. Most tieflings either returned to the layers of hell, or
fled to rural areas to hide and live in secret. A life in hiding is often
necessary, as many churches and organisations, such as the church of
\nameref{sec:Lor}, actively hunt and prosecute tieflings for being evil, and
hellish abominations.

\begin{35e}{Tiefling Traits}
  The basic 3.5e traits of tieflings are still in place, except that their
  favoured class has been changed to \emph{any}, instead of \emph{rogue},
  and they no longer have a level adjustment.

  Tieflings may have wings, which increases their level adjust by one.
\end{35e}
