\subsection{Umgeher}
\label{sec:Umgeher}

\aren{I was once the midwife of an \emph{Umgeher}...}

\graham{The less shared about this experience the better.}

\emph{Umgeher} (old Teranim for someone who walks again) are undead humanoids
that retained their own individuality, will, memories and determination across
the process that turned them into undead. They were created centuries ago by
the ancient vampires that reign in the city kingdom of \nameref{sec:Helmarnock},
and were given the physical ability to reproduce on their own, without turning
others towards undeath.

This allowed them to establish themselves as their own species on Aror, and
thus soon travelled and spread across the entire known world. Umgeher are
neither immortal, nor are they invincible. Umgeher live to be a hundred years,
do not require food or sleep, but must drink water to survive. More so, their
flesh and skin is in a constant state of decay, and must combat their never
ending dissolution with oils, ointments or arcane spells. They have no bodily
hair, and often wear wigs to blend into normal population. Umgeher have a
distinct physiology vulnerable to damage, compared to other undead, and
require doctors to heal wounds, fix broken bones, or diagnose degrading health
at advanced ages.

Umgeher, like any species, are free to determine their own fates and shape
their own destinies. They do have to constantly combat the ignorance and fear
of the other races, but most city states have now allowed umgeher to become
full citizens, and treat them equal to any core humanoid race. This was a
recent trend however, and most umgeher prefer to build their own little
communities and towns in more rural areas.

Many religious institutions that see necromancy and undead as a defilement of
life, also persecute, hunt and destroy umgeher. Those institutions are also
to blame for the many lies that have spread across the general populace about
umgeher, such as their fanatical cravings about humanoid flesh, or that they
will take over heavy labour sectors in an economy.

\begin{35e}{Umgeher Traits}
  \begin{itemize}[noitemsep]
    \item Type: \emph{Undead}.
    \item Medium: as medium creatures, \emph{Umgeher} have no special bonuses or
      penalties due to their size.
    \item \emph{Umgeher} base land speed is 30 ft.
    \item As living undead umgeher gain all undead traits, except only gain
      partial immunity to critical attacks. This effect is equivalent to 50\%
      fortification. Umgeher follow humanoid growth cycles (i.e. are born, have
      a childhood, young adulthood, adulthood and finally seniority) and live to
      become roughly 100 years. Furthermore Umgeher must drink water like any
      living species.
    \item \emph{Umgeher} have a live long experience in disguising themselves as
      humans, and thus gain a \emph{+2 racial bonus} on \emph{Disguise} and
      \emph{Bluff}.
    \item Favoured Class: Any. When determining whether a multi class takes an
      experience point penalty, his or her highest-level class does not count.
    \item Automatic languages: Teranim. Bonus languages: Any (except secret
      languages).
    \item Level Adjustment: none
  \end{itemize}
\end{35e}
