\section{Documents}
\label{sec:Documents}

\subsection{Citizen Papers}
\label{sec:Citizen Papers}

The cheapest of all identification methods are the citizen papers. Often a
single scroll, elaborately designed and embellished that holds the citizen's
name, race, gender and age; along with a seal of the kingdom or nation to
which they are a citizen off. These papers are important travel documents for
most citizens, and usually cost between five or ten \hyperref[sec:Shin]{shins}
to be issued. Families often just have one citizen paper for the entire family.

\subsection{Business Licence}
\label{sec:Business Licence}

Business licences are important documents for anyone that intent to form their
own businesses, or conduct trade across the world of Aror. The paper is usually
a beautifully embellished scroll, that contains basic information about the
business, the owner, and the seat of the kingdom or barony in which the business
has its head quarters. Many larger businesses ask for copies or the original
paperwork before conducting trade with another business, and many agents of
businesses are issued a copy of the licence as a document of identification.

Most city kingdoms issue business licences, while some city kingdoms and
baronies also offer business licences for areas of commerce that may be
outlawed in another area. For example \nameref{sec:Helmarnock} issues licences
for necromancers, while the all slaving nations issue business licences for
slavers, which might be outlawed in nations that ban slavery.
