\section{Drugs}
\label{sec:Drugs}

The trade of often illicit, dangerous, addictive yet stimulating or arousing
substances is another sad reality of Aror. Often entire businesses have
evolved around manufacturing, smuggling and selling these drugs to those
addicted, and the global drug trade makes untold numbers of shards per year.

The more harmless drugs, such as tobacco, alcohol and sarelis are allowed in
most states and nations, while the more dangerous drugs are illegal to produce
and possess. Nevertheless an underground network of local thieves guilds,
smugglers and well hidden farmers and alchemists, produce, ship and supply all
corners of the world with their toxic creations.

\begin{35e}{Drugs}
  The rules for drugs, their usage, as well as any rules on how to make them
  are laid out in the 3.0 book called \emph{Book of Vile Darkness}.
\end{35e}

\begin{table*}[!htb]
  \captionsetup{labelformat=empty,font={large,bf},position=top}
  \caption{Overview of Drugs}
  \rowcolors{1}{white}{light-grey}
  \begin{tabular}{l l l l l}
    \textbf{Name} & \textbf{Type}  & \textbf{Price} & \textbf{Alchemy DC} & \textbf{Addiction} \\
    Atropa        & Ingested DC 17 & 5 shins/g      & 12                  & High \\
    Karthas Paste & Ingested DC 20 & 50 shins/g     & 20                  & Extreme \\
    Sarelis       & Inhaled DC 12  & 10 shins/g     & 27                  & Low \\
    Synemium      & Ingested DC 18 & 50 shards/ml   & 25                  & Extreme \\
    Xoridina      & Ingested DC 15 & 20 shins/g     & 15                  & Medium \\
  \end{tabular}
\end{table*}

\subsection{Atropa}
\label{sec:Atropa}

Atropa is a small flower that grows in abundance on most northern continents
of Aror. It has white pedals, and small green stalk. It has a soft, nutty and
sweet smell. It is mildly poisonous but it would take a large amount of the
flower to actually harm a human being.

Petals from the plant are dried in the sun, and then ground into a fine
grained white powder. This powder is then mixed with other herbs and
ingredients. The mixture is then inhaled through the nose, or mixed with water
and ingested. It is then capable of suppressing the need for shape shifters
(especially were creatures) to transform into their animal form. The powder
mixture is highly addictive however. It is highly valued by were creatures
that live in society, and is also often forcefully injected into captured and
imprisoned were creatures and druids.

\begin{35e}{Atropa}
  \srditem{Addiction Rating}{High}
  \srditem{Satiation Time}{3 days}
  \srditem{Damage}{It deals normal damage to shape shifters (were creatures,
    druids, and other creatures that can change form), and half damage to
    non-shifters.
  }
  \srditem{Initial Effect}{1d4+1 points of wisdom damage to non-shifters,
    1d8+1 damage to shifters.}
  \srditem{Secondary Effect}{Shape shifting ability is suppressed for the time
    of the satiation. The character loses all ability to shape shift, and
    cannot be forced to shape shift through external means, such as a full
    moon.
  }
  \srditem{Overdose}{Non-shape shifters who take the drug more than once
    within 24 hours take 2d6 points of damage. Shape shifters who take the
    drug more than once within 12 hours must make a separate save (Fort DC 36)
    or die in terrible pain.
  }
\end{35e}

\subsection{Karthas Paste}
\label{sec:Karthas Paste}

Karthas paste is a mixture of several herbs and mushrooms, all of which can be
found in damp and cold places (such as forests or caves). The ingredients are
dried, boiled, and then condensed to a thick, brownish paste that tastes sweet.
The ingredients are rather common, but the process of making the paste potent
enough requires a skilled alchemist.

It is highly addictive, wards off hunger, thirst and pain. It's main effect
clouds the users judgement, making him more susceptible to commands and
orders, often impairing the user's judgement so far as to make him believe
that potential dangerous orders and tasks are a good idea. It is thus often
mixed with \hyperref[sec:Food]{bird butter} and fed to slaves, and those that
have to do dangerous work such as mine \nameref{sec:Everblack}, or are sent
into battle against their will.

\begin{35e}{Karthas Paste}
  \srditem{Addiction Rating}{Extreme}
  \srditem{Satiation Time}{2 days}
  \srditem{Initial Effect}{Hunger is suppressed for two days.}
  \srditem{Secondary Effect}{User gains a -4 penalty to will saves, and
    gains an additional -8 penalty to skill checks to resist suggestions,
    bluffs or intimidations through the appropriate skills.
  }
  \srditem{Overdose}{If more than one dose is taken in a 12 hour period, the
    user takes 2d6 points of non-lethal damage. Using it more than three times
    within 24 hours causes 2d6 points of damage and paralyses the user for 2d4
    hours.
  }
\end{35e}

\subsection{Sarelis}
\label{sec:Sarelis}

Sarelis is a small weed or herb that is grown in tropical environments, such as
the vast jungles north of \hyperref[sec:South Goltir]{Goban mountain}, the
jungles of the \nameref{sec:Silver Isles} or \nameref{sec:Yuacata}. The weed
is harvested, dried and then mixed with tobacco and smoked.

Among all the drugs available on Aror it is the least potent, but nonetheless
addictive. It calms the nerves, makes one physically sluggish and causes mild
auditory and visual hallucinations. However it also heightens all senses, and
generally calms even the most aggressive people down allowing them to remain
calm and collected. It is quite popular, but never smoked pure but often mixed
with normal, harmless weeds.

\begin{35e}{Sarelis}
  \srditem{Addiction Rating}{Low}
  \srditem{Satiation Time}{10 days}
  \srditem{Initial Effect}{Harmless visual and auditory hallucinations}
  \srditem{Secondary Effect}{2 alchemical bonus to wisdom, as well as +5
    alchemical bonus to \emph{Diplomacy}.}
  \srditem{Side Effect}{None.}
  \srditem{Overdose}{Taking a second dose before the first has worn off causes
  the user to be nauseated for 1d4 x 10 minutes.}
\end{35e}

\subsection{Synemium}
\label{sec:Synemium}

Synemium, often simply shortened to \emph{``syn''} or the \emph{``blue gold''},
is the refined, blue, shimmering and thickish fluid that is made out of the
resin of the tree of the same name. The tree grows only in the jungles of
\nameref{sec:Yuacata}, and its resin is thus very hard to extract. The resin
itself must be refined and distilled before it can be used as a drug.

It is highly toxic in larger quantities (30 millilitres), and is thus only taken
in small drops. These drops are often absorbed through blood, or ingested
through the mucous membranes of the nose. It heightens and sharpens the
intellect, as well as allowing the user to stay awake and sharp for several
days without the need for sleep or rest.

It is highly priced and valued among those that do mental labour, such as
wizards, clerics, tacticians or researchers, but its astronomical price
makes it a luxury drug.

\begin{35e}{Synemium}
  \srditem{Addiction Rating}{High}
  \srditem{Satiation Time}{variable}
  \srditem{Initial Effect}{1d4+1 strength damage}
  \srditem{Secondary Effect}{1d4+1 alchemical bonus to intelligence and wisdom}
  \srditem{Side Effects}{Once taken, it automatically heightens (as the
    Heighten Spell Feat) the next 2d4 spells the character casts. Once all
    heightened spells have been cast satiation ends, and withdrawal of the
    drug kicks in. If the user does not cast spells, or his spells cannot be
    heightened, then withdrawal kicks in within 1d4+1 days.
  }
  \srditem{Overdose}{Those who take the drug more than once within 24 hours
    must make a separate save (Fort DC 28 negates) or die in terrible pain.
  }
\end{35e}

\subsection{Xoridina}
\label{sec:Xoridina}

Xoridina, often simply shortened to \emph{``dina''} or \emph{``devil's nut''},
is a family of large gigantic trees that grow in the southern realms of
Aror. They produce a small, pebble-sized nut, that becomes highly addictive
once the nuts have ripened. The wood of the tree is prized, as it is hard and
sturdy and thus often used to build ships.

The ripe nuts are often crushed to a fine powder, and then added to drinks and
foods. It is highly addictive, and has a calming effect on those who consume
it, and it makes them lethargic, relaxed and laid back. It numbs the senses,
as well as any pain and is thus often used as a battle field pain relief
medicine.

It is one of the most commonly available, as well as one of the cheapest drugs
available, as the tree itself grows in large numbers and each tree contains
hundreds, if not thousands, of nuts.

\begin{35e}{Xoridina}
  \srditem{Addiction rating}{Medium}
  \srditem{Satiation Time}{5 days}
  \srditem{Initial Effect}{2 dexterity damage}
  \srditem{Secondary Effect}{The user gains DR 5/- for 1d2 hours}
  \srditem{Overdose}{Those that take this drug more than once in 24 hours must
    make a separate save (DC 20) or fall asleep for 8 hours.}
\end{35e}
