\section{Blood Locks}
\label{sec:Blood Locks}

Deepkin Blood Locks are half mechanical, half arcane locks that only open for
one specific person the lock was ``programmed'' for, or their descendants. They
appear as large gaping mouths (often mouths of predatory animals, such as lions,
wolves, or even dragons) in which a hand is placed. The lock will then pierce
the skin, draw a small drop blood, and unlock once the blood has been verified.
Some blood also appear as simple goblets or mugs, into which blood was must
trickled. An alternate version exists, called the Deepkin Mark Lock, which only
opens to those that wear the correct \hyperref[sec:Arcane Marks]{Arcane Mark}.
A combination of these two locks also exist, and are often simply referred to
as ``Deepkin locks''.

These locks were invented by the ancient Deepkin clan of \nameref{sec:Nicte},
to limit highly sensitive areas to only those that wore a Deepkin clan mark.
Nowadays they are mainly used by noble houses, to restrict access to direct
descendants, or trusted external members wearing an arcane mark.

Deepkin locks have a reputation for being sturdy, highly attuned (being able
to detect descendants over many generations), and for being almost impossible
to be picked or tricked.

\begin{35e}{Blood Lock}
  Arcane Locks use \emph{Arcane Mark} at creation, and only open for those who
  wear the correct \hyperref[sec:Arcane Marks]{arcane mark}. Blood Locks used
  a vial of blood at creation, and open only for the person who contributed
  the blood, or a direct descendant of that person. A Deepkin Lock, in which
  both blood and an \emph{Arcane Mark} was used, combine the effects the two
  locks above. None of these locks can be bypassed by arcane magic that opens
  doors, such as a \emph{Knock} spell. But blood heritage can be faked by
  passing an \emph{Use Magic Device} DC 40 check.

  Strong transmutation, CL 13th; Craft Wondrous Item, \emph{Arcane Lock},
  \emph{Arcane Mark} or a vial of blood, or both; 50,000 GP
\end{35e}
