\section{Implants}
\label{sec:Implants}

Implants are small arcane devices that are surgically inserted into a
creatures body, often beneath the skin, and grant the user and wearer certain
passive bonuses or active bonuses, such as immunity to certain effects, or
limited ability to cast spells.

These implants were invented by \nameref{sec:Asmoday}, the treasurer and chief
arcane researchers of the \nameref{sec:Devils}. The devils found themselves
technically free of the scourge's reign, but were still inherently susceptible
to the scourge's massive psionic power's of mind control. Unable to change their
basic physiology, the devils instead relied on powerful magical artefacts to
counter act the scourge's psionic powers. Now all free devils have an implant
embedded in their skulls (or even brains) that blocks the mind controlling
psionic powers of the scourge, which were crafted by Asmoday or his underlings,
and surgically installed by \nameref{sec:Ishtar} or her underlings.

Implants can grant a wide variety of passive abilities to the wearer, but must
specifically crafted for a specific species and wearer in mind. These implants
must then be surgically inserted into the wearer's body through surgery. Too
many implants will interfere with each other, so it depends on the creature's
body on how many implants can be supported at any given time. A skilled
crafter of implants can adapt an implant for another species or wearer, but must
alter the implant to do so. Furthermore implants are a very delicate piece of
equipment, and many are destroyed when their wearer die a violent death.

The basic implant without any magical enhancements costs around 30 shards
worth of \nameref{sec:Everblack} to produce, and is then enhanced with magical
abilities.

\begin{35e}{Implants}
  Implants follow the same magic item creation rules as normal magic items,
  except that the feat ``Create Implant'' is required to make them. Implants go
  into a new item slot \emph{inside} the creature's body. This new body slot is
  not affected by ``body slot affinity''. There is a 75\% chance that an implant
  is destroyed if its wearer dies a violent death. All implants that grant a
  passive effect must be made to work continuously.

  The limit on how many implants a creature can support depends on the
  creature's HD. First determine the implants power level, which is item's
  worth in shard divided by one thousand. ($ \frac{Shard}{1000} $) and round
  up. A creature can support any combination of implants whose combined power
  level does not exceed its HD.

  Implants whose powers are continuous can be adapted to register as
  supernatural abilities by adding 500 shards (5000 gold) to the implant's
  base price.
\end{35e}

\subsection{Specific Implants}
\label{sec:items:Implants}

\begin{table*}[!htb]
  \captionsetup{labelformat=empty,font={large,bf},position=top}
  \caption{Overview of Implants}
  \rowcolors{1}{white}{light-grey}
  \begin{tabular}{l l l p{7cm}}
    \textbf{Implant}            & \textbf{Price} & \textbf{PL}  & \textbf{Benefit} \\
    Implant of Spiderclimb      & 18,000 gp      & 2            & Continuous splider climb ability \\
    Implant of Scourge Immunity &  3,000 gp      & 1            & Protection from psionic mind control ability of the Scourge \\
  \end{tabular}
\end{table*}

\begin{35e}{Implant of Spiderclimb}
  \srditem{Description}{Grants continuous splider climb to the wearer, as the
    spell \emph{spider climb}
  }
  \srditem{Power Level}{2}
  \srditem{Details}{Faint transmutation, CL 4; \emph{Craft Implant} and
    \emph{spider clib}, Price 18,000 GP, 0.01 lbs}
\end{35e}

\begin{35e}{Implant of Scourge Immunity}
  \srditem{Description}{Grants immunity from the mind controlling powers of the
    scourge.
  }
  \srditem{Power Level}{1}
  \srditem{Details}{Faint telepathy, CL 1; \emph{Craft Implant} and
    \emph{conceal thoughts}, Price 3,000 GP, 0.01 lbs}
\end{35e}
