\section{Jewellery}
\label{sec:Jewellery}

\subsection{Master Ring}
\label{sec:Master Ring}

This iron ring, often emblazoned with a set of keys or an iron chain, is used
to exert control over slaves. The ring can be keyed \nameref{sec:Slave Band}
or \nameref{sec:Slave Mark}, and then allow the owner of the master ring to
control, spy or even damage the wearers of the slave marks or bands. Someone
who wears a keyed slave band or mark cannot touch or use the master ring
directly without suffering horrible, flesh eating damage.

\begin{35e}{Master Ring}
  \srditem{Master Ring}{An iron ring, emblazoned with either a set of keys or
    chains can deal 3d6 points of either normal or non-lethal damage per round
    as a free action to anyone wearing a slave mark or band keyed to
    it. Furthermore the owner of the master ring can, at will and as a free
    action, exchange messages with anyone wearing a keyed slave band or mark
    as if using the \emph{Sending} spell. The master ring can also be used as
    a focus for divination spells, which then target a wearer of a keyed slave
    band or mark as decided by the caster. The target of this divination spell
    has a -4 penalty on saving throws against any divination spell cast through
    the master ring.}
  \srditem{Crafting}{Caster Level: 11th, Prerequisites: \emph{Forge Ring},
    \emph{Dominate Person}, Price: \emph{500 shards}}
\end{35e}

\subsection{Slave Band}
\label{sec:Slave Band}

A slave band is either an iron collar, ring, or shackle for the wrists or
ankles. Once put on it cannot be easily removed except by the wearer of the
keyed \nameref{sec:Master Ring}. However wears the slave band is subject to
the damage and any divination spells the wearer of the keyed master ring.
Unlike slave marks, slave bands can be removed but require a combination of
mechanical and arcane skill to be safely unlocked.

In the last centuries various counter measures to the slave collars have been
developed, allowing slaves to bet set free. In turn the craftsmen have changed
to permanent slave tattoos instead, which cannot be so easily removed. Slowly
the arcane tattoos (called \hyperref[sec:Slave Mark]{slave runes}) are
replacing the arcane collars.

\begin{35e}{Slave Band}
  \srditem{Slave Band}{An iron ring or collar, once put on cannot be easily
    removed except by the wearer of the keyed master ring. The wearer of the
    slave band is subject to the damage from the keyed master ring. The wearer
    of a slave band can also exchange messages with the wearer of the keyed
    master ring three times per day as if using the \emph{Sending} spell. The
    wearer of the slave band cannot directly touch or use the keyed master
    ring, and suffers 3d6 points of damage during such an attempt.}
  \srditem{Crafting}{Caster Level: 5th, Prerequisites:
    \emph{Craft Wondrous Item}, \emph{Crushing Despair},
    Price: \emph{100 shards}.}
\end{35e}
