\section{Weapon Enhancements}

\subsection{Snow Elf Bow}
\label{sec:Snow Elf Bow}

A \emph{snow elf bow} is a specially crafted bow in use with the tribal snow
elves of the great pales. They are imbued with special divine magic, from
either \nameref{sec:Isamir} or \nameref{sec:Forun}. These can be distinguished
from each other as the bows take on red or white veins depending on what deity's
help was used to craft them. Isamir aligned bows are made for those that have
impeccable hand eye coordination, and are known to always hit true, while Forun
blessed bows are made for those with great strength that can draw even the
heaviest of bows.

\begin{35e}{Snow Elf Bow}
  The snow elf craft template can be added to any type of composite bow (short,
  or long composite bow). Snow elf bows always look distinctive in having blue
  (Isamir) or red (Forun) veins and strands running through the wood. Snow elf
  bows do not require strings, as the divine magic within forms a magical string
  if the user attempts to fire it.

  \srditem{Cost}{Snow elf craft template adds 200 shards (2000 GP) to the
    other costs associated with creating a given weapon.
  }
  \srditem{Affinities}{Flaming (for Forun aligned) or Cold (for Isamir aligned).
  }
  \srditem{Special}{Forun aligned snow elf bows allow the user to apply their
    strength bonus to damage when making ranged attacks, while an Isamir
    aligned snow elf bow allows the user to apply their dexterity bonus to
    damage with the bow.
  }
\end{35e}

\subsection{Telescoping Weapon}
\label{sec:Telescoping Weapon}

A \emph{telescoping weapon} is specifically crafted, and enchanted to fold
down to a compact side, usually not bigger than the handle of a dagger or
arming sword. The art of forging, creating, and enchanting such a weapon is
complicated, intricate and was first mastered by the Deepkins of clan
\nameref{sec:Aru'el}. With the fall of the Deepkin clan the secret of how to
create such weapons was lost to history. No real attempts have been made to
recreate the art of forging these weapons, as the \emph{weapon absorption}
enhancements achieves the same goal of making bulky weapons easier to
transport, and draw yet for a fraction of the cost.

These weapons are still masterfully crafted, to the point of being objects of
art, and will last a wielder way beyond his or her lifetime. Telescoping
weapons are sacred implements to the \nameref{sec:Mist Reavers}, and to many
others they are highly priced, and collectable pieces of art from an age of
unprecedented craftsmanship.

\begin{35e}{Telescoping Weapon}
  A telescoping weapon template can be added to any type of weapon that consists
  of continuous material that is not interrupted by chains, cloth, string or
  leather (e.g. slings, or flails cannot be made telescoping). A weapon has to
  be crafted with being telescoping in mind from the start, and an existing
  weapon cannot be changed to be telescoping.

  \srditem{Cost}{A telescoping weapon template adds 500 shards (5000 GP) to the
    other costs of associated with creating a given weapon.
  }
  \srditem{Special}{Telescoping weapon can be reduced to the size of a dagger
    handle as a free action, and thus requires little space to be stowed. In
    its compacted form you gain a +4 bonus to conceal the weapon your body by
    using a \emph{sleight of hand} check. A telescoping weapon has been
    lightened through arcane processes, and thus always counts as a light
    weapon in regards to \emph{two-weapon fighting}.
  }
\end{35e}

\subsection{Weapon Absorption}
\label{sec:Weapon Absorption}

\begin{35e}{Weapon Absorption}
  \emph{Weapon Absorption} is an enhancement that can be added to any light
  weapon. The weapon is bonded to a particular wearer, and that wearer may
  store and retrieve the weapon from and to his forearm at will as a free
  action. The weapon leaves a visible tattoo upon the wearer's forearm,
  symbolising the nature of the weapon (i.e. a dagger symbol for a dagger, or
  a small hammer for a light hammer). The weapon returns to the wearers
  forearm if the wearer loses contact with it, and a person may only store one
  weapon per forearm. Once a bond between a weapon and a wearer has been
  established, the wearer cannot part with the weapon. A \emph{Remove Curse}
  spell is required to unbind the weapon from the chosen wearer. A weapon
  with this enhancement which does not have a current dedicated wearer, will
  automatically bond with the first person that directly touches the weapon.
  An intelligent weapon can resist bonding, as well as being absorbed or drawn
  from the wearer.
  \srditem{Crafting}{Moderate transmutation, CL 5, \emph{Magic Weapon}, Price:
    +3000 gp (300 shard)
  }
\end{35e}
