\section{Wondrous Items}
\label{sec:Wondrous Items}

\subsection{Null Stone}
\label{sec:Null Stone}

A \emph{null stone} is a specially prepared and treated everblack crystal that
slowly siphons power to it from its surroundings. Such stones are expensive to
make but are invaluable as they can negate magical artefacts and wielders of
magic that they come in contact with. These null stones are often embedded in
shackles and binds to keep witches, warlocks and other spell wielders from
using their powers. Although such null stones can be made to explode by
overcharging them as any everblack crystal, this outcome is rarely in the best
interest of the person who was made to wear null stone.

Null stones do not permanently destroy the magical ability of the person or
the artefact but merely suppress them. Once the null stone has been removed
from the vicinity of a magical object or magically gifted person, the powers
regenerate within twenty-four hours. Also null stones do not work immediately,
but require to be near the object or caster for an hour until they have
drained all the residual magic power.

These null stones are often embedded into a \nameref{sec:Slave Band} to
suppress a slaves' or prisoners' magical abilities. Sometimes they are also
crafted directly beneath a slaves' or prisoner's skin to permanently dampen
magical abilities. Although this approach wards against some forms of tampering
it might slowly poison the prisoner or slave who is forced to wear everblack
beneath their skin.

\begin{35e}{Null Stone, Lesser}
  \srditem{Null Stone, Lesser}{This lesser null stone is capable of suppressing
    any magical effect of spell level 3 or lower. It needs to be placed at the
    source of the magical effect, or near the origin of the spell (like a
    caster or magical item) and takes effect after one hour. It's suppressive
    effects last as long as the null stone remains intact and is near the
    source of the magic. Once the null stone has been removed any magical
    effects or sources (such as casters or magical items) regain their power
    after twenty four hours.}
  \srditem{Crafting}{Prerequisites: \emph{Craft Wondrous Item}, 5000 shards
    worth of everblack crystals.}
\end{35e}

\begin{35e}{Null Stone}
  \srditem{Null Stone}{This null stone is capable of suppressing any magical
    effect of spell level 6 or lower. It needs to be placed at the source of
    the magical effect, or near the origin of the spell (like a caster or
    magical item) and takes effect after one hour.  It's suppressive effects
    last as long as the null stone remains intact and is near the source of
    the magic. Once the null stone has been removed any magical effects or
    sources (such as casters or magical items) regain their power after twenty
    four hours.}
  \srditem{Crafting}{Prerequisites: \emph{Craft Wondrous Item}, 10000 shards
    worth of everblack crystals.}
\end{35e}

\begin{35e}{Null Stone, Greater}
  \srditem{Null Stone, Greater}{This greater null stone is capable of
    suppressing any magical effect of spell level 9 or lower. It needs to be
    placed at the source of the magical effect, or near the origin of the
    spell (like a caster or magical item) and takes effect after one
    hour. It's suppressive effects last as long as the null stone remains
    intact and is near the source of the magic. Once the null stone has been
    removed any magical effects or sources (such as casters or magical items)
    regain their power after twenty four hours.}
  \srditem{Crafting}{Prerequisites: \emph{Craft Wondrous Item}, 20000 shards
    worth of everblack crystals.}
\end{35e}
