\subsection{Dragon Teleporter}
\label{sec:Dragon Teleporter}

A dragon teleporter is a magical contraption, that consists of three large
pillars, that sharpen to a point at their end. They are arranged in a circle
that arch inward, touching each other at the top, to form a sort of arch over
a small area beneath them. Once activated arcane energy flows from their stem
to the tip, where they form a glowing, floating ball of energy beneath the
arch, that acts as the horizon for the teleportation magic. Once a living
person touches the horizon, they are instantly transported near one of the
pillars of the remote teleporter. A teleporter that receives a person, can
still teleport one other person away at the same time.

Draconic runes are inscribed into the pillar and help with selecting a target
for the teleportation, and can be used to program new targets into an existing
teleporter. A dragon teleporter requires considerable arcane power to operate,
and can only teleport to one person at a time. A dragon teleporter can still
``receive'' another person that has been sent to it by another dragon
teleporter. A dragon teleporter can also be used as a focus for conventional
teleportation magic, allowing teleportation from any place in the world to
a teleporter, given enough magical prowess.

In \emph{MI:782} one of these dragon teleporters was found in the depths of
the \nameref{sec:Great Divide} by a mining expedition. It was reverse
engineered by arcane scholars, and wizards and then installed in all city
kingdoms that could afford to buy and maintain such a complicated device.
The devices are now hailed for facilitating trade, cultural exchange,
diplomatic missions, as well as allowing the middle, and upper classes of
society to travel and see the world.

Dragon Teleporters can now be crafted, and repaired by the major magical
institutions, but are extremely expensive. Very few institutions can, or want
to, afford a dragon teleporter. All major city kingdoms operate a teleporter,
and it has become a sort of status symbol among kingdoms, and baronies.

\begin{35e}{Dragon Teleporter}
  Building a new dragon teleporter costs roughly one million shards, half of
  which must be high quality \nameref{sec:Everblack}.

  Dragon Teleporters act as a focus point for teleportation magic, allowing
  any caster who can cast \emph{Teleport} (or its greater variant) to teleport
  to any Dragon Teleporter that is currently in operation, without
  teleportation failures.
\end{35e}
