\subsection{Monolith}
\label{sec:Monolith}

The \emph{Monolith} is a dragon-made contraption of unknown design, unknown
appearance, and unknown location, whose technical internals, location, as well
as its inner workings are a closely kept secret by the \nameref{sec:Dragons}.

It was crafted several hundred thousand years ago in order to prevent any
further \hyperref[sec:Giants]{Giant} invasion onto Aror. It does so by
preventing, and shielding Aror from travel to and from other extra-dimensional
planes of existence. It also functions as a cloak shielding Aror from being
scried from other planes, acting as an extra-planar cloak. Given enough
magical energy the Monolith's function can be circumvented, but it inherently
makes a trip to Aror unfeasible, and dangerous.

When the professors, students and Arch Magi of the \nameref{sec:Hall of
  Knowledge} began looking into \emph{calling}, and \emph{summoning} magic
they realised that conjuration magic is inherently more difficult to perform
than other forms of magic. This lead them to discover that something on Aror
blocks, or suppresses these forms of magic, making them almost impossible to
perform. Their investigation lead to the dragons, who acknowledged the
existence of the device, and its purpose. Prolonged interrogations wielded
little information about the device's design, location or on how to improve
conjuration magic to circumvent its purpose. After being asked on how the
device works the dragons simply answered: ``like a mega-ton heavy Everblack
monolith absorbing only dangerous kind of magic''. Many powerful psykers, and
scholars also believe that the Monolith acts as a shield from the
\nameref{sec:Scourge}'s psionic powers, and influence.

The Monolith itself was fundamental in shaping Aror's early history, shielding
the planet from inter-planetary meddling, effectively hiding, and isolating the
planet from all extra-dimensional planes, and beings. It was not until the
\nameref{sec:Aurelis} found Aror through astronomical charting, and observation
that first contact with an ``extra-planar'' species was established.

\begin{35e}{Monolith}
  The Monolith makes all magic that summons creatures, items or other objects
  from another plane (or planet) more difficult, by adding a 20\% spell
  failure chance to such magic (this applies to \emph{all} forms of magic).
  Teleportation magic across planes (but not planets) to and from Aror has a
  75\% of failure.

  It further changes all outsiders that are conjured to Aror to the
  \emph{native} sub type. Should they be slain they their souls will enter the
  \nameref{sec:Soul Well}, possibly making reincarnation impossible. Any
  intelligent outsider summoned to Aror is allowed a \emph{Knowledge (The
    Planes)} to realise that Aror might be their final destination. Any checks
  with outsiders to hash out a deal are thus also more difficult (+10
  circumstance bonus to the DC), should the outsider realise where he is.
\end{35e}
