\subsection{Soulcraft Artefacts}
\label{sec:Soulcraft Artefacts}

``Soulcraft'' is the art of creating artefacts from soul power, much like
arcane smiths use arcane energies to forge artefacts. Soul crafted artefacts
may manifest themselves for users of incredible soul powers, but techniques
that allow their deliberate construction were invented by Deepkin clan of
\nameref{sec:Aru'el}. Their teachings are now lost to history, as many soul
crafted artefacts, and the knowledge on how to forge more, were lost during
the \nameref{sec:Great Exodus}.

These artefacts, often arms, armour, trinkets, and gadgets, had incredible
power when wielded against souls, or other creatures with souls. Many were
crafted with potent abilities, powers, and inexplicable beauty, and
craftsmanship. It is unknown how these were forged, or whether anyone has
regained that knowledge. However \nameref{sec:Stenheim} is actively funding
expeditions to find, unearth and recover soul crafted artefacts. These are
then meticulously studied, and archived by the deepkin engineers, and
scholars. It is unknown how many of these sit in Stenheim's vault. Many
believe that Stenheim is merely collecting, and safeguarding them so that
they do not fall into evil hands.

Still soul crafted artefacts are still made today ``by accident''. Often
because a powerful soul, or a particularly powerful soul magician pours
his or her own soul into an object. This may happen unintentionally as one
forms a deep emotional bond with an object, or deliberately by sacrificing
some of their soul power to enhance their items.

\aren{As our beloved bard, and Arch Magi has said so eloquently: ``We forget
  the space between people and things is empty. We forget, and don't notice
  the loss.''
}

A soul crafted artefact can also be an ancestral artefact. In such a case the
artefact was crafted (either intentionally or by accident) by a direct
ancestor of the wielder, giving both the artefact and the wielder additional
powers, and abilities since their soul powers are related to each other. Such
artefacts then often become family heirlooms, passed down from generation to
generation.

\begin{35e}{Soulcrafted Artefacts}
  Soul crafted weapons are made ``by accident'' through the use of soul powers,
  or by people with incredibly powerful souls. The item must be something the
  wielder shares a deep connection with, and the powers reflect the wielders
  personality, powers, and his or her very core. Such items only work for the
  original wielder.

  Conventionally crafted soul artefacts work for everyone, yet no feat (and
  thus no knowledge) exists, that allows their creation. They can only be
  found.
\end{35e}

\begin{note}
  Soul crafted weapons are a way for DMs to make items that are use-, and
  meaningful to a particular player, depending on their achievement, story
  progression or perhaps ill-fate. They are a meant to be rare, special, and
  specifically tailored to one NPC or player character.
\end{note}
