\subsection{Abyss}
\label{sec:Abyss}

\graham{Do. Not. Go. There. And if you do; just stay there lest you bring
  \emph{it} back with you.
}

The \nameref{sec:Scourge}'s native home planet is called the \emph{abyss}.
Confusingly the particular scourge entity of the abyss is also referred to by
the name ``abyss''. Many personify the place, by using the term
interchangeably for the scourge entity, and the planet itself.

The abyss is a warm, volcanic planet that is geologically active. Volcanos,
geysers and hot springs spew forth hot gases and water to the surface. However
it has human breathable atmosphere, but the average temperatures range from 40
to 60 degrees Celcius, making it inhospitable for most humanoids. The plane is
devoid of any other live, save from the scourge and its spawn. The scourge of
the abyss has managed to cover most of the planet, making the planet a
hellish, contorted and grotesque landscape ruled by the ever present
abyssal entity and its abominations.

The sky of the abyss is filled with dark clouds that block the sunlight from
shining through to the surface. Still, the planet itself is a hot and humid
atmosphere, and it seems that the scourges mainly nourishes itself from that
heat.

The abyss is populated by uncountable number of \hyperref[sec:Demons]{demons}
which aid the scourge with acquisition of new food, feeding and maintaining
the growth of the scourge on the planet itself. It is a truly hellish and
grotesque landscape, filled with roaming demons that constantly kill,
disembowel, or otherwise process any fresh food that is brought to them through
teleporters, and portals. These portals work by harvesting planar powers, and
thus many worlds - such as Aror, and \nameref{sec:Celestis} - are shielded from
direct demonic invasion from the Abyss.

Since the scourge always sends living creatures there to be killed by its
daemons, there is a small population of various species living in the abyss.
They are a mixture of other planar species, humanoids, and other intelligent
creatures that hide in the vast expanses of the abyss from the roaming demons.

The Abyss itself uses its vast psionic powers in an attempt to infiltrate, and
corrupt powerful psykers. While it seas the universe, and the landscape of
planes of existence as just one big pool of psionic energy, it can identify
particular powerful psykers, such as \nameref{sec:Emir}, or powerful psykers
of the \nameref{sec:Scions of Silence}, or the \nameref{sec:Helemic Order}.
After successfully taking over a powerful psyker it will attempt to coerce
it into opening a portal to the Abyss.
