\subsection{Celestis}
\label{sec:Celestis}

The planet of ``Celestis'' is the closest inhabited planet to Aror. It is the
home of the \nameref{sec:Aurelis}, a species of winged humanoids that have
generally been seen as allies by the people of Aror. It is the third planet
from its sun, which is confusingly also called Celestis.

Before the planets devastation, it was not unlike to Aror itself. It had two
snowy, cold polar regions to the north and south; lush rain forests and tropical
regions near the equator, as well as high mountain ranges and boreal forests.
The vast majority of the planets surface is covered with water, but it has one
massive continent that harbours all of the land-based live. The southern part
of the continent housed most of the Aurelis, while a minority of the Aurelis
lived in the northern part of the continent. The planets biggest city, and
capital for the Aurelis, called ``Gamos'' is located in the southern
hemisphere of the planet.

The planet was heavily devastated during an event called the \nameref{sec:War
in Heaven}. The \nameref{sec:Scourge} of the \nameref{sec:Abyss} managed to
infiltrate and settle on the northern part of planet, leading to a century
long conflict that devastated more than half of the land based life on the
planet. The scourge consumed most of the native land-based flora and fauna,
draining most land locked salt-water seas, lakes and rivers of the northern
hemisphere. While the scourge mostly consumed the north, leaving it a barren
and deserted wasteland, the south, and especially the land around Gamos
remained untouched. Most Aurelis from the north fled towards the capital,
settling the surrounding land by building villages, towns and cities.

The devastation of the planet's plant and animal life was so devastating, that
it lead to a shift in the planets overall climate towards hotter summers,
milder winters, and overall less rainfall. The remaining Aurelis struggle to
resettle the vast desert of the northern hemisphere, not only to restore the
previous beauty, and ecological diversity, but also to gain more land for
farming. This process has been slowly progressing for over eight millennia,
continuously threatened by the resurgence of small growths of the
\nameref{sec:Scourge} trapped in the desert, as well as new races arriving in
the desert. \nameref{sec:Gnolls} from Aror, as well as \nameref{sec:Giants}
have made the northern wasteland their home, and are contesting ownership of
the land from the Aurelis.

After the incursion of the scourge, the sages and wizards of Gamos have copied
the arcane technology from the dragons that blocks inter-planar travel. Although
isolation slowed the recovery of the people, and the planet, the risk of
another scourge invasion was deemed to high. Celestis can still be visited by
teleporting across the vast inter-stellar expanse, but it can no longer be
visited through planar shifts.

Nevertheless the planet remains habitable, and after defeating the Scourge
millennia ago, both the planet and its people are recovering. Especially Gamos
is often visited by Arorian traders, and diplomats, as many city kingdoms see
the Aurelis as their partners, or even allies.
