\subsection{Hell}
\label{sec:Hell}

\emph{Hell}, often also called the ``Layers of Hell'', or simply ``The
Layers'', is the home planet of the pacru'i (the \nameref{sec:Devils}). It is
a smaller planet tidally locked to its smaller, and dimmer sun. The planet is
known as the ``the layers'' among its inhabitants, but most others simply call
it hell.

The surface knows three distinct climate regions. The part of the planet that
faces the sun is an extremely hot, desert wasteland, simply called the
``empty''. Scouring, and howling storms ravage the surface, which are capable of
sanding off the flesh and skin of any unfortunate enough to be trapped there.
While the atmosphere is technically breathable by humanoids, the air is so hot
that it burns the lungs of anyone not inherently hardened against it like the
devils. The other half of the planet, that faces away from the sun, is a dark,
cold, and ice covered wasteland in which blizzards, and snow storms ravage
endlessly. Very few devils live on the surface of either side of the planet,
and the planet has no natural surface flora or fauna. The planet was chosen for
this particular reason, since it gives the \nameref{sec:Scourge} little to feast
upon should it ever land on the planet.

However between the two extremes lies a small narrow strip ranging from north
to south. Since this narrow strip is constantly seeing either the sun rise or
set, it is called the ``land of perpetual dawn''. Temperatures in this narrow
strip of land are moderate (between 20 and 30 degrees Celsius), and water can
be liquid, forming lakes and rivers. Only the most powerful of devils are
allowed to live there however, and most devils live underground.

Most of the pacru'i live underground, in a vast, multi-layered network of
connected caverns, and caves. Generally, the deeper the layer, the higher the
societal status of the devil living there. Very few caverns, and caves of the
layers are natural, and most have been carefully hewn into the stone. Devils
are generally considered to be impressive architects of stone, rivalling many
deep dwarven clans with their impressive structures, underground fortresses,
cities and towns. Devil engineers have purposefully redirected lava streams,
geothermic vents, and hot water sources to increase temperatures in the
caverns, or use them as power source for machinery.

Most of the layers are divided into smaller regions, each ruled by a single
baron or baroness of the devils. Each region may differ wildly in terms of
societal structure, rules, and inhabitants but all of them follow the basic
tenants of \nameref{sec:Baphomet}. Travelling to the layers without adequate
protection, or an invitation from a high-ranking devil is not advised.

\subsubsection{Hell's Currency}

The currency of hell are gold coins on the lowest level, and arcane
\nameref{sec:Implants} at the highest. A devil's rank, and power is equally
measured by the amount of lesser devils under his service, his material
wealth, as well as how many powerful implants the devil carries with him
or her. The higher ranking kings, dukes, presidents, and tyrants of hell
grant all of these to their most loyal servants, and in the case of implants,
it is \nameref{sec:Ishtar}'s job to oversee that they are installed. These
implants are what give the devils their seemingly innate magical powers,
but may as well be taken away should their service be found lacking. Those
devils that commit crimes have all their implants ripped out of them,
including the basic implant that protects them from the insanity inducing
psionic whispers of the \nameref{sec:Scourge}. These criminals are then either
banished from the layers, or into the second-to-last layer called
\emph{chasm}.

\subsubsection{Hell's Surface}
\label{sec:Hells Surface}

The surface of hell is the domain of \nameref{sec:Lilith}. While she
technically rules both the frozen wastes, and the desert wasteland, she
concentrates her rule on the land of perpetual dawn. There she has built an
oasis of relaxation, luxury and debauchery meant to draw in wealthy
travellers, and devils alike. The surface is generally considered the richest
region of the layers, as well as the most protected and secure. Travellers
will find themselves welcome there, as long as they can afford the food,
lodging, and brothels; and can afford to partake in betting, and gambling
around the various tournaments, blood sports, and arena fights.

\subsubsection{Boneyard}
\label{sec:Boneyard}

The boneyard is the vast network of tunnels, caves and caverns just beneath
the surface, and generally considered to be \nameref{sec:Ishtar}'s
realm. Countless devils are buried here, either in small outcroppings, large
bone piles, or lying in the vast caverns slowly rotting away. It is from this
horrible sight of death and decay, that the boneyard gets its name. Many
devils buried here died unnatural deaths, either by accidents or by losing
their battles against their wounds or illnesses under the care of Ishtar's
doctors and nurses. It is also home to many lower ranking devils, such
tieflings, succubi or Erinye, as Ishtar's rulings are as fair as they are
harsh. Living in the Boneyard comes with its own risks, as many followers of
Ishtar regularly abduct its inhabitants for experiments, or to harvest their
organs. The work done by devils so close to decaying corpses comes with an
increased risk of illnesses, and infections.

\subsubsection{Forest}
\label{sec:Forest}

The ``Forest'' lies just beneath the Boneyard, and contains vast, and large
natural cavers that contain the majority of the layer's water supply. The
forest is ruled over by the Belial, hell's ruthless general and army
commander. Here the devils, under Belial's watch, use the water to grow large
bio-luminescent fungi. The wood of those fungi is used as a building material,
while its flesh can be cooked and consumed. The forest is the richest region
in terms of fresh water, food, and basic materials, and is thus often raided
by the other layers. Belial thus keeps a large standing army, who is responsible
for defending his resources, goods, and materials. The Forest is a perpetual
battle ground, where the raiders and defenders fight for every centimetre of
land, and every last barrel of food or water.

\subsubsection{Treasury}
\label{sec:Treasury}

The treasure sits firmly beneath the forest, and is considered
\nameref{sec:Asmoday}'s realm. The name is a bit misleading, as the Treasury
is actually sprawling metropolis, where most of the devils of the layers live,
and work. It is filled with countless arcane and scientific laboratories,
smithies, workshops and factories, producing complex goods, weapons and arcane
artefacts. It is generally considered safe for outsiders to visit, and those
that do travel here may find them able to bargain for artefacts, lost arcane
knowledge, or the souls of those unfortunate enough to have been made servants
of the layers. Asmoday rules over the treasury with an iron fist from the
central spire, and by the force of his many arcane servants, and proteges,
such as \nameref{sec:Forneus}.

\subsubsection{Chasm}
\label{sec:Chasm}

The ``Chasm'' extends beneath the treasury, and is an uncivilised, barren land
filled with deep pits, jagged and sharp rocks, and streams of molten lava. Its
endlessly twisting tunnels form a maze, very few known how to escape from once
you have been trapped inside. Only the most savage, feral and ruthless devils
survive this place, and it is avoided by most other devils, and visitors. Even
though this realm has no formal ruler, it is the home to the
\nameref{sec:Runemaster}, and his minions. Most devils that break the tenants
of hell are sent to chasm into exile. Traversing the Chasm is required by
those who seek to venture deeper into the layers.

\subsubsection{Sanctum}
\label{sec:Sanctum}

Those that successfully traverse the deadly maze of the chasm reach the
``Inner Sanctum'' (or just the Sanctum). It is the deepest layer of the pit,
and thus the seat of power of \nameref{sec:Baphomet}, and his most trusted
general \nameref{sec:Beleth}. The sanctum's caverns, and caves are filled with
shrines, churches and cathedrals erected to worship Baphomet. Many of its
inhabitants are priests, inquisitors and soldiers that enforce his will upon
the layers of hell. Most devils that travel here do so either as a form of
pilgrimage, or proposition before the emperor of hell himself. Very few
actually get to meet him, as Beleth, his right hand maiden, welcomes most of
his visitors on his behalf.
