\section{Aurelis}

Aurelis are race of winged humanoid creatures. Angels are very powerful
Aurelis, and thus keep the \emph{Angel Traits} instead of gaining the
\emph{Aurelis Traits}.

\subsection{Aurelis Traits}
\begin{itemize}[noitemsep]
  \item Darkvision out to 60 feet, and low light vision.
  \item Resistance to acid 10, cold 10, and immunity to petrifaction
  \item +4 racial bonus to saves against poison and disease.
  \item -2 bonus to constitution
  \item +4 bonus to charisma and wisdom.
  \item Flight: all Aurelis can fly, unless they wear medium or heavy armour,
    then their flight is reduced to gliding towards the ground.
  \item Tongues (Su): All Aurelis can speak with any creature that has a
    language, as though using a \emph{tongues} spell (CL is equal to HD).
    This ability is always active.
\end{itemize}

\subsection{Aurelis Commoner}
\label{sec:monster:Aurelis Commoner}

\begin{35e}{\Large{Aurelis Commoner}}
  \srditem{Size/Type}{Medium Outsider (Aurelis, Extraplanar)}
  \srditem{Hit Dice}{3d8 (13 HP)}
  \srditem{Initiative}{+5}
  \srditem{Speed}{30 ft., fly 100 ft. (good)}
  \srditem{Armour Class}{11 (+1 dex), touch 10, flat-footed 11}
  \srditem{BAB}{+3 / +4}
  \srditem{Attack}{+1 Heavy Mace +5 (1d8+2) or slam +4 (1d8+1)}
  \srditem{Full Attack}{+1 Heavy Mace +5 (1d8+2) or slam +4 (1d8+1)}
  \srditem{Space/Reach}{5 ft./5 ft.}
  \srditem{Special Attacks}{-}
  \srditem{Special Qualities}{DR 5/evil, darkvision 60 ft., low light vision,
    resistance to acid 10 and cold 10, immunity to petrifaction}
  \srditem{Saves}{Fort +4 (+8 vs. poison), Reflex +3, Will +4}
  \srditem{Abilities}{Str 13, Dex 11, Con 10, Int 10, Wis 13, Cha 12}
  \srditem{Skills}{Concentration +7, Diplomacy +7, Escape Artist +6, Hide +6,
    Intimidate +7, Listen +9, Sense Motive +7, Spot +9}
  \srditem{Feats}{Alertness, Improved Initiative}
  \srditem{Environment}{Aurelis}
  \srditem{Organisation}{Solitary, pair, squad (3-5) or large organisations
    (ca. 100 or more)}
  \srditem{Challenge Rating}{3}
  \srditem{Treasure}{Normal coins, double goods, standard items}
  \srditem{Alignment}{Any good or lawful neutral}
  \srditem{Advancement}{By character class}
  \srditem{Level Adjustment}{+2}
\end{35e}

\subsection{Aurelis Guardian}
\label{sec:monster:Aurelis Guardian}

\begin{35e}{\Large{Aurelis, Level 8 Paladin}}
  \srditem{Size/Type}{Medium Outsider (Aurelis, Extraplanar)}
  \srditem{Hit Dice}{3d8+8d10+36 (93 HP)}
  \srditem{Initiative}{+4}
  \srditem{Speed}{30 ft., Glide (60 ft.) (Good)}
  \srditem{Armour Class}{25 (+10 Armor, +5 Shield), touch 10, flat-footed 25}
  \srditem{BAB}{+11 / +17}
  \srditem{Attack}{+3 Bastard Sword of Frost +20 (1d8+6) 17-20x2}
  \srditem{Full Attack}{+3 Bastard Sword of Frost +20/+15/+10 (1d8+6) 17-20x2}
  \srditem{Space/Reach}{5 ft./5 ft.}
  \srditem{Special Attacks}{-}
  \srditem{Special Qualities}{DR 5/evil, darkvision 60 ft., low light vision,
    resistance to acid 10 and cold 10, immunity to petrifaction}
  \srditem{Saves}{Fort +16 (+20 vs. poison), Reflex +8, Will +11}
  \srditem{Abilities}{Str 22, Dex 10, Con 16, Int 8, Wis 16, Cha 22}
  \srditem{Skills}{Concentration +7, Diplomacy +7, Escape Artist +6, Hide +6,
    Intimidate +7, Listen +9, Sense Motive +7, Spot +9}
  \srditem{Feats}{Alertness, Improved Initiative, Power Attack, Cleave,
    Weapon Proficiency (Bastard Sword), Improved Critical (Bastard Sword)}
  \srditem{Special}{Aura of good, Detect Evil, Smite Evil 2/day, Aura of
    courage, Lay on hands, Divine Health, Turn Undead, Special Mount, Remove
    Disease 1/week}
  \srditem{Spells}{Divine Favour 1/day, Protection from Evil 1/day, Zone of
    Truth 1/day}
  \srditem{Equipment}{Gloves of Strength +5, Belt of Constitution +4, Ring of
    Charisma +4, Cloak of Resistance +3, +3 Half Plate, +2 Bastard Sword of
    Frost, +3 Large Steel Shield}
  \srditem{Environment}{Aurelis}
  \srditem{Organisation}{Solitary, pair, squad (3-5)}
  \srditem{Challenge Rating}{13}
  \srditem{Treasure}{Normal coins, double goods, standard items}
  \srditem{Alignment}{Lawful good}
  \srditem{Advancement}{By character class}
  \srditem{Level Adjustment}{+2}

  His abilities before racial modifiers and level increases were: Str 15, Dex
  10, Con 14, Int 8, Wis 12, Cha 13.
\end{35e}
