\subsection{Daemons}
\label{sec:monsters:Daemons}

\subsection{Daemon Traits}
\label{sec:Daemon Traits}

\begin{itemize}[noitemsep]
  \item Type changes to ``daemon'' (Corporeal Daemon)
  \item d12 sided hit dice
  \item Base attack bonus equal to total HD
  \item Good reflex and will saves
  \item Skill points equal to (4 + Int modifier, minimum 1) per Hit Die, with
    quadruple skill points for the first Hit Die.
  \item Immunity to petrifaction.
  \item Not at risk of death from massive damage.
  \item Daemons do not eat, sleep or breathe.
  \item Proficient with light armour, simple weapons, their natural attacks,
    and any armour, weapons or equipment it is described as wearing or using.
  \item \emph{Manifest Body (Ex)}: Daemons are free souls roaming the land,
    valleys and mountains that can manifest a body at will. If the body is
    killed, their spirits return to the soul well. It takes them usually 1d4
    months before they can reappear again.
  \item \emph{Spirit Form (Ex)}: When not in a mortal form, daemons are
    considered free spirits or souls, and gain those traits accordingly.
  \item \emph{Aura (Ex)}: Powerful evil, or good aligned daemons have an
    \emph{aura of good or evil} surrounding them (see detect evil spell/good
    spells for further information).
\end{itemize}

\subsubsection{Black Hounds}
\label{sec:monsters:Black Hounds}

\begin{35e}{\Large{Black Hounds}}
  \srditem{Size/Type}{Medium Daemon}
  \srditem{Hit Dice}{4d12+12 (38 HP)}
  \srditem{Initiative}{+2}
  \srditem{Speed}{40 ft.}
  \srditem{Armour Class}{14 (+2 dexterity +2 natural armour), 12 touch, 12
    flat footed
  }
  \srditem{BAB / Grapple}{+4/+11}
  \srditem{Attack}{Bite +11 melee (1d6+7)}
  \srditem{Full Attack}{Bite +11 melee (1d6+7)}
  \srditem{Space/Reach}{5 ft./5 ft.}
  \srditem{Special Qualities}{Daemon traits, Trip (Ex), Selective Presence
    (Ex), Harbingers of Death (Ex)
  }
  \srditem{Saves}{Fort +4, Ref +6, Will +6}
  \srditem{Abilities}{Str 24, Dex 14, Con 16, Int 10, Wis 14, Cha 10}
  \srditem{Skills}{Listen (9), Sense Motive (11), Spot (9), Survival (9)}
  \srditem{Feats}{Negotiator, Run}
  \srditem{Environment}{Any}
  \srditem{Organisation}{Solitary}
  \srditem{Challenge Rating}{4}
  \srditem{Treasure}{None}
  \srditem{Alignment}{Always Neutral}
  \srditem{Advancement}{7-8 HD (Large)}
  \srditem{Trip (Ex)}{A Black Hound that hits with a bite attack can attempt
    to trip its opponent as a free action without making a touch attack, or
    provoking an attack of opportunity. If the attempt fails, the opponent
    cannot react to trip the Black Hound.
  }
  \srditem{Selective Presence (Ex)}{A Black Hound can, at will, opt to appear
    only to those it wishes. This ability functions like a continuous
    combination of \emph{Greater Invisibility}, and \emph{Pass without Trace},
    but is a soul-based ability. Not even \emph{True Seeing} can thus reveal
    the presence of the hound. \emph{Soul Sight} will still reveal the presence
    of the Hound's soul, allowing a soul caster to spot a hidden Black Hound.
  }
  \srditem{Harbingers of Death (Ex)}{A Black Hound may perform a \emph{Coup de
      Grace} against willing targets, and against those who are immune to
    critical hits. If it performs a \emph{Coup de Grace} the critical
    multiplier for this attack is increased by 2 (for a total of x3 for
    the bite).
  }
\end{35e}
