\section{Demons}
\label{sec:Demons}

\subsection{Demon Traits}
\label{sec:Demon Traits}

\begin{itemize}[noitemsep]
  \item Immunity to electricity and poison
  \item Resistance to acid 10, cold 10, and fire 10
  \item \emph{Puppets of the Scourge (Ex)}: All spell-like abilities, and some
    supernatural abilities of demons that reproduce spell effects (such as
    true seeing of a Balor) are gifts granted by the scourge through
    telepathy.  As long as the demon moves on the surface of the scourge it
    gains \emph{blindsight} 30 ft. These abilities are lost should they be
    severed by the scourge, or suppressed by effects that also effect psionic
    abilities.
  \item \emph{Telepathic Link (Ex)}: As long as a telepathic link between the
    scourge and the demon exists, the scourge can see, smell, hear, and feel
    through the demons by utilising its senses. This also gives demons telepathy
    between them and the scourge, as well as between each other.
  \item \emph{Hive Mind (Ex)}: Demons have no inherent higher intelligence as it
    is granted by the scourge. If the link to mother scourge is severed,
    demons are reduced to 3 intelligence until a psionic link is established
    again. Such demons will revert to a more primal state, following basic
    instincts such as the search food, procreation and defending territory.
\end{itemize}

\subsection{Tjort}
\label{sec:Tjort}

\begin{35e}{\Large{Tjort}}
  \srditem{Size/Type}{Medium Outsider (Extra Planar, Evil, Chaotic, Demon)}
  \srditem{Hit Dice}{6d8+30 (52 HP)}
  \srditem{Initiative}{+5}
  \srditem{Speed}{40 ft.}
  \srditem{Armour Class}{19 (+1 dex, +8 natural), touch 11, flat-footed 18}
  \srditem{BAB/Grapple}{+5 / +10}
  \srditem{Attack}{Claws +10 1d8+6}
  \srditem{Full Attack}{2 Claws +10 1d8+6}
  \srditem{Space/Reach}{5 ft./5 ft.}
  \srditem{Special Attacks}{Rend 2d6+6}
  \srditem{Special Qualities}{Damage reduction 10/cold iron or good,
    darkvision 60 ft., immunity to electricity and poison, resistance to acid
    10, cold 10, fire 10, spell resistance 12, telepathy 100 ft., blindsight
    30 ft. Puppet of the Scourge (Ex), Telepathic Link (Ex), Hive Mind (Ex)
  }
  \srditem{Saves}{Fort +10, Reflex +6, Will +6}
  \srditem{Abilities}{Str 22, Dex 12, Con 20, Int 8, Wis 13, Cha 16}
  \srditem{Skills}{Climb +18, Escape Artist +9, Jump +18, Hide +9, Listen +9,
    Move Silently +9, Search +9, Survival +9}
  \srditem{Skills}{A Tjort has a +4 racial bonus to climb and jump checks, can
    always choose to take 10 on a climb check, even if it is rushed or
    threatened.
  }
  \srditem{Feats}{Power Attack, Improved Initiative, Improved Natural Attack
    (Claws)
  }
  \srditem{Environment}{Abyss}
  \srditem{Organisation}{Solitary, pair}
  \srditem{Challenge Rating}{4}
  \srditem{Treasure}{Standard}
  \srditem{Alignment}{Chaotic Evil}
  \srditem{Advancement}{7-10 HD (Large)}
  \srditem{Level Adjustment}{-}
\end{35e}

Tjorts are humanoid male creatures with goat legs, horribly deformed faces
and overly muscular appearance. They are the abyss' worker and defence drones,
and will attack anything that is not a demon but wanders the abyss.

\subsection{Onoskelis}
\label{sec:Onoskelis}

\begin{35e}{\Large{Onoskelis}}
  \srditem{Size/Type}{Medium Outsider (Extra Planar, Evil, Chaotic, Demon)}
  \srditem{Hit Dice}{4d8+12 (30 HP)}
  \srditem{Initiative}{+5}
  \srditem{Speed}{30 ft.}
  \srditem{Armour Class}{16 (+1 dex, +5 natural), touch 11, flat-footed 15}
  \srditem{BAB/Grapple}{+4 / +4}
  \srditem{Attack}{Claws +4 1d6+4}
  \srditem{Full Attack}{2 Claws +4 1d6+4 and bite +2 1d4+4}
  \srditem{Space/Reach}{5 ft./5 ft.}
  \srditem{Special Attacks}{-}
  \srditem{Special Qualities}{Damage reduction 5/cold iron or good,
    darkvision 60 ft., immunity to electricity and poison, resistance to acid
    10, cold 10, fire 10, spell resistance 10, telepathy 100 ft., blindsense
    60 ft., blindsight 30ft., Puppet of the Scourge (Ex), Telepathic Link
    (Ex), Hive Mind (Ex), Blind
  }
  \srditem{Saves}{Fort +7, Reflex +5, Will +7}
  \srditem{Abilities}{Str 18, Dex 12, Con 16, Int 8, Wis 16, Cha 10}
  \srditem{Skills}{Climb +15, Escape Artist +8, Jump +15, Hide +8, Listen +10,
    Move Silently +10, Search +10, Survival +10}
  \srditem{Skills}{Am onoskelis has a +4 racial bonus to climb and jump
    checks, can always choose to take 10 on a climb check, even if it is
    rushed or threatened.
  }
  \srditem{Feats}{Power Attack, Improved Initiative}
  \srditem{Environment}{Abyss}
  \srditem{Organisation}{Solitary, pair}
  \srditem{Challenge Rating}{3}
  \srditem{Treasure}{Standard}
  \srditem{Alignment}{Chaotic Evil}
  \srditem{Advancement}{4-6 HD (Medium)}
  \srditem{Level Adjustment}{-}
\end{35e}

Onoskelis are female humanoid creatures with goat legs, that roam the layers
of abyss, hunting for anything that could be edible. They are blind, and have
a large, elongated head that is one huge mouth with large claws. Onoskelis
track and kill prey by scent, sound and through any information the scourge
provides through the telepathic link. They will attack anything that roams in
the abyss, but are avoided by all other demons as commanded by the scourge
itself.
