\section{Devils}
\label{sec:monster:Devils}

\subsection{Baphomet}
\label{sec:monster:Baphomet}

Baphomet is the ruler and king of all of hell.

\begin{35e}{\Large{Baphomet}}
  \srditem{Class}{10th Level Paladin of Tyranny}
  \srditem{Size/Type}{Large Outsider (Pit fiend)}
  \srditem{Hit Dice}{18d8+144+10d10+130 (410 hp)}
  \srditem{Initiative}{+12}
  \srditem{Speed}{40 ft. (8 squares), fly 60 ft. (average)}
  \srditem{Armour Class}{40 (-1 size, +8 Dex, +23 natural), touch 17,
    flat-footed 32}
  \srditem{BAB / Grapple}{+28/+50}
  \srditem{Attack}{+5 Unholy Greatsword of Hell Fire +51 3d6+31 +2d6 (Fire)}
  \srditem{Full Attack}{+5 Unholy Greatsword of Hell Fire +51/+46/+41/+36/+31
    3d6+31 +2d6 (Fire) and 2 wings +44 melee (2d6+6) and bite +44 melee (4d6+6
    plus poison plus disease) and tail slap +44 melee (2d8+6)
  }
  \srditem{Space/Reach}{10 ft./10 ft.}
  \srditem{Special Attacks}{Constrict 2d8+26, fear aura, improved grab,
    spell-like abilities, summon devil
  }
  \srditem{Special Qualities}{Damage reduction 15/good and silver, darkvision
    60 ft., immunity to fire and poison, resistance to acid 10 and cold 10,
    regeneration 5, see in darkness, spell resistance 32, telepathy 100 ft.
  }
  \srditem{Class Features}{Smite Good 3/day, Detect Good, Aura of Evil, Divine
    Grace, Deadly Touch, Aura of Despair, Divine Health, Cause Disease 2/week}
  \srditem{Spells Known}{1: Divine Favour, Read Magic 2: Undetectable Alignment}
  \srditem{Saves}{Fort +39, Ref +35, Will +37}
  \srditem{Abilities}{Str 47, Dex 27, Con 37, Int 26, Wis 26, Cha 36}
  \srditem{Skills}{Balance +10, Bluff +40, Climb +39, Concentration +34,
    Diplomacy +28, Disguise +40 (+42 acting), Hide +25, Intimidate +42, Jump
    +45, Knowledge (arcana) +35, Knowledge (nature) +10, Knowledge (the
    planes) +35, Knowledge (religion) +35, Listen +29, Move Silently +29,
    Search +29, Sense Motive +21, Spellcraft +31, Spot +35, Survival +14 (+10
    on other planes, +10 when tracking), Tumble +31
  }
  \srditem{Feats}{Cleave, Great Cleave, Improved Initiative, Iron Will,
    Multiattack, Power Attack, Quicken Spell-Like Ability (fireball)
  }
  \srditem{Items}{Baphomet's Will (Ring) (+10 Charisma, +5 Resistance),
    Baphomet's Might (Ring) (+10 Strength, +10 Constitution), Baphomet's Reign
    (Greatsword) (+5 Unholy Large Greatsword of Hell Fire)
  }
  \srditem{Environment}{Layers of Hell}
  \srditem{Organisation}{Solitary}
  \srditem{Challenge Rating}{30}
  \srditem{Treasure}{Double Gold, Double Goods, Double Items}
  \srditem{Alignment}{Lawful Evil}
  \srditem{Advancement}{By character class}
\end{35e}

\subsection{Beleth}
\label{sec:monster:Beleth}

Beleth rules over a legion of succubi and incubi, and is mainly responsible
for striking deals with mortals. She also offers arbitration, counselling in
law, and teaches the fundamentals of law and rights.

\begin{35e}{\Large{Beleth}}
  \srditem{Class}{6th Level Bard}
  \srditem{Size/Type}{Normal Outsider (Succubus)}
  \srditem{Hit Dice}{6d8+6d6+36 (81 hp)}
  \srditem{Initiative}{+1}
  \srditem{Speed}{30 ft., fly 50 ft. (average)}
  \srditem{Armour Class}{20 (+1 Dex, +9 natural), touch 11, flat-footed 19}
  \srditem{BAB / Grapple}{+10/+11}
  \srditem{Attack}{Claw +11 melee (1d6+1)}
  \srditem{Full Attack}{2 claws +11 melee (1d6+1)}
  \srditem{Space/Reach}{5 ft./5 ft}
  \srditem{Special Attacks}{Energy drain, spell-like abilities, summon devil}
  \srditem{Special Qualities}{Damage reduction 10/cold iron or good,
    darkvision 60 ft., immunity to electricity and poison, resistance to acid
    10, cold 10, and fire 10, spell resistance 18, telepathy 100 ft., tongues
  }
  \srditem{Class Features}{Bardic Music, Bardic Knowledge, Countersong,
    Fascinate, Inspire Courage +1, Inspire Competence, Suggestion
  }
  \srditem{Spells Known}{\textbf{0:} Detect Magic, Dancing Lights, Fleeting
    Fame, Ghost Sounds, Read Magic, Prestidigitation. \textbf{1:} Cure Light
    Wounds, Improvisation, Invisibility (Swift). \textbf{2:} Alter Self, Detect
    Thoughts
  }
  \srditem{Saves}{Fort +8, Ref +11, Will +22}
  \srditem{Abilities}{Str 13, Dex 13, Con 21, Int 16, Wis 14, Cha 34}
  \srditem{Skills}{Bluff +36, Concentration +10, Diplomacy +29, Disguise +36*
    (+38 acting), Escape Artist +10, Gather Information +21, Hide +10,
    Intimidate +36, Knowledge (Arcana, Local) +21, Listen +19, Move Silently
    +10, Perform (Oratory) +26, Search +12, Sleight of Hand +10, Spot +19,
    Survival +2 (+4 following tracks), Use Rope +1 (+3 with bindings)
  }
  \srditem{Feats}{Dodge, Mobility, Persuasive, Force of Personality, Heighten
    Spell, Quicken Spell, Obtain Familiar (Imp)
  }
  \srditem{Items}{Beleth's Fine Garments (Robe) (+8 AC, +8 Charisma), Beleth's
    Conviction (Ring) (+4 to all CHA skills), Hellfire Necklace (+8
    Constitution, +5 Resistance)
  }
  \srditem{Environment}{Layers of Hell}
  \srditem{Organisation}{Solitary}
  \srditem{Challenge Rating}{7}
  \srditem{Treasure}{Standard}
  \srditem{Alignment}{Neutral Evil}
  \srditem{Advancement}{By character class}
\end{35e}

\subsection{Hellfire Spirit}
\label{sec:monster:Hellfire Spirit}

Hellfire spirits are free souls that wander that layers of hell. They
sometimes take possession of devils, but most of the time hide from the devils
to survive. They are in constant agony, as the hot climate and heat of the
layers of hell constantly burns them. They appear as translucent ghosts that
have been set aflame. Some burn red, while others burn blue. Most of them have
gone mad from the pain, the horrors of the layers of hell, and thus attack
anything and everyone that roams hell.

\begin{35e}{\Large{Hellfire Spirit}}
  \srditem{Size/Type}{Medium Outsider (Spirit, Corporeal)}
  \srditem{Hit Dice}{4d12+4}
  \srditem{Initiative}{+1}
  \srditem{Speed}{30 ft. fly (good)}
  \srditem{Armour Class}{12 (+2 dex.), 12 touch, 10 flat-footed}
  \srditem{BAB / Grapple}{3 / -}
  \srditem{Attack}{+3 incorporeal touch (melee) (1d6 soul damage)}
  \srditem{Full Attack}{+3 incorporeal touch (melee) (1d6 soul damage)}
  \srditem{Space/Reach}{5 ft./5 ft.}
  \srditem{Special Qualities}{Darkvision 60 ft., incorporeal traits, undead
    traits, spirit traits, Possession (Ex), Telepathy 60 ft., Fire Shield (Ex)
  }
  \srditem{Saves}{Fort: +2, Ref: +3, Will: +4}
  \srditem{Abilities}{Str 10, Dex: 14, Con: 13, Int: 10, Wis: 12, Cha: 18}
  \srditem{Skills}{Hide +9, Listen +10, Move Silently +9, Spot +10}
  \srditem{Feats}{Alertness, Dodge}
  \srditem{Environment}{Layers of Hell}
  \srditem{Organisation}{Solitary}
  \srditem{Challenge Rating}{4}
  \srditem{Treasure}{None}
  \srditem{Alignment}{Any, but often chaotic evil}
  \srditem{Advancement}{4-9 HD (Medium)}
  \srditem{Possession (Ex)}{Hellfire Spirits may attempt to possess bodies as
    stated in the \nameref{sec:Possession} rules. Their base DC is \emph{17}.
  }
  \srditem{Fire Shield (Ex)}{Hellfire Spirits are under the continuous effect of
    \emph{Fire Shield} as the spell (CL 3). Whether it is cold or fire, should
    be determined at random.
  }
\end{35e}

\subsection{Lilith}
\label{sec:monster:Lilith}

\nameref{sec:Lilith}, or the ``scarlet whore'', rules over the hell's
surface. She rules over many legions of various devils, and is mainly
responsible for striking deals and the defence of the layers of hell. Unlike
other succubi she no longer has any wings, and thus cannot fly. Like all other
generals of hell, she draws her power from directly Baphomet.

\begin{35e}{\Large{Lilith, 17th Level Warlock}}
  \srditem{Size/Type}{Medium Outsider (Succubus)}
  \srditem{Hit Dice}{6d8+17d6+90 (176 HP)}
  \srditem{Initiative}{+1}
  \srditem{Speed}{30 ft.}
  \srditem{Armour Class}{35 (+1 Dex, +9 Natural, 10 Armor, 5 Protection),
    touch 11, flat-footed 34}
  \srditem{BAB / Grapple}{+18/+19}
  \srditem{Attack}{+5 Shock Scimitar +24 1d6+1 18-20x2}
  \srditem{Full Attack}{+5 Shock Scimitar +25/+17/+12/+7 1d6+1 18-20x2}
  \srditem{Space/Reach}{5 ft./5 ft.}
  \srditem{Special Attacks}{Energy drain, spell-like abilities, summon demon}
  \srditem{Special Qualities}{Damage reduction 14/cold iron, darkvision 60
    ft., immunity to electricity and poison, resistance to acid 10, cold 10,
    fire 10, sonic 5, and electricity 5 spell resistance 18, telepathy 100
    ft., tongues
  }
  \srditem{Class Features}{Eldritch Blast (8d6), Detect Magic, Deceive Item,
    Imbue Item, Fiendish Resilience (5), Energy Resistance (5)}
  \srditem{Invocations Known}{\emph{Least}: Baleful Utterance, Eldritch Spear,
    Otherworldly Whispers. \emph{Lesser}: Eldritch Chain, Relentless
    Dispelling, Flee the Scene. \emph{Greater}: Noxious Blast, Nightmares Made
    Real, Devil's Whispers. \emph{Dark}: Binding Blast
  }
  \srditem{Saves}{Fort +20, Ref +16, Will +29}
  \srditem{Abilities}{Str 13, Dex 13, Con 21, Int 16, Wis 14, Cha 38}
  \srditem{Skills}{Bluff +45, Concentration +10, Diplomacy +38, Disguise +23*
    (+27 acting), Escape Artist +10, Hide +10, Intimidate +45, Knowledge (any
    one) +12, Listen +29, Move Silently +10, Search +12, Sense Motive +22, Spot
    +29, Survival +2 (+4 following tracks), Use Rope +1 (+3 with bindings),
    Use Magic Device +44
  }
  \srditem{Feats}{Dodge, Mobility, Persuasive, Mortalbane (+2d6 5/day), Maximise
    Spell, Force of Personality, Obtain Familiar, Improved Familiar}
  \srditem{Items}{+8 Charisma Cloak, +8 Constitution Belt, Lilith's Garments
    (+10 Armor Bonus, +5 Protection), Lilith's Seal (+5 Resistance, Permanent
    Freedom of Movement)
  }
  \srditem{Environment}{Layers of Hell}
  \srditem{Organisation}{Solitary}
  \srditem{Challenge Rating}{20}
  \srditem{Treasure}{Double Gold, Double Goods, Double Items}
  \srditem{Alignment}{Neutral Evil}
  \srditem{Advancement}{By character class}

  Lilith has a female succubi called \emph{Eris} as familiar.
\end{35e}
