\section{Golems}

\subsection{Everblack Golem}
\label{sec:monster:Everblack Golem}

Everblack golems come in many different shapes and sizes. But the most common
are crafted and constructed similar to stone golems. They are shaped out of
two and a half metric tons of composite everblack (and are thus expensive to
make), but have many benefits over other constructs. As any other Golem they
follow the will of their creator.

\begin{35e}{\Large{Everblack Golem}}
  \srditem{Size/Type}{Large Construct}
  \srditem{Hit Dice}{18d10+30 (129 HP)}
  \srditem{Initiative}{+1}
  \srditem{Speed}{20 ft.}
  \srditem{Armour Class}{30 (-1 Size, -1 Dex, +22 Natural)}
  \srditem{BAB / Grapple}{+12/+28}
  \srditem{Attack}{Slam +23 melee (2d10+11)}
  \srditem{Full Attack}{2 Slams +23 melee (2d10+11)}
  \srditem{Space/Reach}{10 ft./10 ft.}
  \srditem{Special Qualities}{Construct traits, damage reduction 10/bludgeoning
    and adamantine, darkvision 60 ft., complete immunity to energy, low-light
    vision, spell like abilities
  }
  \srditem{Saves}{Fort +6, Ref +5, Will +6}
  \srditem{Abilities}{Str 33, Dex 9, Con -, Int -, Wis 11, Cha 1}
  \srditem{Skills}{-}
  \srditem{Feats}{-}
  \srditem{Environment}{Any}
  \srditem{Organisation}{Solitary or gang (2-4)}
  \srditem{Challenge Rating}{15}
  \srditem{Treasure}{None}
  \srditem{Alignment}{Always Neutral}
  \srditem{Advancement}{19-24 HD (Large); 25-54 HD (Huge)}
  \srditem{Dispel Magic, Greater (Su)}{An Everblack Golem can use Dispell Magic,
    Greater, as the spell, as a free action once every 1d4+1 rounds. The effect
    has a range of 30 ft. with a dispel check of 1d20+13.
  }
  \srditem{Complete Immunity to Energy (Ex)}{An Everblack Golem is immune to all
    forms of energy damage, including non-typed magical damage (such as from a
    magic missile or destruction spell), energy damage from magical weapons, or
    energy damage from environmental effects. It will absorb that damage, and
    release that damage onto the next foe the golem strikes with its slam
    attack. This charge is used up in the first successful melee attack the
    golem makes. The golem can only release one absorbed magical effect per
    slam attack, in the order it has absorbed them.
  }
  \srditem{Construction}{An Everblack Golem's body is sculpted out of two and
    a half tons of composite everblack costing about 5000 shards. Assembling
    the body requires a DC 32 Craft (Armorsmithing) check or a DC 32
    (Weaponsmithing) check.

    CL 16th, Craft Construct, Trap the Soul, Geas/Quest, Limited Wish, Caster
    must be at least 16th level; Price 25000 shard; Cost 10000 shard + 7000
    XP.
  }
\end{35e}
