\section{Ilians}
\label{sec:monster:Ilians}

\subsection{Arnak}
\label{sec:monster:Arnak}

Arnaks were once the worker class of the \nameref{sec:Ilians}. They rely on
their brute bodily strength, and their sharp teeth to fight enemies. Arnaks
that are still part of an Ilian society are remotely controlled through
psionic machinery, and will carry out their tasks ignoring others unless they
are a distraction or danger to themselves. Lone Arnaks that have been
separated from their societies will return to an aggressive, savage behaviour;
attacking and eating anything humanoid they can find.

\begin{35e}{\Large{Arnak}}
  \srditem{Size/Type}{Humanoid (Arnak)}
  \srditem{Hit Dice}{8d8+8 (48 HP)}
  \srditem{Initiative}{+7}
  \srditem{Speed}{40 ft.}
  \srditem{Armour Class}{16 (+3 Dex, +3 Natural), touch 13, flat-footed 13}
  \srditem{BAB / Grapple}{+8/+16}
  \srditem{Attack}{Slam +8 1d4+4}
  \srditem{Full Attack}{2 Slams +8 1d4+4 and Bite +9 2d6+4 plus venom}
  \srditem{Space/Reach}{5 ft./5 ft.}
  \srditem{Special Attacks}{-}
  \srditem{Special Qualities}{Track, Scent (Ex), Blindsense (Ex), Hibernation
    (Ex), Arnak Spawn (Ex), Telepathic (Ex)
  }
  \srditem{Saves}{Fort +3, Ref +9, Will +4}
  \srditem{Abilities}{Str 18, Dex 16, Con 12, Int 8, Wis 13, Cha 8}
  \srditem{Skills}{Listen +7, Spot +6}
  \srditem{Feats}{Improved Initiative, Weapon Focus (Bite), Improved Grapple}
  \srditem{Environment}{Underground}
  \srditem{Organisation}{Solitary, pair or pack (3-5)}
  \srditem{Challenge Rating}{8}
  \srditem{Treasure}{No coins, normal goods, no items}
  \srditem{Alignment}{Any (if part of an Ilian settlement), any evil (if alone)}
  \srditem{Advancement}{By character class}
  \srditem{Venom (Ex)}{Arnak deliver venom with each bite. Fortitude save DC: 20
    negates, or otherwise the victim is paralysed for 1d4+1 rounds.
  }
  \srditem{Hibernation (Ex)}{Arnak loses Blindsense and Scent except when
    within 5 ft. when in hibernation beneath a stalactite. An Arnak in
    hibernation gains \emph{regeneration 3}.
  }
  \srditem{Arnak Spawn (Ex)}{If an arnak has a humanoid creature in a grapple
    or pin it can attempt to inject an \emph{Arnak Spawn} into the creature as
    a free action. A reflex slave DC 17 allows a grappled humanoid creature to
    shake off the spawn. If the victim is pinned or otherwise at the mercy of
    the Arnak no saving throw is allowed. An arnak spawn will drain its host
    for 1 point of constitution per day until 4d4 days have passed or the host
    dies prematurely of constitution drain. If the victim dies prematurely, so
    will the spawn. Once the spawn has matured, it will burst from the victims
    chest dealing 4d6 points of damage (Fortitude DC:16 half). Victims with an
    arnak spawn in their body are considered \emph{diseased}.
  }
\end{35e}

\subsection{Elnak}
\label{sec:monster:Elnak}

Elnak are the crafting and tinkerer caste of the Ilians, and try to avoid open
conflict. If they are forced to fight, they prefer to rely on their limited
psionic powers, and will fall back to wielding blades once their psionic
powers have been spent.

\begin{35e}{\Large{Elnak}}
  \srditem{Size/Type}{Humanoid (Arnak)}
  \srditem{Hit Dice}{6d8 (28 HP)}
  \srditem{Initiative}{+3}
  \srditem{Speed}{30 ft.}
  \srditem{Armour Class}{14 (+3 Dex, +1 Natural), touch 13, flat-footed 11}
  \srditem{BAB / Grapple}{+4/+4}
  \srditem{Attack}{+1 Shortsword +8 1d6+1 19-20x2}
  \srditem{Full Attack}{+1 Shortsword +8 1d6+1 19-20x2}
  \srditem{Space/Reach}{5 ft./5 ft.}
  \srditem{Special Attacks}{-}
  \srditem{Special Qualities}{Telepathic (Ex) (90 ft.)}
  \srditem{Psionic Power Points}{40}
  \srditem{Psionic Powers Known}{1: Call To Mind, Conceal Thoughts, Crystal
    Shard, Force Screen, Missive, Far Hand

    2: Energy Push, Concealing Amorpha, Identify (Psionic)

    3: Keen Edge (Psionic), Telekinetic Thrust, Energy Bolt
  }
  \srditem{Saves}{Fort +2, Ref +5, Will +5}
  \srditem{Abilities}{Str 10, Dex 16, Con 10, Int 18, Wis 10, Cha 8}
  \srditem{Skills}{Concentration +10, Craft (Psionic Machinery) +17, Knowledge
    (Arcana) +14, Knowledge (Psionics) +14, Psicraft +14, Spellcraft +14
  }
  \srditem{Feats}{Weapon Finesse, Toughness, Skill Focus (Craft Psionic
    Machinery)}
  \srditem{Environment}{Underground}
  \srditem{Organisation}{Solitary, pair, or as part of an Ilian settlement}
  \srditem{Challenge Rating}{6}
  \srditem{Treasure}{No coins, normal goods, no items}
  \srditem{Alignment}{Any}
  \srditem{Advancement}{By character class, often a psionic class such as Psion}
\end{35e}

\subsection{Karek}
\label{sec:monster:Karek}

Karek are the fighter and warrior class of the \nameref{sec:Ilians}. They were
powerful, both in physical prowess as well as in psionic might. Karek fought
in, and lead armies, worked as enforcers and police, and also ruled smaller
outposts or settlements. Kareks were engineered to be generals, cunning
strategists, as well as fierce, quick and deadly warriors. They were not front
line troops, that ``honour'' falls to the Arnaks, but instead specialist shock
troops and special forces. Karek have four arms, and thus wield a wide variety
of weapons accompanied by shield to protect themselves.

\begin{35e}{\Large{Karek}}
  \srditem{Size/Type}{Humanoid (Arnak)}
  \srditem{Hit Dice}{12d8+48 (102 HP)}
  \srditem{Initiative}{+10}
  \srditem{Speed}{40 ft.}
  \srditem{Armour Class}{33 (+6 Dex, +4 Natural, +6 shield, +7 armour), touch
    16, flat-footed 27}
  \srditem{BAB / Grapple}{+12/+20}
  \srditem{Attack}{+22 Primary +4 Heavy Pick 1d8 19-20x4}
  \srditem{Full Attack}{+22/+17/+12 Primary +4 Heavy Pick 1d8 19-20x4, and +20
    with +4 Warhammer 1d8x3, and +20 with +4 Longsword 1d8 19-20x2
  }
  \srditem{Space/Reach}{5 ft./5 ft.}
  \srditem{Special Attacks}{-}
  \srditem{Special Qualities}{Telepathic (Ex) (90 ft.)}
  \srditem{Psionic Power Points}{55}
  \srditem{Psionic Powers Known}{1: Demoralize, Disable, Deceleration, Empty Mind

    2: Energy Push, Tongues (Psionic), Inflict Pain, Ego Whip

    3: Keen Edge (Psionic), Telekinetic Thrust

    4: Telekinetic Maneuver, Freedom of Movement (Psionic)
  }
  \srditem{Saves}{Fort +15, Ref +17, Will +7}
  \srditem{Abilities}{Str 26, Dex 22, Con 18, Int 15, Wis 10, Cha 15}
  \srditem{Skills}{Listen +15, Spot +15, Jump +23, Climb +23}
  \srditem{Feats}{Improved Initiative, Power Attack, Multi-Weapon Fighting,
    Combat Reflexes, Improved Critical (Heavy Pick)
  }
  \srditem{Equipment}{+4 Heavy Pick, +4 Warhammer, +4 Longsword, +4 Heavy
    Steel Shield, Cloak of Resistance +3, Ring of Protection +3, +3 Mithral
    Chainshirt
  }
  \srditem{Environment}{Underground}
  \srditem{Organisation}{Solitary, pair, or as part of an Ilian settlement}
  \srditem{Challenge Rating}{14}
  \srditem{Treasure}{Double coins, double items, no goods}
  \srditem{Alignment}{Any}
  \srditem{Advancement}{By character class, often a psionic class such as
    Psychic Warrior}
\end{35e}
