\section{Red Legion}
\label{sec:monster:Red Legion}

The Red Legion is the mainstay army of \nameref{sec:Morkan}, and is mostly made
up of battlefield conscripts: enslaved core humanoid races that have been forced
to fight when their villages have been raided and destroyed. Their captains are
usually Morkan citizens, and lead their conscripts into battle. Some squads are
also joined by a scout, who prefers to use bows and light weapons.

\subsection{Red Legionnaire}
\label{sec:monster:Red Legionnaire}

\begin{35e}{\Large{Red Legionnaire, 3th Level Warrior}}
  \srditem{Size/Type}{Medium Humanoid (Human)}
  \srditem{Hit Dice}{3d8}
  \srditem{Initiative}{+5}
  \srditem{Speed}{30 ft.}
  \srditem{Armour Class}{15 (+3 Armour, +1 Shield, +1 Dex), 11 touch, 14 flat
    footed}
  \srditem{BAB / Grapple}{+3 / +4}
  \srditem{Attack}{Battleaxe +4 1d8+1 (20x3) or Longbow +4 1d8 (20x3)}
  \srditem{Full Attack}{Battleaxe +4 1d8+1 (20x3) or Longbow +4 1d8 (20x3)}
  \srditem{Space/Reach}{5 ft./5 ft.}
  \srditem{Special Qualities}{-}
  \srditem{Saves}{Fort +3, Reflex +2, Will +0}
  \srditem{Abilities}{Str 13, Dex 12, Con 11, Int 10, Wis 9, Cha 8}
  \srditem{Skills}{Climb +4, Jump +4}
  \srditem{Feats}{Power Attack, Improved Initiative}
  \srditem{Equipment}{Battleaxe, Longbow, Arrows (20), Studded Leather, Light
    Wooden Shield}
  \srditem{Environment}{Any}
  \srditem{Organisation}{Solitary, pair, or squad (4-8) with a captain}
  \srditem{Challenge Rating}{3}
  \srditem{Treasure}{Normal gold, normal goods, normal items}
  \srditem{Alignment}{Any}
  \srditem{Advancement}{By character class}
\end{35e}

\subsection{Red Legion Captain}
\label{sec:monster:Red Legion Captain}

Captains of the Red Legion often lead a small squad of red legionnaires (4-8
men and women). These captains are often citizens of Morkan that chose to do
their civil service in the red legion.

\begin{35e}{\Large{Red Legion Captain, 6th Level Fighter}}
  \srditem{Size/Type}{Medium Humanoid (Dwarf)}
  \srditem{Hit Dice}{6d10+6 (40 HP)}
  \srditem{Initiative}{+7}
  \srditem{Speed}{30 ft.}
  \srditem{Armour Class}{22 (+6 Armour, +2 Shield, +2 Dex, +2 Prot.), 14
    touch, 20 flat footed}
  \srditem{BAB / Grapple}{+6 / +10}
  \srditem{Attack}{+1 Longsword +12 1d8+3 (19-20x2) or Longbow +8 1d8 (20x3)}
  \srditem{Full Attack}{+1 Longsword +12/+7 1d8+3 (19-20x2) or Longbow +8/+3
    1d8 (20x3)}
  \srditem{Space/Reach}{5 ft./5 ft.}
  \srditem{Special Qualities}{-}
  \srditem{Saves}{Fort +7, Reflex +4, Will +2}
  \srditem{Abilities}{Str 18, Dex 14 Con 15, Int 12, Wis 10, Cha 8}
  \srditem{Skills}{Spot +9, Listen +9}
  \srditem{Feats}{Power Attack, Improved Initiative, Weapon Focus (Longsword),
    Weapon Specialisation (Longsword), Point Blank Shot, Precise Shot, Rapid
    Shot
  }
  \srditem{Equipment}{+1 Longsword, +1 Longbow, Arrows (20), +1 Chainmail, +1
    Heavy Wooden Shield, Gloves of Strength +2, Cloak of Protection +2}
  \srditem{Environment}{Any}
  \srditem{Organisation}{Solitary, pair, or squad (4-8) with a captain}
  \srditem{Challenge Rating}{3}
  \srditem{Treasure}{Double gold, normal goods, normal items}
  \srditem{Alignment}{Any}
  \srditem{Advancement}{By character class}

  The captain's ability scores before racial modifiers and level ups were: Str
  15, Dex 14 Con 13, Int 12, Wis 10, Cha 8
\end{35e}

\subsection{Red Legion Scout}
\label{sec:Red Legion Scout}

Red Legion Scouts are skilled trackers, hunters, as well as scouts. They prefer
to travel light, and often use their bows to stage ambushes. Most are scouts,
but some are rangers or rogues. Usually a squad will have one scout with them.

\begin{35e}{\Large{Red Legion Scout, 5th Level Scout}}
  \srditem{Size/Type}{Medium Humanoid (Dark Elf)}
  \srditem{Hit Dice}{5d10+6 (40 HP)}
  \srditem{Initiative}{+10}
  \srditem{Speed}{30 ft.}
  \srditem{Armour Class}{19 (+4 Armour, +4 Dex, +1 Prot.), 15 touch, 15 flat
    footed}
  \srditem{BAB / Grapple}{+3 / +5}
  \srditem{Attack}{+1 Kukri +7 1d4+2 (18-20x2) or +1 Composite Longbow +9
    1d8+2 (20x3)}
  \srditem{Attack}{+1 Kukri +7/+7 1d4+2 (18-20x2) or +1 Composite Longbow +9
    1d8+2 (20x3)}
  \srditem{Space/Reach}{5 ft./5 ft.}
  \srditem{Special Qualities}{Skirmish (+2d6, +1AC), Trapfinding, Battle
    Fortitude +1, Uncanny Dodge, Fast movement +10 ft., Trackless Step, Bonus
    Feat}
  \srditem{Saves}{Fort +3, Reflex +9, Will +2}
  \srditem{Abilities}{Str 14, Dex 20 Con 13, Int 10, Wis 12, Cha 8}
  \srditem{Skills}{Spot +9, Listen +9}
  \srditem{Feats}{Weapon Finesse, Point Black Shot, Improved Initiative}
  \srditem{Equipment}{+1 Kukri (2), +1 Composite Longbow (+2), Arrows (40), +1
    Chainshirt, +1, Gloves of Dexterity +2, Cloak of Protection +1
  }
  \srditem{Environment}{Any}
  \srditem{Organisation}{Solitary, pair, or squad (4-8) with a captain}
  \srditem{Challenge Rating}{6}
  \srditem{Treasure}{Normal gold, normal goods, normal items}
  \srditem{Alignment}{Any}
  \srditem{Advancement}{By character class}

  The scout's ability scores before racial modifiers and level ups were: Str
  14, Dex 15 Con 13, Int 10, Wis 12, Cha 8
\end{35e}
