\subsection{Citizenship}
\label{sec:Citizenship}

The large and vast city kingdoms of the humanoid races take great emphasis
on written documents and record keeping. They also keep a citizen register
within which it all official residents and citizens of the city kingdom are
registered by name, gender, race and age.

Citizens of city kingdoms enjoy additional freedoms within their home nation,
such as the ability to purchase property, found businesses, or own and sell
slaves. Being a citizen of a city nation also offers protection when visiting
other large nations, as many of these cities have mutual protection and
recognition agreements amongst each other that guarantee special wards, such
as protection from enslavement or right to counsel and representation from your
own nation should they be accused of committing crimes.

City nations and kingdoms often issue three types of official identification
papers: \emph{citizen papers}, \emph{citizen marks} and
\emph{marks of nobility}.

\subsubsection{Citizen Papers}
\label{sec:Citizen Papers}

The cheapest of all identification methods are the citizen papers. Often a
single scroll, elaborately designed and embellished that holds the citizen's
name, race, gender and age; along with a seal of the kingdom or nation to
which they are a citizen off. These papers are important travel documents for
most citizens, and usually cost between five or ten \hyperref[sec:Shin]{shins}
to be issued. Families often just have one citizen paper for the entire family.

\subsubsection{Citizen Marks}
\label{sec:Citizen Marks}

A more expensive way to mark citizens is the arcane \emph{citizen mark}. It is
based upon \hyperref[sec:Deepkin]{deepkin} blood magic, and infuses itself
with the citizens body. At will, the citizen may then produce or hide an
arcane tattoo anywhere on their own body, which contains all the necessary
information to identify him as a citizen of a city kingdom or nation. These
usually cost up to 200 shins to inscribe, but cannot be stolen, misplaced or
so easily forged.

\subsubsection{Nobility Marks}
\label{sec:Nobility Marks}

Nobility marks work just the same as citizen marks, except that they are
customised toward the house of nobility that issues them. Instead of
identifying that person as a citizen of a kingdom, these marks identify the
person to be of noble blood line. These marks are scribed usually at birth of
a new member of a noble family, and act as a proof of nobility across the
known world of Aror.
