\section{City Kingdoms}
\label{sec:City Kingdoms}

The world of \emph{Aror} is covered in a few huge and ancient human kingdoms
that exert their influence and power from vast cities. These cities often
house millions of humanoid creatures, and the kingdom's influence and power
extended outward to surrounding areas. Most of these cities are sprawling
metropolises that house an overwhelming amount of humanoids. The populations
listed here include any surrounding area, smaller baronies permanently under
the kingdom's control, and even outlying cities that fall under the
jurisdiction of the kingdom.

The massive populations of some of these city kingdoms can often only be
sustained through slave labour, and by optimising agriculture through arcane
machinery. Many baronies and aristocratic houses are wealthy and owners of
huge patches of land, who make their fortunes by selling their produce and meat
to the city kingdoms. Small, self sustaining farms are rare close to large
city kingdoms, as they have all been bought up by these huge land barons.
\nameref{sec:House Liares} of Helmarnock is a prime example of a wealthy
aristocratic family that gained their wealth solely by providing the city
kingdom with produce, meat and other agricultural products.

All of these city kingdoms are connected together with \hyperref{sec:Dragon
  Teleporter}{dragon teleporters}, which allows travel and trade between the
kingdoms. They are often a beacon of stability and security. Surrounded by
wild nature, unstable baronies, and small and greedy earldoms that vie for
power and wealth.

Many of these city kingdoms have their own unique culture, local language
dialects, their own laws and customs, and often also unique governments. However
most of these kingdoms are ruled by humans, where other races often take a
secondary role as minorities within the general populace. Still the mixture
of races, backgrounds and various cultures often add a unique touch to the
whole.

In many cases the town or city kingdom you came from defines you more than
your race. A \hyperref[sec:Snow Elves]{snow elf} born in
\nameref{sec:Avenfjord} will have grown up with that cities culture, most
likely favouring the arts over the hunting bow. Much like a halfling of
\nameref{sec:Norbury} will be a staunch believer of the meritocratic culture
prevalent in the warrior kingdom.

All of these city kingdoms, as well as many bigger baronies, have a system
where they register citizens and also issue official documents to their
citizens. These are often copper rings for common citizens, or even official
documents of identification in case of officials or noble houses. Being a
citizen of one city kingdom not only grants considerable benefits in your
home, but often also grants you special status or privileges in allied city
kingdoms.

The large and vast city kingdoms of the humanoid races take great emphasis
on written documents and record keeping. They also keep a citizen register
within which it all official residents and citizens of the city kingdom are
registered by name, gender, race and age.

Citizens of city kingdoms enjoy additional freedoms within their home nation,
such as the ability to purchase property, found businesses, or own and sell
slaves. Being a citizen of a city nation also offers protection when visiting
other large nations, as many of these cities have mutual protection and
recognition agreements amongst each other that guarantee special wards, such
as protection from enslavement or right to counsel and representation from your
own nation should they be accused of committing crimes.

City nations and kingdoms often issue three types of official identification
papers: \emph{citizen papers}, \hyperref[sec:Citizen Mark]{citizen marks} and
\hyperref[sec:Nobility Mark]{marks of nobility}.

In between most of these city kingdoms stretches out a vast network of smaller
baronies and earldoms. Most of these are too insignificant to mention, and the
unstable nature of small rulings makes tracking them through time a far too
tedious task to be worthwhile for a book of this scope.

\aren{We can perhaps list them all in a separate book. With three thousand
  pages...}

\begin{note}
  The region between city kingdoms is left blank intentionally so that dungeon
  masters and players have leeway to design their own baronies and villages.
\end{note}

%% City Kingdom of Avenfjord
\input{chapters/citykingdoms/avenfjord}
%% City Kingdom of El-Fayam
\input{chapters/citykingdoms/elfayam}
%% City Kingdom of Esmajar
\input{chapters/citykingdoms/esmayar}
%% City Kingdom of Fes al-Bahsir
\input{chapters/citykingdoms/fesalbashir}
%% City Kingdom of Forsby
\input{chapters/citykingdoms/forsby}
%% City Kingdom of Helmarnock
\input{chapters/citykingdoms/helmarnock}
%% City Kingdom of Hraglund
\input{chapters/citykingdoms/hraglund}
%% City Kingdom of Kesmar
\input{chapters/citykingdoms/kesmar}
%% City Kingdom of Morkan
\input{chapters/citykingdoms/morkan}
%% City Kingdom of Nen-Hilith
\input{chapters/citykingdoms/nenhilith}
%% City Kingdom of Norbury
\input{chapters/citykingdoms/norbury}
%% City Kingdom of Stenheim
\input{chapters/citykingdoms/stenheim}
%% City Kingdom of Tredegår
\input{chapters/citykingdoms/tredegar}
