\chapter{Religions and Deities}

\section{Religion on Aror}
\label{sec:Religion}

The deities of Everblack have been divided into two major groups by most of
the divine scholars: Actual deities, and powerful extra-planar or
extra-dimensional creatures that either pose as such, or have enough power to
enforce their will as if they were deities.

\textbf{True deities} are manifestations of abstract ideas and higher
metaphysical concepts, that grant those that follow their ideals with
power. These deities \emph{never} speak to their followers directly, cannot be
``visited'' on some obscure plane, will never visit the world in turn as an
``avatar'', and can also not be reasoned with. And you may either chose to
align yourself with their ideals, question their ideals and power, or you
choose to ignore them completely.

However it is a strange fact of live that those that do align their lives,
ideals, and value systems according to specific dogma that manifests these
abstract ideas and concepts in the world are granted seemingly divine favour
and power. Some become paladins, holy knights with an arcane power to heal,
while others are granted a vast array of powerful arcane spells at their
disposal. Deviate from the true deity's path, and you risk losing that
power. Followers of these gods have collected thousands of years of history,
rituals, teachings and dogmas and often brought them under one roof as a
religious order or church devoted to said true deity. While following the
proven and existing dogma will lead to reward from the true deity, it is never
the \emph{only way} to elicit favour from said deity. Often new
interpretations of the ideals and value systems are discovered to be as
favoured by the true deity as the tried and true older dogma. This often leads
to schisms within religious orders and institutions, as well as new orders
being founded based off the new set of dogma. \emph{Nyddwr}, a goddess of
olden times, is an example of an abstract ideal manifest as a religion.

On the other hand \emph{Aror} is under the influence of \textbf{lesser
  deities}, a few powerful extra dimensional or extra planar entities, that
pose as gods. Most of these are malevolent and often twist their followers
into doing evil. While the true deities seem eternal, these entities are prone
to disappearing, or having their power usurped by other entities. Although
followers of the true gods often look down on the follower of these entities,
the divine power granted by these entities cannot be denied. It often rivals,
or even surpasses the powers granted by true deities. \emph{Aria} is a prime
example of a powerful extra dimensional entity that is worshipped as a god
among many people on Aror.


\section{True Deities}
\label{sec:True Deities}

%% Forun
\input{chapters/deities/forun}
%% Nyddwr
\input{chapters/deities/nyddwr}
%% Marwaid
\input{chapters/deities/marwaid}
%% Old Ways
\input{chapters/deities/oldways}
%% Order
\input{chapters/deities/order}

\section{Lesser Deities}
\label{sec:Lesser Deities}

%% Aria
\input{chapters/deities/aria}
%% Forneus
\input{chapters/deities/forneus}
%% Griannar
\input{chapters/deities/griannar}
%% Isamir
\input{chapters/deities/isamir}
%% Lilith
\input{chapters/deities/lilith}
%% Lor
\input{chapters/deities/lor}
%% Morana
\input{chapters/deities/morana}
%% Runemaster
\input{chapters/deities/runemaster}
%% Silent Queen
\input{chapters/deities/silentqueen}
%% Three Kings
\input{chapters/deities/threekings}
%% Xir
\input{chapters/deities/xir}
