\chapter{Magic in Everblack}
\label{sec:Magic}

Magic is ever present in the world of Everblack. It is used by scholars and
wizards, to improve the lives of everyone, or by dark and ruthless mages to
bring harm and war upon the world. This chapter discusses the foundations of
magic within the world of Everblack, and brings new rules for magical effects
such as \emph{rituals} and \emph{soul magic}.

\section{Three Sources of Magic}

There are three main sources of magic in the world of Everblack. Both divine
and arcane magic, which stem from the same source. The distinction is that
divine magic is granted already prepared in the form of spells to divine
casters, while arcane researchers and scholars build their own spells out of
that same raw magical energy that also fuels divine spells.

The second power are psionical powers, which manifest in the powerful minds of
psykers, and psionic creatures such as \nameref{sec:Ilians}. They do not draw
their power from the same pool as divine or arcane power, and come directly
from the mind of the powerful being that casts that spell. Compared to the
other two, psionic powers are the rarest on Aror.

The third magical source of power is the soul of living beings, which allows
one to cast \nameref{sec:Soul Magic}. This power is either drawn from one's
own soul, or from souls of those around them. Much like psionic power, it
stems directly from the trained or inherent power of the individual, and does
not rely on external sources, such as a raw energy web that seeps in from
other planes. While arcane or divine necromancy is the art of manipulating
and corrupting bodies, soul magic is the art and craft of using ones inherent
power to shape and fuel souls.

\subsection{Divine Magic}
\label{sec:Divine Magic}

Divine Magic comes directly from a deity, a deity representing a concept, or a
powerful individual, such as \nameref{sec:Daemons} or \nameref{sec:Devils}. In
the case of lesser deities, the deity in question grants that power, in the
understanding that the power is used to further the deities interests, and
goals. Once that power is granted, it cannot be revoked by the lesser deity
until it is used, or lost. True deities do not exist as living beings, being
concepts given power, and thus work differently. A priest that follows a true
deity draws strength and power from the concept said deity represents. For
example a priest of the \nameref{sec:Order} draws strength from an inner desire
to create order out of chaos, and from defeating the evil that may stem from
chaos. A priest of a true deity may lose their power should they stray too
far from their true deities concepts, ideas and ideology.

\subsubsection{Resurrection}

Resurrection magic works differently on Aror. Upon death all souls dilute into
the soul well, coming apart by the seams until they can no longer be recovered.
Much like you cannot recover the exact same water particles once you have
poured them into the ocean. The soul of a recently deceased can only survive
this dissolution of the self if another powerful soul of the well intervenes.
While some powerful souls may do so to further their own reasons, many will only
do so if they see a benefit for themselves. So those that wish to cheat death
will have to make a deal with a powerful daemon.

\begin{35e}{Resurrection}
  Any resurrection or reincarnation magic only works within 1d4 hours of
  death. After that resurrection magic only succeeds if a powerful daemon
  wishes for it to succeed.
\end{35e}

\subsection{Arcane Magic}
\label{sec:Arcane Magic}

Those deities that give power to their clerics, and priests cannot do so with
perfect efficiency. The process of granting, and using divine powers leaks
magical energy which remains trapped on Aror. This magical energy can be
harvested, shaped, and channelled into spells by those that study the craft of
\emph{arcane magic}. Due to its versatile nature, and its inherent
independence from a higher power, arcane magic is considered more powerful
that divine magic but also exceptionally difficult to study, hard to
understand, and dangerous to wield.

\begin{35e}{Arcane Magic}
  Arcane Magic of \emph{all} forms require years to learn, and wield even at
  the most basic levels. Any and all arcane wielders (even those that use
  ``inherent'' arcane magic like bards and sorcerers) are usually 10 to 20
  years older their divine or martial counterparts to make up for the years
  spent training, and learning. Unless of course they one of the rare
  \hyperref[sec:Graham Balance]{child prodigies}.
\end{35e}

\subsection{Necromancy}
\label{sec:Necromancy}

Necromancy is the art and craft of manipulating both body and soul to achieve
a purpose. In many cases the craft destroys the soul, leaving only a soulless
husk behind, while in others it does exactly the reverse. The art of
necromancy was discovered when \nameref{sec:Morana} turned some of her
followers to vampires, and has since been excessively studied by scholars,
priests and wizards. \nameref{sec:Isamir} also gave the power of necromancy to
the \nameref{sec:Inua} who closely guard the secrets of their rituals, spells
and incantations.

Liches, and \nameref{sec:Vampires} are the epitome of applied necromancy, and
many scholars have spent millennia studying them to better understand the
craft. While many necromancers wish only to study the vampire to better help
them survive, much like a doctor would for the living, others use the powers to
do evil, creating vicious and horrid creatures to do their bidding. Necromancy
is thus outlawed in many regions, and cities, requires oversight, or a special
permit.

% Rituals
\input{chapters/magic/rituals}

% Runemagic
\input{chapters/magic/runemagic}

% Soul Magic
\input{chapters/magic/soulmagic}
