\chapter{Planes \& Planets}
\label{sec:Planes}

Around 800.000 years ago, when the dragons first settled Aror, they
deliberately cut off the planet from all other planes of existence. Thus no
plane could ever contaminate the ``material plane'' (i.e. Aror) ever
again. The dragons never gave a reason on why they did so, but most scholars
agree, it was an attempt to monopolise planar travel, and thus lock out their
enemy the \nameref{sec:Giants}.

Roughly 200.000 years later the giants managed to breach the blockade, and
invaded Aror. After they were defeated by the dragons, the blockade was
reinforced and held until \emph{MI:1918}, or over 600.000 years. The breach
was sealed again, with the help of the wizards of the \nameref{sec:Magistrata
Arcanum}, and the \nameref{sec:Hall of Knowledge}.

No plane of existence can be reached directly from Aror, and Aror cannot be
directly reached from any other plane of existence. However planets near Aror
within the galaxy can be reached through teleportation spells. Some of these
planets support life, and from them you could reach other planes of existence.
Due to the difficulty of reaching other planes from Aror, inter-planar travel
is rather rare. What is quite common however, are visits to the planets that
are close to Aror, such as \nameref{sec:Aurelis}.

Since there is no astral plane reachable from Aror, the souls of the dead
instead go into the \nameref{sec:Soul Well}. There are also no astral beings
that are worshipped as gods on Aror, since the followers would not be able to
communicate with it. Most scholars, wizards and leaders of Aror agree that
this isolation from the planes is a good thing, as there already are a
plethora of threats native to Aror. However this also means that many
extra-planar threats (such as the Githyanki) are unknown to people of Aror.
The mechanics that lead to planar isolation have even been copied by other
races, such as the \nameref{sec:Devils}, or the \nameref{sec:Aurelis} to
shield their realm from other planes.

The most confusing part about planar and planetary science on Aror is the
terminology. Since very, very few have actually travelled to another plane,
the distinction between the two concepts is not well known. The words
``planes'' and ``planet'' are used interchangeability, causing confusion to
those that know the difference.

\aren{This mistake was sadly also made repeatedly by our esteemed Graham, and
for the sake of preserving the original work, these errors are retained.}

\section{Planets}

% Abyss
\input{chapters/planets/abyss}
% Celestis
\input{chapters/planets/celestis}
% Layers of Hell
\input{chapters/planets/hell}
