\section{Backgrounds}
\label{sec:Backgrounds}

Backgrounds are an additional perk you can take at first level that defines
what you have been up to since you started adventuring. These backgrounds work
similar in spirit to the same mechanic of the newest version of \emph{D\&D}, but
come with the added benefit of firmly placing a character into the world of
Aror.

All backgrounds may come with benefits, but some benefits may be lost should
you fail to comply with certain requirements, or fall from grace with the
organisation related to the background. This is possible as these abilities
are either directly deity-given powers, or because the organisation itself
provides you with the necessary knowledge, tools, and training to sharpen and
hone the skills granted by the background. This is reflected in the rules as
losing the ``class skill'' status of a given skill.

\subsection{Helemic Acolyte}
\label{sec:Helemic Acolyte}

You trained as an acolyte of the \nameref{sec:Helemic Order}, which helped
you to unlock your psionic potential. You are thus capable of manifesting
psionic powers.

\begin{35e}{Helemic Acolyte}
  You gain +4 psionic power points at level 1, and you gain the ability to
  manifest one additional psionic power at level 1.
\end{35e}

\subsection{Mist Reaver Acolyte}
\label{sec:Mist Reaver Acolyte}

You trained as an acolyte and knave beneath a Mist Reaver, but did not
complete your training and initiation ritual. Perhaps you did not wish to
become a vampire, or you turned away from a life of hunting and slaying
monstrous creatures. The training to become a Mist Reaver acolyte is demands a
lot of travel, and this background is thus incompatible with any background
that requires you to stay in one place for a long period of time (such as
``Subject of the Crown'', or ``Slave'').

\begin{35e}{Mist Reaver Acolyte}
  You gain proficiency with all light and one handed martial weapons, light and
  medium armours, as well as all shields (except tower shields), and you gain
  the feat \emph{Favoured Enemy (Monstrous Races, Humanoids)} which includes
  monstrous races with a humanoid appearance: orcs, goblins, hobgoblins, gnolls,
  and bugbears.
\end{35e}

\subsection{Pious Acolyte}
\label{sec:background:Pious Acolyte}

Your entire childhood was filled with religious service towards your deity and
church. While not fully a priest, you your religious zeal, and service to your
deity, dogma and church have rewarded you with great power. This background
does not exist for deities that do grant divine power (such as
\nameref{sec:Ishtar}). Pious Acolytes are also often shamanic acolytes, or
witches in learning of the \nameref{sec:Old Ways}, or other tribal villages.

\begin{35e}{Pious Acolyte}
  For any deity that grants divine power, you gain domain spells, and domain
  spell slots like any cleric for \emph{one} domain you select at character
  creation. This effect does not stack with domain slots and spells granted by
  the cleric class, or other classes that also gain domain slots and
  spells. Your caster level is your equal to your HD. If you fall from faith,
  lose connection with your deities ideals, are cast from the church, or do
  anything that displeases your deity and/or church, you lose the benefits of
  this background.
\end{35e}

\subsection{Scion of Silence}
\label{sec:Scion of Silence}

You were trained as a psionic assassin under the brutal and horrific regime
of the elder Scions. You survived the ritual, unlocked your psionic potential,
and were then set loose upon the world to the organisation's lethal bidding.

\begin{35e}{Scion of Silence}
  You must be \emph{evil}. You gain +2 psionic power points at first
  level. You also gain and a +4 bonus to \emph{Hide}, and \emph{Move
    Silently}, which become class skills. Your initiation ritual counts as the
  ``special'' requirement for the \emph{Assassin} prestige class.
\end{35e}

\subsection{Slave}
\label{sec:background:Slave}

You were enslaved since you were born, and are still the property of another
person, organisation or state. But somehow you managed to flee from your life
of servitude. But just because you fled, doesn't mean you are save. One or
more organisations might be hunting you, or are perhaps tracking you through a
slave bracelet, or an arcane slave mark. Since a born slave cannot be a
citizen, this background is incompatible with the ``Subject of the Crown''
background.

\begin{35e}{Slave}
  You gain +2 bonus to \emph{constitution} for all those days spent doing
  heavy labour, and a +4 bonus to \emph{bluff}, and \emph{survival} to be able
  to survive the harsh realities of slavery.
\end{35e}

\subsection{Slave Hunter}
\label{sec:Slave Hunter}

You are a slave hunter, either an independent contractor, or perhaps for the
\nameref{sec:Velvet Hand} or \nameref{sec:Hunters Guild}. Independent
contractors cannot be slaves themselves, but you may also have the ``Slave''
background in combination with being a slave hunter for the Hunter's Guild or
Velvet Hand.

\begin{35e}{Slave Hunter}
  You gain a +4 bonus to \emph{Intimidate}, \emph{Sense Motive},
  \emph{sec:Spot}, and those three skills become class skills. You also gain
  the benefits of the \emph{Track} feat.
\end{35e}

\subsection{Snow Elf of the Pale}
\label{sec:background:Snow Elf}

You grew up amongst the snow elves of the northern or southern pale, but were
exiled from your tribe. You learned the ancient secrets of the tribes of the
north and south, and are thus an excellent hunter, and tracker. This
background is incompatible with the ``Subject of the Crown'' background.

\begin{35e}{Snow Elf of the Pale}
  You gain a +2 bonus \emph{wisdom}, and you are proficient with normal, and
  composite long bows. You further gain +2 attack and damage with normal, and
  composite long bows. Deep snow, and ice are not considered difficult terrain
  for you.
\end{35e}

\subsection{Subject of the Crown}
\label{sec:background:Subject of the Crown}

You have grown up as a fully fledged citizen of one of the major city kingdoms
of Aror, taking on the city nations customs, traditions, overall values, as
well as being fluent in all locally used languages. You thus hold the city
kingdom's citizenship, which may or may not grant you additional benefits when
visiting your home nation. This background also means that you have fulfilled
any obligations that are required for you to be a registered citizen, such as
fulfilling your civil service as a citizen of \nameref{sec:Norbury}. See the
table below on benefits you get for your citizen ship. The ``Subject of the
Crown'' background is special, as in can potentially be taken alongside another
background.

\begin{table*}[!htb]
  \captionsetup{labelformat=empty,font={large,bf},position=top}
  \caption{Subject of the Crown (3.5)}
  \rowcolors{1}{white}{light-grey}
  \begin{tabular}{l p{5cm} p{7cm}}
    \textbf{City Kingdom}                    & \textbf{Automatic Languages} & \textbf{Benefit} \\
    \nameref{sec:Avenfjord}                  & Enro'ad, Taavid, Teranim     & +4 bonus to \emph{Perform}, and \emph{Diplomacy}, these skills become class skills \\
    \nameref{sec:El-Fayam}                   & Kalest, Teranim, Latas       & +4 bonus to \emph{Appraise}, and \emph{Bluff}, these skills become class skills \\
    \nameref{sec:Esmayar} (Pre-Invasion)     & Kalest, Teranim, Latas       & +4 bonus to \emph{Gather Information}, and \emph{Bluff}, these skills become class skills \\
    \nameref{sec:Esmayar} (Post-Invasion)    & Gnoll, Giant                 & +4 bonus to \emph{Intimidate}, and \emph{Bluff}, these skills become class skills. Your citizenship is not recognised by other city kingdoms \\
    \nameref{sec:Fes al-Bashir}              & Kalest, Teranim              & +4 bonus to any one \emph{Knowledge} skill, which becomes a class skill \\
    \nameref{sec:Forsby}                     & Teranim, Reatham, Doresh     & +4 bonus to \emph{Forgery}, and \emph{Bluff}, which becomes a class skills \\
    \nameref{sec:Helmarnock}                 & Teranim, Old Teranim         & +4 bonus to \emph{Sleight of Hand}, and \emph{Knowledge (History)} which become class skills \\
    \nameref{sec:Hraglund}                   & Teranim, Old Teranim, Enro'ad& +4 bonus to \emph{Survival}, and \emph{Knowledge (Religion)} which become class skills \\
    \nameref{sec:Kesmar}                     & Rutari, Teranim              & +4 bonus to \emph{Appraise}, and \emph{Sense Motive} which become class skills \\
    \nameref{sec:Morkan}                     & Teranim, Danvark, Old Teranim& +4 bonus to \emph{Intimidate}, and proficient with all light and one-handed martial weapons, as well as light armour, and shields (except tower shields) \\
    \nameref{sec:Nen-Hilith} (Pre-Invasion)  & Enro'ad, Taavid, Teranim     & +4 bonus to \emph{Perform}, and \emph{Diplomacy}, these skills become class skills \\
    \nameref{sec:Nen-Hilith} (Post-Invasion) & Giant                        & +4 bonus to \emph{Hide}, and \emph{Survival}, these skills become class skills \\
    \nameref{sec:Norbury}                    & Teranim, Danvark, Old Teranim&+4 bonus to \emph{Craft}, which becomes a class skill, proficient with all light and one-handed martial weapons, as well as light armour, and shields (except tower shield) \\
    \nameref{sec:Stenheim}                   & Doresh, Teranim, Old Teranim &+4 bonus to \emph{Spellcraft}, and \emph{Knowledge (Architecture and Engineering)}, which become class skills \\
    \nameref{sec:Tredegar}                   & Teranim, Old High Teranim    &+4 bonus to \emph{Appraise}, and \emph{Diplomacy} which become class skills \\
  \end{tabular}
\end{table*}

\subsection{Walburga Witch}
\label{sec:background:Walburga Witch}

You grew up among the female only witches coven of Walburga, and your soul was
successfully awoken during their initiation ritual. Even though you no longer
reside among your fellow witches, you may still follow Morana's teachings and
dogma. Should you fall from Morana's grace, you will also be exiled from the
witches coven. Only women may be part of the coven.

You gain a +2 bonus to \emph{charisma}. During your initiation ritual you were
soul awoken, and may immediately learn one level 1 soul power.

Should you still follow Morana, you are also able to cast \emph{Hide From
  Undead}, and \emph{Inflict Light Wounds} three times per day as a spell-like
ability.

\subsection{Well of Truth Agent}
\label{sec:Well of Truth Agent}

You trained as a spy, thief, diplomat, trader, and guardsman of the
\nameref{sec:Well of Truth}. You were responsible for stealing many magical
artefacts, pieces of knowledge, and successfully guarded other followers of
Aria during pilgrimages or missions. You lose any benefits of this background
if either Aria, or her follower deem you to have fallen from grace.

You gain a +4 bonus to \emph{hide}, \emph{move silently}, and \emph{forgery}
and those skills become class skills. You may cast \emph{See Invisibility}
once per day, as a spell-like ability.
