\section{Feats}
\label{sec:Feats}

\begin{table*}[!htb]
  \captionsetup{labelformat=empty,font={large,bf},position=top}
  \caption{Overview of Feats}
  \rowcolors{1}{white}{light-grey}
  \begin{tabular}{l l p{7cm}}
    \textbf{General Feats}    & \textbf{Prerequisites}           & \textbf{Benefit} \\
    Craft Implant             & Caster level 3rd                 & Craft implants \\
    Improved Weapon Finesse   & Weapon Finesse                   & Gain dexterity on damage with finesse weapons \\
    Radiant Soul              & Soul Awakened, 13+ Charisma      & Your power point die step increases by one \\
    \textbf{Background Feats} & \textbf{Prerequisites}           & \textbf{Benefit} \\
    Adept of Aria             & Believer of \nameref{sec:Aria}   & +4 bonus on hide, move silently, and they become class skills. Disguise Self three times per day \\
    Follower of Forun         & Believer of \nameref{sec:Forun}  & +2 charisma, +4 bonus to heal checks and knowledge (old ways) checks, and they become class skills \\
    Follower of Marwaid       & Believer of \nameref{sec:Marwaid}& +2 intelligence, +4 bonus to knowledge (old ways) checks, \emph{Shield Other} twice per day \\
    Follower of Nyddwr        & Believer of \nameref{sec:Nyddwr} & +2 wisdom, +4 bonus to sense motive and knowledge (old ways) checks. \\
    Hunter of the Guild       & Member of the \nameref{sec:Hunters Guild} & +4 bonus to intimidate, search, spot and survival and they become class skills, gain \emph{Track} \\
    Psyker                    & Member of the \nameref{sec:Helemic Order} & 4 bonus bonus power points at level 1, and two level 1 psion powers. \\
    Seer of Nyddwr            & Seer of \nameref{sec:Nyddwr}, female only & +4 wisdom, +4 bonus to sense motive, diplomacy and knowledge (old ways), telepathy 30 ft. \\
    Slave of Norbury          & Enslaved in \nameref{sec:Norbury}& +2 strength and constitution, registered slave of Norbury \\
    Soldier of Norbury        & Grew up in \nameref{sec:Norbury} & +2 strength, citizenship in Norbury, proficient with light, medium armour and all martial weapons \\
    Snow Elf of the Pale      & Tribal snow elf of the pale      & +2 bonus to wisdom; proficiency, +2 attack and damage with longbows and composite longbows, snow and ice is not difficult terrain for you \\
    Well of Truth Agent       & Believer of \nameref{sec:Aria}   & +4 bonus to open lock and forgery, and they become class skills. See Invisibility once per day \\
  \end{tabular}
\end{table*}

\subsection{General Feats}
\label{sec:General Feats}

\begin{35efeat}{Improved Weapon Finesse}
  \srditem{Description}{You can add your dexterity modifier instead of your
    strength modifier to damage for weapons that can be used with Weapon
    Finesse}
  \srditem{Requirements}{Weapon Finesse, Bab 6, Dexterity 17}
\end{35efeat}

\begin{35efeat}{Craft Implant}
  \srditem{Description}{You can craft small magical implants that can be
    inserted into a creature's body. These implants then grant special or
    extraordinary abilities, or even spell like abilities. Crafting an implant
    takes one day for each 1000 g the implant costs, and you must spend $
    \frac{1}{25} $ of the implants gold cost in XP, and use up raw materials
    half of this GP cost.

    You can also mend a broken implant, which costs half the gold, XP, time
    and materials of what it would cost to create the item anew from scratch.

    An implant is created for a special creature type in mind and will only
    work for said creature. But for half the cost in gold, XP, time and
    materials of what it would cost new, you can adapt an existing implant
    for another creature type.

    Some implants incur extra costs in material components or XP, as noted in
    their descriptions. These costs are in addition to those derived from the
    item's base price. You must pay such a cost to create an item or to mend a
    broken one.
  }
  \srditem{Prerequisite}{Caster level 3rd}
\end{35efeat}

\begin{35efeat}{Radiant Soul}
  \srditem{Description}{Your soul power point die step is increased by one,
    for any future class levels, as long as they give you soul power points.
  }
  \srditem{Requirements}{Soul Awakening, 13+ Charisma}
\end{35efeat}

\subsection{Background Feats}
\label{sec:Background Feats}

Everblack introduces one new feat type: \emph{background feats}. Each character
may take one background feat at level 1, which does not count toward the total
amount of feats the character may take. These feats represent your character's
background, early history or perhaps an education that your character has
completed before becoming an adventurer. These feats should help you place your
character into the world, as well as giving him connections towards religions,
organisations and events within the world.

Only one of these feats may be taken at level 1, unless otherwise specified.
For example certain elves (due to their long childhoods), may take two
background feats. Some of these feats have repercussions in how the world
views your character, so read these feat entries carefully. If in doubt,
discuss these feats with your DM first.

\begin{35efeat}{Adept of Aria}
  \srditem{Description}{You trained as an adept of Aria in your early
    childhood, with a goal of becoming a priestess or priest of Aria.}
  \srditem{Requirements}{Follower and believer of Aria, that has undergone
    training in a secret temple of Aria for several years. You lose the
    benefits of this feat if you abandon Aria, or she abandons you.}
  \srditem{Benefits}{You gain a +4 bonus to hide and move
    silently and these two skills also become class skills. You can also
    cast \emph{Disguise Self} three times per day as a spell-like ability.
  }
  \srdbackgroundfeat
\end{35efeat}

\begin{35efeat}{Follower of Forun}
  \srditem{Description}{You have trained for years as an aspirant in the
    church of Forun with the intention of becoming a priest. As part of
    your training you were taught how to heal and care for the wounded,
    look after the sick and also lead a small community as a spiritual
    centre and authority figure.}
  \srditem{Requirements}{Follower and believer in Forun that has undergone
    training as a potential priest. You lose the benefits of this feat if you
    abandon Forun.}
  \srditem{Benefits}{You gain a +2 bonus to charisma.  You also gain a +4
    bonus to heal and knowledge (religion), and both skills become class
    skills for you.
  }
  \srdbackgroundfeat
\end{35efeat}

\begin{35efeat}{Follower of Marwaid}
  \srditem{Description}{You have trained for years as an shaman or cleric
    dedicated to the goddess of sacrifice \nameref{sec:Marwaid}. As part of
    your training your were taught that there is no greater virtue than
    sacrifice, to those around you, as well as those that would sacrifice
    for others.}
  \srditem{Requirements}{Follower and believer that has undergone years of
    training as a shaman or cleric of Marwaid. You lose the benefits of this
    feat if you abandon Marwaid.
  }
  \srditem{Benefits}{You gain a +2 bonus to intelligence. You also gain a +4
    bonus to heal and knowledge (old ways), and both become class skills for
    you. You may also cast \emph{Shield Others} twice per day, as a spell like
    ability.
  }
  \srdbackgroundfeat
\end{35efeat}

\begin{35efeat}{Hunter of the Guild}
  \srditem{Description}{You are a hunter, employee and slaver of the
    \nameref{sec:Hunters Guild}. For years you have trained to track down
    runaway slaves of Norbury.
  }
  \srditem{Requirements}{Member of the Hunter's Guild, as well as any non-good
    alignment.
  }
  \srditem{Benefits}{You gain +4 bonus to intimidate, search, spot and survival,
    and these skills become class skills. You also gain the benefits of the
    \emph{Track} feat.
  }
  \srditem{Drawbacks}{As a slaver you might be unwelcome or even barred from
    entering cities, nations and baronies that ban slavery. You are required to
    take orders from the \nameref{sec:Hunters Guild}.
  }
  \srdbackgroundfeat
\end{35efeat}

\begin{35efeat}{Psyker}
  \srditem{Description}{You were found by the \nameref{sec:Helemic Order}
    and trained to unleash your inherent but latent psionic gifts. As a psyker
    you know capable of manifesting psionic powers.
  }
  \srditem{Requirements}{You spent most almost all of your early adult life as
    a monastic member and psyker with the \nameref{sec:Helemic Order}, which
    taught you to use your latent abilities.
  }
  \srditem{Benefits}{You gain a +4 bonus power points at level 1, and you gain
    the ability to manifest two level 1 \emph{psion} powers.
  }
  \srditem{Drawbacks}{Like any psionic in Aror, you are subject to have your
    mind taken over by extremely powerful psionic entities, such as the
    \nameref{sec:Abyss}, or powerful \nameref{sec:Ilians}.
  }
  \srdbackgroundfeat
\end{35efeat}

\begin{35efeat}{Seer of Nyddwr}
  \srditem{Description}{You have trained for years to became one the three
    priestess of \nameref{sec:Nyddwr}. For one reason or the other, you are on
    longer part of a group of three, and now are free to travel and adventure
    again.
  }
  \srditem{Requirements}{Follower and believer that has undergone years of
    training required to become a seer of Nyddwr. You lose the benefits of this
    feat if you abandon Nyddwr, or stray from the traditions and rules required
    of a seer. You must be female.
  }
  \srditem{Benefits}{You gain a +4 bonus to wisdom. You also gain a +4 bonus
    to sense motive, diplomacy, and knowledge (old ways), and both become
    class skills for you. You may also cast \emph{Detect Thoughts} twice per
    day, as a spell like ability.  You also gain \emph{Telepathy (30 ft.)}
    among your fellow seers.
  }
  \srdbackgroundfeat
\end{35efeat}

\begin{35efeat}{Follower of Nyddwr}
  \srditem{Description}{You have trained for years to become a priest or
    priestesses of \emph{Nyddwr}. You have trained to read other peoples worries
    and woes, and have thus gained an unique insight into what troubles other
    people.}
  \srditem{Requirements}{Follower and believer that has undergone years of
    training as a shaman or cleric of Nyddwr. You lose the benefits of this
    feat if you abandon Nyddwr.
  }
  \srditem{Benefits}{You gain a +2 bonus to wisdom. You also gain a +4 bonus
    to sense motive and knowledge (old ways), and both become class skills for
    you. You may also cast \emph{Detect Thoughts} twice per day, as a spell
    like ability.
  }
  \srdbackgroundfeat
\end{35efeat}

\begin{35efeat}{Norbury Slave}
  \srditem{Description}{You spent much of your life in enslavement in
    Norbury, doing heavy labour or fought in the slave regiments of the
    city.}
  \srditem{Requirements}{grew up enslaved in Norbury for the majority of your
    life.}
  \srditem{Benefits}{You gain +2 bonus to strength and constitution.}
  \srditem{Drawbacks}{You are still enslaved within Norbury, and must fear
    being captured by the \nameref{sec:Hunters Guild} until you are officially
    set free. You also start without any gold or initial funds.}
  \srdbackgroundfeat
\end{35efeat}

\begin{35efeat}{Soldier of Norbury}
  \srditem{Description}{You grew up as a citizen of Norbury, and stayed there
    for most of your early live. You completed the mandatory basic training
    and civil service and now hold a basic citizenship of Norbury.}
  \srditem{Requirements}{grew up free in Norbury, spent the majority of
    your childhood there, and completed the mandatory civil service of
    Norbury.}
  \srditem{Benefits}{You gain a +2 bonus to strength, and are proficient with
    light armour and medium armour, as well as with all martial weapons. You
    hold Norbury citizenship in form of a citizen papers.}
  \srditem{Drawbacks}{You are in the active reserve of Norbury, and may be
    called to arms in times of crisis and emergencies.
  }
  \srdbackgroundfeat
\end{35efeat}

\begin{35efeat}{Snow Elf of the Pale}
  \srditem{Description}{As a \hyperref[sec:Snow Elves]{snow elf} you grew up in
    the tribal villages of great pale of either the southern or northern
    poles.
  }
  \srditem{Requirements}{Snow Elf of a tribal village in the great pale}
  \srditem{Benefits}{You gain +2 bonus to wisdom, and you are proficient with
    normal and composite long bows. You further gain +2 attack and damage with
    normal and composite long bows. Deep snow and ice is not difficult terrain
    for you.
  }
  \srditem{Drawbacks}{As an adventurer that has left tribes of the pales, you
    were exiled from your tribe for one reason or the other.
  }
  \srdbackgroundfeat
\end{35efeat}

\begin{35efeat}{Well of Truth Agent}
  \srditem{Description}{You trained as a spy, thief or guardsman of the
    Well of Truth. You stole magical artefacts, knowledge or guarded the
    secret libraries of the well of truth.}
  \srditem{Requirements}{Follower and believer of Aria, that has undergone
    training as an agent in a secret library of the Well of Truth. You lose
    the benefits of this feat if you abandon Aria, or she abandons you.}
  \srditem{Benefits}{You gain a +4 bonus to open lock and
    forgery and these two skills also become class skills. You can also cast
    \emph{See Invisibility} once per day as a spell-like ability.}
  \srdbackgroundfeat
\end{35efeat}
