\subsection{Psionic Magic}
\label{sec:Psionic Magic}

Psionic magic - or psi magic - is the third pillar in the magic community of
Aror, and in terms of practitioners the second most popular magic on
Aror. Psionic magic stems from a creature's mind, and allows them to manifest
their thoughts and will into the world. This takes years of practice and
training. Psionic magic is deeply aligned with the colour green. Psionically
charged \nameref{sec:Everblack} is green, and psions often emit green light
when using their powers.

Many creatures of Aror are inherently psionically talented. For example every
\hyperref[sec:Ilians]{Ilian} is a psion of varying degrees of power, depending
on their cast. Every \nameref{sec:Scourge} spawn is also a highly powerful
psionic entity, and so in turn are its children.

Psions amongst the monstrous and humanoid people of Aror are extremely rare,
yet the ability to manifest such powers runs in the family. Children of
powerful psions are expected to become psions themselves, although the power
has been known to skip a generation, or individual descendants. These powers
often manifest in early childhood, and then require years of training and
nurturing to develop to a stage where the powers can be wielded in a reliable
and safe manner. Many noble houses pride themselves on being descendants of
powerful psykers, often acknowledging this fact by using the colour green, or
the staff of an \nameref{sec:Emir} in their heraldry.

The science behind psionic powers is poorly understood, and thus there is no
infrastructure available to further its study. There are no official courses
on psi magic offered at the big universities, and there are but a few
organisations dedicated to understanding and furthering the development of
psionic magic. The art and craft is still taught through apprenticeship, and
it takes almost a decade to fully master the basics of psi magic. Children
with latent psionic ability are usually detected early, as they either
haphazardly manifest weaker powers such as telepathy, or telekinesis, or
are capable at an early age to accurately follow the 4/4 metre projected by
\nameref{sec:Baphomet}.

\graham{If your child dreams of a hellish clock following a 4/4 metre, you
  should seek aid from a fellow Psion.}

\subsubsection{Abyss}

The Abyss, a particularly big growth of the \nameref{sec:Scourge}, is the most
powerful psyker in the known multi verse. Through its sheer size, and a flock
of billions of \nameref{sec:Demons} at its side, its psionic presence is
without equal. Even though the \nameref{sec:Monolith} was installed to block
the Abyss from seeing Aror and its psykers, the use of high level psionic
powers still draws the Abyss' gaze towards Aror.

Its presence in psionic realm is one of petrifying, and unrelenting horror,
Many psykers that tried to communicate with the Abyss have gone mad, tempted
and corrupted by its influence. Through the help of powerful psykers the Abyss
has invaded other realms in the past, using them as agents or even hosts. The
Abyss is cunning, and devious foe, and many have become victims of its schemes
and plots without knowing it.

Studies have shown that more invasions of Aror where detected by watchful
psykers - and thus allowing for an orderly and early response - than have
been instigated by psykers.

\graham{So please do not burn your friendly neighbour psyker at the pyre,
  just because you thought you saw a demon lurking in the shadows.}

\subsubsection{Baphomet}

The second most powerful psyker, after the Abyss, is the leader of the
devils \nameref{sec:Baphomet}. His presence serves as a calming and orderly
counter balance to the presence of the Abyss. He projects a psionic beacon
into the noosphere which allows other psykers to drown out the Abyss' presence
by focusing and concentrating on its rhythmic metre. Baphomet has been known
to communicate with powerful psykers through telepathy, although such
occasions are rare.

Baphomet is the definite scholar on psionic theory and science, and she is
willing to debate, and share her knowledge with those that proof to be equals
in that field. Her curiosity for psionic theory is of genuine interest in
the field, and she has given out warnings of impending Abyss invasions, or
shared the secrets of psionic powers without an ulterior motive. Although
the study of the arcane is more prevalent in devil society, Baphomet has a
steady and devout following on both the Layers, as well as on Aror.

\subsubsection{Noosphere}
\label{sec:Noosphere}

The noosphere (or mind scape) is a psionic realm shared by all psionically
gifted creatures across the multi verse. It is through this medium that
telepathic messages are exchanged, and a psion's power can be measured by
how brightly their presence shines in this medium, and by how far they
can project their power within it. Even though it is a neutral place without
shape or form, the noosphere is shaped by the minds of those that inhabit
it. While Abyss' dreadful and horrific psionic gestalt is ever present in
the noosphere, there are far too many happenings within the mind scape for
it to notice any particular psyker. Yet many psykers avoid staying connected
to the noosphere longer than absolutely necessary.