\section{Scourge}
\label{sec:Scourge}

The scourge is an extra planar and psionic life form whose sole purpose is to
grow and expand. It takes the shape of a roughly five centimetre thick, rough
flesh that is warm to the touch. The scourge can grow indefinitely, and can
range from the size of a small patch a few square metres to covering entire
cave systems, areas, or even entire planes.

The scourge feasts on organic matter to survive and grow. It grows over any
organic material that lands upon it surface and begins to slowly digest and
devour it. The scourge can absorb and devour anything soft and organic such as
water, flesh, bone, skin, hair, plants, wood, soft fertile dirt, and even some
softer composite organic materials like cloth or leather. It cannot devour
stronger compounds such as rocks, crystals, glass, iron or steel. It requires
roughly an hour to absorb 10 kg of organic material.

\subsection{Intelligence}

The scourge is driven by finding new food, which in turn helps it to grow and
expand. Anything organic is considered food, irregardless on whether that food
is alive, intelligent, struggling, feeling pain or if it is already dead
matter. Most scholars agree that the scourge has no concept of mercy or pain
and simply devours.

Its most devious ability is to learn from any organic material it absorbs. The
scourge then puts these new abilities to use to find more nourishment for
itself. For example once it has absorbed plants it might grow leaves in the
sun, or once it has absorbed a predator it might spawn its own predator to
hunt and kill other life forms. The more material it absorbs, the better it
begins to understand the creatures it attempts to copy. So an important
secondary goal for the scourge is to find new genetic material to absorb.

The creatures intelligence of the scourge increases with each absorbed
biological sample, as it learns about new tools, their uses and how to best
put them to use for its own needs. Its intelligence is also directly
proportional to its size, as it must grow to be able to store the information
it absorbs. Small patches of scourge that are split from the main growth
are disconnected from the vast absorbed knowledge, and must either reconnect,
or learn everything a new.

\subsection{Appearance}

The scourge itself is a thin layer of red flesh and skin that slowly grows
over all surfaces it covers, perhaps a few centimetres thick. It grows over
stone floors, clings to cave walls and will cover ceilings and soft dirt.
Once it has absorbed knowledge about other living materials such as bone or
cartilage it will incorporate these elements into its own design. The scourge
has been known to use bone-like material to create bridges, uphold and support
walls, or make ladders and stairs so that its spawn can best natural barriers.
This gives the scourge a grotesque appearance of a living cave or a forest
of flesh and bone, where all trees are made of one creature.

The size of a scourge ranches from very small (perhaps a few square metres in
size), to moderate (covering small caves), big (big caves or a square kilometre
of forest), extreme (covering entire areas) to overwhelming covering entire
planes or planets.

Bigger scourge growths (such as the one in the abyss) are capable of producing
complex biological features. The abyss can spawn organs such as eyes or ears
within on its surface to better observe its surroundings. It might also spawn
maws of sharp teeth and jaws to grind down food for easier digestion.

\begin{35e}{Size}
  A scourge growth has 30 hit points per square metre (30 hp per square feet),
  and a DR of 5/-. The scourge is further resistant to fire, acid and
  electricity (DR 10).
\end{35e}

\subsection{Psionic Powers}

The psionic powers of a scourge grow in proportion with its size. At a smaller
size it may only communicate with other psionic creatures that are either very
close or are in direct contact with the scourge. But as it grows it may cast
its psionic will and powers across vast distances, and in case of the abyss,
even across the boundaries of planes. The scourge never speaks telepathically,
but instead attempts to control any creature it connects with telepathically
through the transmission of basic instincts and desires.

\begin{35e}{Psionics}
  Any psionic creature that attempts to make contact with the scourge must
  succeed a will save or be subject to the \emph{Dominate, Psionic} spell
  cast by the scourge that lasts 1d4+1 hours.
\end{35e}

\subsection{Abyss}
\label{sec:Abyss}

Its home plane is simply referred to as the \emph{abyss}. Confusingly the
particular scourge entity of the abyss is also simply referred to as ``the
abyss''. The abyss is a warm, volcanic planet that is very geologically
active. It has human breathable atmosphere, but the average temperatures range
from 40 to 60 degrees. The plane is devoid of any other live, save from the
scourge and its spawn. The scourge of the abyss has managed to cover most of
the planet, making the planet a hellish, contorted and grotesque landscape
ruled by the ever present single minded scourge.

The sky of the abyss is filled with dark clouds that block the sunlight from
shining through to the surface. Still, the planet itself is a hot and humid
atmosphere, and it seems that the scourges mainly nourishes itself from that
heat.

The abyss is further populated by uncountable number of demons which aid
the scourge with acquisition of new food, feeding and maintaining the growth
of the scourge on the planet itself.

\subsection{Demons}
\label{sec:Demons}

Once a scourge has learned enough about other biological lifeforms, it begins
to spawn its own creatures, modelled after those that it has absorbed.
However the spawn that the scourge produce are often horrible mockeries of the
original. Creatures or animals are often spawned with horrible deformities, or
with severe disabilities and are often just barely capable of performing the
tasks they were designed by the scourge to do. These creatures are
telepathically linked to their mother. The creatures its spawns perform a wide
variety of tasks, such as scouting new areas, defend the hive, directly hunt
for food, or even process the food that has already been captured. Spawn that
is created by the scourge in the \emph{abyss} are called \emph{demons}.

Demons serve a wide variety of functions in the abyss, but the most important
are the acquisition of new food and biological material, and the defence of
the abyss itself. Many demons are intelligent, but do not have their own
free will. Instead they are always controlled by the scourge, either directly
or indirectly through transmission of basic impulses and desires.

\emph{Dretches} are small, horribly deformed vaguely humanoid creatures that
lump about the abyss. They are the scourge's eyes and ears, allowing it to
see what is happening on its surface. It also uses the dretches as a first
line of defence. \emph{Quasits}, have a similar role and also serve as winged
scouts to the scourge.

\emph{Babau} are humanoid, swift and quick hunters that the scourge uses to
hunt down and kill prey. They work together with \emph{vrocks} which are
winged, vulture like creatures that roam the skies of the abyss looking down
for prey.

The \emph{succubus} is a female humanoid creature, capable of mammalian
reproduction that the scourge spawned for the sole purpose of collecting new
biological blueprints. The \emph{incubus} does the same, but has male
reproductive organs instead.
