\subsection{Farou Island}
\label{sec:Farou Island}

\emph{Farou Island} is a huge island off the east coast of
\nameref{sec:Arania}, and used to be the original home of the dragons, before
they moved east onto \nameref{sec:Draigynus}.

Farou contains a central mountain range, which is also called Farou. The
mountain range gives birth to many rivers, which in turn feed thousands of
smaller lakes, which again feed the islands vast and impressive tropical flora
and fauna. The island is simply known as the ``savage jewel'' by most humanoid
cultures, as its stunning beauty is only darkened by the feral beasts that
roam its jungles, and swamps.

The ancient dragons that first settled Aror made this island their home,
building housings, research labs, vaults, temples and even draconic cities on
its surface. After the giants followed them onto Aror, the island was the main
battle ground between these two ancient extra-planar species. Even though the
dragons won, many buildings, temples, and laboratories were destroyed during
the conflict, and now exist as ruins on the island. A specific mountain in the
Farou range is simply called the ``dragon grave'', as many dead dragons have
been buried on its steep slopes, and in its crevasses. After the core humanoid
races emerged on Aror, the dragons moved further east as to avoid interfering
with their natural development.

Slowly nature regained control of the island. Very few humanoid settlements
exist there, and most are expeditions of \nameref{sec:Fes al-Bashir}, that
have established harbours on the island's coast. Although the island is
mostly free of dangerous monstrous creatures, the thick vegetation, harsh
swamps, and treacherous and often unstable dragon ruins, make exploration
a dangerous endeavour.
