\subsection{Great Divide}
\label{sec:Great Divide}

The continent of \nameref{sec:Eilean Mor} is split in half, from the north west,
to the south east, by a large mountain chain called the \emph{Great Divide}.

Many dwarven, deepkin and especially dark elven clans call the mountains their
home, and have built small underground cities and settlement in the vast caves
of the mountain chains. The mountains are also known for being home to many
beast races, such as tribes of orcs and goblinoids.

Many rivers spring forth from the massive glaciers that top the great divide,
feeding hundreds of lakes as well as making the land fertile both to the north
and the south. South of the great divide lies a vast boreal forest called the
\nameref{sec:Dirgewood}.

The mountain chain has not only divided the land in half, but has also been
a major divider on the continent in the culture of the people. Since the north
of Eilean Mor has no major city kingdoms except \nameref{sec:Tredegar}, it has
always been viewed as more uncivilised than the southern region. This of
course holds no longer true, but that sentiment is still stuck with the people
of the south. So much so that the phrase \emph{``north of the divide''} has
become a moniker to denote someone who lacks manners.

Still the mountain range is a huge geographical obstacle, and only a few
dangerous mountain paths lead safely through the mountains. Since these paths
are often waylaid by monstrous bandits, rarely anyone ever crosses these
mountains, unless they absolutely have to. Most of the baronies and small
cities north of the great divide instead trade with the south, and the rest
of the world, through the sea.

The northern tip of the great divide is currently claimed by
\nameref{sec:Norbury}, who owns and operates a large castle in the mountain
range called castle \emph{Rothorn}. The castle oversees several mining
operations based in the mountain range producing ore such as copper and silver
for the kingdom.

The southern end is owned by \nameref{sec:Tredegar}, and is heavily mined
by various dwarven clans for the city kingdom. The iron and adamantine ore
from the mountains is heavily used by the kingdom to make excellent arms and
armour.
