\subsection{Kanaria Archipelago}
\label{sec:Kanaria Archipelago}

North of \nameref{sec:Karnak} lies a vast archipelago called the Kanaria
Archipelago. A vast collection of small and large islands that stretch out
into all directions. These islands share the same humid climate as most of
Karnak and are thus tropical paradises, with white beaches, palm trees, clear
water and covered with thick and lush rainforests. This paradise is only a
façade however, as most are inhabited by various tropical beast races, such as
hydras, or nagas, or tribal humanoids, and medusa, that are fiercely
protective of their islands.

As one of the few remaining frontiers, many explorers travel to the archipelago
in the hopes of discovering new land, islands, riches and gold. The waters
however are often treacherous, the island inhabitants dangerous and many
unsavoury groups. Slavers and pirates operate out of bases hidden in the
silver isles, preying on the native population, and passing ships alike.

Nevertheless the islands are known for harbouring many exotic plants, fruits,
and herbs, such as tobacco, chocolate and coffee. While the mountains and
volcanoes of the isles are filled with silver, gold, and
\hyperref[sec:Everblack]{everblack}. The trading companies of many large city
kingdoms have outposts and colonies on the isles, and often bitterly rival
over these resources. This brings them in direct conflict with the humanoid
tribes of the isles, called the \emph{Inua} who they often exploit, displace
or even enslave.

\subsubsection{Inua}
\label{sec:Inua}

The Inua are several native humanoid (halfling, dwarven, elves as well as
human) tribes that have lived on the islands of the archipelago since the last
ice age. Inua generally have darker skin, a stout and strong build due to their
reliance on heavy labour, and their own language called \emph{Inue}. They live
in tribes or small towns, and are excellent hunters, gatherers, and boat
builders. They often travel around the archipelago to hunt, fish, or to raid
other Inua tribes that dot the islands.

They often wear minimal clothing made out of fur and hide, and use crude and
primitive weaponry made out of stone, bone and wood. Very few Inua tribes have
mastered weapons out of metal, such as iron or even steel. Their appearance is
often frightening, as they enjoy piercing and tattooing themselves, especially
with white or other bright colours. Nevertheless they have a long, and rich
tradition and history, most of which is shared orally. The Inua are known to
be excellent warriors, cunning huntsmen, deeply spiritual, and communal people.

They are staunch believers of an entity they call \nameref{sec:Isamir}.
He tells them to honour the sea, the lakes, and all things that dwell within
them. He is said to conjure storms to cleanse islands, but also to grant
smooth weather so that the Inua can fish. He demands sacrifices of his people,
and they often sacrifice large catches they make, and sometimes even go so
far to sacrifice members of other tribes or foreigners to him. In recent years
however the worship of \nameref{sec:Isamir} has been challenged among the
Inua. Worship of \hyperref[sec:Forun]{Elora} (the ``lady of fire'' in Inua)
has become widespread, as she grants divine power, warmth and does not require
living sacrifices to be made to her.

Still the Inua are known for building secret temples in the jungles of their
islands. These temples are holy places, where no foreigner is allowed to
tread, and thus they are often guarded by mummified undead that the shamans of
the Inua create and command. These undead were once strong and proud warriors
that now fulfil the last great honour of the Inua: defend the holy sites
against intruders for all eternity. The Inua are expert embalmers, and their
shamans are renowned necromancers, and often also worship \nameref{sec:Morana}.

Although proud and strong warriors, the Inua are not as developed in terms of
technology as the rest of the humanoid that come to the archipelago. Even
though they more technologically primitive than the humanoid races of the city
kingdoms, their fierceness in battle, expert skill in stealthily attacking
with small manoeuvrable boats, unparalleled knowledge of the islands, and
their necromancer shamans allowed them to resist many invasions and
attacks. Some tribes have suffered defeat by the hands of the expeditions that
came to the islands, and have thus become wary, secretive or outright
xenophobic. Some tribes openly trade with the foreigners to their islands, in
hopes of making alliances or friends, while others are openly hostile and will
scare off or kill anyone that dares to set foot on their islands.

The Inua are in a constant battle against the foreigners that come to their
islands in the hopes of exploiting their resources. They openly wage sea
war against slavers, pirates and ships of trading corporations that seek
to displace them to gain access to their wealth.
