\subsection{Silver Isles}
\label{sec:Silver Isles}

In the centre of the vast sea that separates all continents lies a vast
archipelago called the \emph{Silver Isles}. A large collection of small
islands that stretch out into all directions, and are loosely connected to the
continent of \nameref{sec:Goltir} by a land bridge. Almost all of the islands
either lie on, or very close to the equator of \hyperref[sec:Aror]{Aror}. Most
are thus tropical paradises, with white beaches, palm trees, clear water and
covered with thick and lush rain forests.

While not technically a city kingdom, the region itself holds vast power,
both politically and commercially. The islands are rich with all manner of
natural resources, including silver, iron, copper, gold and Everblack. The
people of the isles (often simply called ``islanders'') have organised
themselves by establishing many large cities with vast trading empires,
as well as smaller ports, harbours and settlements all around the archipelago.

\subsection{Masia}
\label{sec:Masia}

These settlements are numerous, but one large harbour port sits in the centre
of it all: Masia. With about 400,000 citizens it is the largest, most
prosperous of all the harbour towns of the isle. It is not recognised as
independent as it is owned by the \nameref{sec:Ror-Aram Trading Corporation},
with \nameref{sec:House Ranian} holding a large stake in the settlement. The
city is thus ruled by a steward, that oversees that the city turns a profit
for the trading corporation. The city is known as haven for smugglers, pirates,
slave trade, but also for unfathomable riches, in which all sorts of luxury
goods - such as tobacco, cigars, coffee and chocolate, are sold.

Common male names are: Agustin, Alfonso, Alsen, Alvaro, Benito, Damian, Diego,
Enrique, Felipe, Gabriel, Garcia, Leon, Manuel, Martin, Ramon, Salvador, Tello,
Valeriano, Ydalla

Common female names are: Ana, Angel, Clara, Elena, Elvira, Fatima, Felipa,
Francisca, Gracia, Juana, Luzia, Manuela, Olalla, Serena, Ynes, Ysabel

\subsection{Fleeting Alliances}

Most smaller harbours, and port towns are usually independent ventures that
live off their agricultural products, as well as mining the mountains of
the islands for their riches. Their allegiances, political, cultural and
commercial significance vary greatly over time, and many attempt to sabotage
their competitors or even try to expand their operations by taking over other
islands. Some do it through the vague veil of threats, sabotage and political
intrigue, while others do it through threats, violence and outright war.

The major players involved in the region are Ror-Aram Trading Guild, House
Ranian, the \nameref{sec:Velvet Hand} as well as the mysterious
\nameref{sec:Silver Hand}. Thus some ports are nothing more than slaver
holdouts, while others are smuggler ports or straight out pirate havens.

Even though the area is often in disarray due to political chaos, struggle our
outright conflict between varying factions, the people of the isles have often
proven that they can work together should the need arise. As was the case during
the Devil siege of \nameref{sec:Forsby}, when the islands offered their highly
secured bays and harbour facilities as a staging ground for a counter strike.
Many of the native cities and ports, including Masia, even joined the counter
attack and provided valuable resources, weapons, experienced sailors and ships.

Keeping the smaller ports and harbour towns separated and in constant conflict,
unable to rally around Masia to form a kingdom, is the main goal of the larger
city kingdoms as well as \nameref{sec:House Ranian} and the Trading Guild. The
divide and conquer tactics have been successful in keeping the people of the
isles from becoming a major power on Aror for several centuries.
