\subsection{Suam Desert}
\label{sec:Suam Desert}

The \emph{Suam Desert} (suam is Gnoll for ``sea of fire'') is a vast sand
desert in the heart of the continent of \nameref{sec:Arania}. With scorching
temperatures averaging between 30, and 40 degrees it is a place hostile to
most forms of life.

The desert is dotted with small oases, which allow limited vegetation, and
fauna to survive the scorching temperatures of Aror's biggest hot desert.
Few humanoids traverse, or live in the desert. The desert is mostly inhabited
by gnolls, who see the Suam Desert as their holy birth right. Although the
oasis would allow for other humanoids to settle, very few do so, as the gnolls
drive everyone off their holy land. Apparently a large surviving settlement
of \nameref{sec:Ilians} live beneath the Suam Desert in a vast network of
sandstone tunnels. These Ilians have fled there from all around the world,
and live beneath the gnolls in secrecy.

The desert does contain a few natural sandstone mountains, valleys and
cliffs. These often contain oases at their basin, as the natural barriers
catch, and collect rain water. Many of these valleys are thus popular with
the local flora and fauna, and their cooling shade provide respite from
the scorching heat of the overhanging suns.

Both the desert, and its inhabitants are actively avoided by humanoids of
Arania, preferring to use ships and teleporters to circumvent crossing the
desert in its entirety. This sentiment is mostly shared by the gnolls of
the desert, as they rarely wander towards the coast, which are primarly
inhabited by the core humanoid races.
