\subsection{Walusian Desert}
\label{sec:Walusian Desert}

The \emph{Walusian Desert} lies between the \nameref{sec:Toralian Highlands}
and the Torainn Mountain range. It is a rocky desert, with high temperatures
in the summer, and mild temperatures in the winter.

The Walusian desert is highly populated in the west, especially at the coast.
Many humanoid settlements, villages, and harbours dot the coast from north
to south. The central land is mostly inhabited by monstrous races, who either
venture north to the Highlands, or west towards the coast to attack, pillage,
and raid the humanoid settlements. It is one of the few remaining areas in
which the \nameref{sec:Strife} is still ever present, as many baronies,
harbours, towns and villages are regularly raided, and destroyed by monstrous
invasions.

Although the people of the coastal region share a common ancestry, culture,
and traditions, they never managed to form a large city kingdom on their own,
due to the ever present threats from the monstrous raiders of the hinterland.
Unlike \nameref{sec:Forsby}, which lies on the same coast further north, the
coastal settlements never had regional tribes in the hinterland that acted as
buffer for monstrous raids, as the tribes of the Highlands did for city
kingdom. Although Forsby extends its military, and economic influence along
the coast, in an effort to stabilise the region, it is not enough to bring
peace to the coast of the Walusian Desert.

The coast is still home to various port cities of varying sizes, some of which
experience a modicum of peace, security, and stability. The biggest of which
is called \emph{Ostia Netum}, which lies in a large natural cliff, not unlike
Forsby itself. Various other smaller harbours in the area are \emph{Sentia},
\emph{Aguntum}, \emph{Sisak} and \emph{Solva}. Walusians are known to be
expert farmers, traders, ship builders, and sailors. Their expertise in
navigating even the most dangerous waters is renowned all across Aror.All in
all the coastal region is estimated to be the home of roughly fifteen million
inhabitants.

Common male names are: Alfano, Adon, Armano, Azo, Bino, Benetto, Carino,
Castello, Cino, Favio, Ferrando, Gilo, Grego, Ileo, Lionardo, Massimo, Matteo,
Meo, Neri, Peder, Perseo, Salvi, Vincentio (Vincent), Zane.

Common female names are: Adaleta (Adeleta), Alagia, Albiera, Austina,
Beatrisia, Belladonna (Belda, Donna), Cara, Cecilia (Cilia), Cina, Dorotea,
Ermellina (Lina), Finola, Leonetta, Lionarda (Liona), Milia, Orelia, Osana,
Scarleta, Soliana, Vivianna, Zuana
