\subsection{Yua'cata}
\label{sec:Yuacata}

Yua'cata is a vast rain forest on the main land of \nameref{sec:Karnak}. It is a
wild and savage place, untouched by civilisation. The rain forest surrounds
the vast fresh water lake of \emph{Mu'ut}, which is the largest fresh water
reservoir on Aror.

Yua'cata is home to thousands of different species of animals, such as birds,
insects, reptilians as well as predatory felines and snakes. The warm climate
and the abundance of water and resources lead to a diverse and large biome. Many
monstrous creatures, as well as many humanoid tribes call the jungle their
home.

\subsubsection{Mu'ut}
\label{sec:Muut}

\emph{Mu'ut} is a large fresh water lake in the centre of the continent of
Karnak. It is geologically active, and its warm water fuels thousands of
smaller and bigger rivers that flow in all directions towards the sea. Mu'ut
can be considered the heart of the Yua'cata rain forest, as its warm waters
fuel the tropical climate, rain and thus the vast rain forest of Yua'cata.
It is the largest fresh water reservoir of Aror, and gives lives to untold
hectares of land, and all those that inhabit it. To many native intelligent
tribes the lake itself is worshipped as a live giving deity.

\subsubsection{Tribes}

The jungle is also inhabited by thousands of tribes of sentient monstrous and
humanoid races, including humans, \hyperref[sec:Wood Elves]{wood elves},
\hyperref[sec:Medusa]{medusa}, as well as lizardfolk, goblinoids. and
sahuagin. Most of these are hunters and gathers, and often differ greatly in
traditions, customs and believes. There is one cultural element that many
tribes share however: an almost holy reverence of the lake of Mu'ut.

\subsubsection{Savage Elves}
\label{sec:Savage Elves}

The most notorious of the jungle tribes are the wood elven tribes of the
Xanarian river. Among other races these wood elves are often referred to as
\emph{savage elves}. They worship an ancient being called \nameref{sec:Xir}
who they believe sleeps beneath the surface of the holy rivers of Mu'ut. Xir
teaches that all unbelievers are impure, and can only be redeemed by feeding
them to him by drowning them in the river. These wood elves raid, pillage,
murder and sacrifice other sentient races they come across without mercy, as
in their eyes there is only one way for them to be redeemed in the eyes of
their lord.

The Xanarian tribes also practice cannibalism. They believe that eating their
own kind after death makes their deceased continue to live within them. They
rarely eat outsiders, as they believe their flesh to be corrupt and impure.

Although the Xaniarian tribes are far and few between, stories told by
explorers have passed into legend, and have become warped, exaggerated, and
twisted over the course of many centuries. The Xanarian tribes are still
dangerous, and hostile towards outsiders, and are thus often actively avoided
by anyone that travels the region.
