\ifimages
\clearpage
\incgraph{media/irene-colour.\imagesuffix}
\clearpage
\fi

\subsection{Irene de'Var}
\label{sec:Irene deVar}

Irene de'Var, Countess of Saremen, is the current ruler of \nameref{sec:House
  deVar} of Saremen in \nameref{sec:Helmarnock}, and thus one of the five
rulers that make up the council of the city kingdom.

Irene is about two metres tall, and has short white dyed hair, deep and dark
red eyes, and blue finger nails that show her usage of \nameref{sec:Ramesk}.
Her origin as a \hyperref[sec:Snow Elves]{snow elf} has granted her with
natural grace and beauty, which she complements with elaborate and intricate
silken garments, expensive and impressive jewellery (both magic and mundane)
as well as graceful posture and mannerism.

The countess is seen as a cunning politician, and a passionate and genius
orator capable of inspiring and moving their subjects through speeches, and
using her commanding presence and eloquence to resolve conflicts through
negotiations. To her people she shows her warmer, more compassionate side,
often meeting her own subjects on festivities or other special occasions.

Originally a snow elf diplomat of Helmarnock stationed in \nameref{sec:Forsby},
she was turned into a vampire in MI:1081 by the Count Nareil of House de'Var,
to serve as an heir in his lineage of nobility. His nobility has roots back to
the time of the great betrayal by \nameref{sec:Morana} during the aeon of
strife, and was instrumental in establishing and defending the city on the
island of Saremen amidst the constant wars and battles fought against the
beast races. Even though the countess has been trained in classical sword
fighting, and especially fencing, she prefers diplomacy over war and conflict.

Irene has ruled House de'Var since MI:1121 after the death of Nareil. She has
since restructured and reformed the House, leading them to become the most
dominant noble family on the island. Irene largely follows the houses traditions
and Nareil's teachings, and stays true to Nareil's style of leadership of
benevolence and diplomacy: Irene outlawed slavery on Saremen in MI:1122
freeing all who were previously enslaved to a citizen of Saremen, and pushed
the council to allow \nameref{sec:Umgeher} and \nameref{sec:Gorgons} back into
the kingdom. The ban on slavery was partially effective, since the city
kingdom has signed the \nameref{sec:Vonir Accord} before her push toward slave
liberation. Even though no new slaves may be taken within Saremen, and all
slaves of Saremen citizens have been freed, slavers of other nations,
including the other islands of Helmarnock are still allowed to follow that
practice on Saremen.  She initiated a council vote on slavery, but was
defeated two to three.

Generally Irene de'Var attempts to drive the society of Saremen towards
individualism, liberty and freedom, lifting many restrictions both in the
social sphere - such as lifting marriage restrictions between mortals and
vampires, ending slavery or allowing Gorgons to become citizens - as well as
in the economical sphere by lowering taxes and making it easier for companies
to do business. Her political leanings and open policies, together with her
well-received, compassionate speeches towards her subjects, have made her a
well beloved and respected countess among the citizens of Saremen. Although
she is a brilliant politician and orator, she keeps a cadre of highly skilled
advisers as a ``council of ministers'' that oversee other aspects of the
island, such as defence, finances, civil engineering or oversee the Academy of
Arcane Arts.

\begin{35e}{Irene de'Var (13 Bard / 2 Fighter)}
  \srditem{Size/Type}{Medium Undead (Vampire)}
  \srditem{Hit Dice}{15d12 (98 HP)}
  \srditem{Initiative}{+13}
  \srditem{Speed}{30 ft.}
  \srditem{Armour Class}{40 (9 dex, 10 armour, 5 deflection, 6 natural), 24
    touch, 31 flat-footed}
  \srditem{BAB / Grapple}{+11 / +17}
  \srditem{Attack}{+24 +4 Rapier 1d6+6 18-20x2}
  \srditem{Full Attack}{+24/+19/+14 +4 Rapier 1d6+13 18-20x2}
  \srditem{Space/Reach}{5 ft./5 ft.}
  \srditem{Special Attacks}{Blood Drain (Ex), Create Spawn (Su), Energy Drain
    (Su)}
  \srditem{Special Qualities}{Scent (Ex), Feral Blindness (Ex),
    Damage Reduction (Su), Resistances (Ex) DR 10 cold and electricity,
    Spider Climb (Ex), Turn Resistance (Ex) +4, Fast Healing (Ex)
  }
  \srditem{Class Features}{Bardic music, Bardic knowledge, Countersong,
    Fascinate, Inspire courage +2, Suggestion, Inspire greatness, Song of
    Freedom
  }
  \srditem{Spells Known}{\emph{Level 0}: Detect Magic, Fleeting Fame, Ghost
    Sounds, Dancing Lights, Prestidigitation, Read Magic

    \emph{Level 1}: Improvisation, Invisibility (Swift), Silent Image, Identify

    \emph{Level 2}: Alter Self, Detect Thoughts, Invisibility, Suggestion

    \emph{Level 3}: Blink, Haste, Dispell Magic, Halt

    \emph{Level 4}: Dimension Door, Freedom of Movement, Invisibility
    (Greater), Blinding Beauty

    \emph{Level 5}: Dispell Magic (Greater), Cacophonic Burst (Greater)
  }
  \srditem{Saves}{Fort +12, Ref +22, Will +26}
  \srditem{Abilities}{Str 22, Dex 28, Con -, Int 18, Wis 22, Cha 36}
  \srditem{Skills}{Bluff (+39), Intimidate (+41), Perform (Oratory) (+31),
    Perform (Dance) (+31), Diplomacy (+41), Gather Information (+31),
    Knowledge (Arcane) (+22), Knowledge (Royalty \& Nobility) (+22), Knowledge
    Local (+22), Sense Motive (+42), Spellcraft (+22), Hide (+17), Move
    Silently (+17), Search (+12), Listen (+14), Spot (+14)
  }
  \srditem{Feats}{Force of Personality, Leadership, Extend Spell, Metamagic
    Song, Improved Weapon Finesse, Improved Initiative, Weapon Finesse,
    Heighten Spell}
  \srditem{Items}{Royal Regalia of Saremen (+8 Charisma, +10 Armour Class),
    Seal of Saremen (+5 Resistance, +10 Diplomacy, +10 Sense Motive), Crown of
    Saremen (+5 Deflection AC, +10 Intimidate)
  }
  \srditem{Challenge Rating}{18}
  \srditem{Alignment}{Neutral Good}
  \srditem{Advancement}{By character class}
\end{35e}
