\subsection{Taras}
\label{sec:Taras}

Taras, a human male, was born in \emph{MI:1898} in a small village near
\nameref{sec:Tredegar}. Hailing from a smaller house of nobility, Taras had
the means to join a wizardry guild at an early age. After having attained a
basic level of arcane mastery, he travelled Aror, especially to visit other
arcane institution such as the \nameref{sec:Magistrata Arcanum}, and the
\nameref{sec:Hall of Knowledge}. On these travels, he met his future
compatriots, namely Xias, a human barbarian from Norbury, as well as Arissa an
elven rogue, and diplomat from Forsby.

All three of them were present in \nameref{sec:Nen-Hilith}, when it came under
siege by the dragons; albeit their aid proved invaluable their city was lost in
\emph{MI:1920} when the giants razed the city to the ground. Together with the
survivors of the city, they fled north to \nameref{sec:Goltir}, and began
rebuilding the elvish and halfling kingdom.

When the newly formed \nameref{sec:Avenfjord} came under attack by the Formians,
intelligent, insect like monsters, the three aided the then ruling monarch once
again. As the war dragged on, the Formians threatened the newly formed, under
equipped, and staving kingdom with extinction. It was Taras who figured out how
to transform the \nameref{sec:Black Blight}, to only affect Formians. After a
fateful battle against the Formian queen, Tara's formulae was spread among the
Formians driving them to near extinction.

Scholars, who interviewed living eye-witnesses, concluded that Taras gained an
interest in statecraft, diplomacy, and leadership during the time with the elves
and halflings, but also a huge disdain towards monstrous races, who he began to
see as a threat to humanoid peace.

Xias then wished to travel home, and both Arissa and Taras followed him to
Norbury. After a particular devastating, and deadly sea raid from
\nameref{sec:Iafandir}, the company of three agreed to raise an army for a
counter attack. After establishing an outpost on the continent, Taras' belief
that monsters were inherently violent, while humanoids had no trouble living
together peacefully became stronger. The years spent dealing with the
monstrous races of the savage lands, turned that belief into a racist, and
militant fervour. Although Xias was the ruler of \nameref{sec:Morkan}, his
hatred for the monstrous races ultimately lead him to betray his own friends.

After seeing that the people on his side during the coup, he shared his beliefs
and doctrine. Although it did not convince everyone, many of his subjects also
shared his conviction. This reciprocation lead to a hardening of Tara's belief,
and he formed an ideology of racial superiority around it, and turned his city
kingdom into a tool to see this ideology implemented.

Taras continued his arcane studies, and in \emph{MI:1968}, at a mighty age of
70, he achieved what very few had achieved before him: lich-dom. Taras, now
bestowed with eternal non-life, he vowed to rule forever-more.

He is known to be excellent statesman, politician, public speaker, but also a
fundamentalist, militarist and a fervent defender of his ``decree of purity'',
in which he seeks to eradicate any monstrous creatures from
\nameref{sec:Iafandir}. Under his reign the kingdom of \nameref{sec:Morkan}
became totalitarian state, committing an unimaginable number of crimes,
including mass enslavement, genocide, torture and suppression of dissidents.
Both the \nameref{sec:Magistrata Arcanum} and the \nameref{sec:Hall of
  Knowledge} acknowledge that Taras is currently the strongest arcane wielder
on Aror by \emph{MI:197}, although he does not hold the title of ``Grand
Magus''.

Taras always wars his royal regalia and crown, and reigns from the central
spire of Morkan. He holds addresses to his subject from its balcony regularly,
but also accepts visitations from common folk, in an attempt to make him
appear as a king of the people. His generals attend most of the public
celebrations and appointments in his place, for example, Eilane his chief
diplomat attends meetings of the \nameref{sec:Two Courts} in his place.

\begin{35e}{Taras (17 Wizard)}
  \srditem{Size/Type}{Medium Undead (Lich)}
  \srditem{Hit Dice}{17d12 (114 HP)}
  \srditem{Initiative}{+8}
  \srditem{Speed}{30 ft.}
  \srditem{Armour Class}{27 (+5 Natural, +8 armour, +4 Dexterity), 14 touch,
    25 flat-footed
  }
  \srditem{BAB / Grapple}{+8/+10}
  \srditem{Attack}{+10 Touch Attack 1d4+2 20x2}
  \srditem{Full Attack}{+10/+5 Touch Attack 1d4+2 20x2}
  \srditem{Space/Reach}{5 ft./5 ft.}
  \srditem{Special Attacks}{Touch Attack, Paralyzing Touch (Su)}
  \srditem{Special Qualities}{Fear Aura (Su), +4 Turn Resistance, Damage
    Reduction 15/bludgeoning and magic, Immunity to Cold, Electricity, and
    Polymorph, +1 Inherent Bonus to Intelligence, +1 Inherent Bonus to
    Charisma, Immunity to Mind Affecting Spells (from item), Telepathy (30
    ft.) (from item)
  }
  \srditem{Class Features}{Summon Familiar, Scribe Scroll}
  \srditem{Spells Known}{\emph{Level 0}: All

    \emph{Level 1}: Alarm, Mage Armour, Identify, Charm Person, Shivering Touch,
    Magic Missile

    \emph{Level 2}: Web, Detect Thoughts, Shatter, Mirror Image, Invisibility,
    Rope Trick

    \emph{Level 3}: Dispel Magic, Magic Circle Against Good, Magic Circle
    Against Evil, Wind Wall, Ray of Exhaustion, Fly, Haste, Slow, Bands of
    Steel, Shivering Touch

    \emph{Level 4}: Dimensional Anchor, Dimension Door, Confusion, Enervation,
    Greater Invisibility, Mirror Image, Greater

    \emph{Level 5}: Teleport, Wall of Stone, Dominate Person, Hold Monster,
    Blink, Greater, Contingent Energy Resistance

    \emph{Level 6}: Dispel Magic, Greater; Repulsion, True Seeing,
    Contingency, Disintegrate, Anticipate Teleportation

    \emph{Level 7}: Banishment, Teleport, Greater; Arcane Sight, Greater;
    Finger of Death, Stun Ray

    \emph{Level 8}: Mind Blank, Greater Prying Eyes, Prismatic Wall, Chain
    Dispel

    \emph{Level 9}: Foresight, Time Stop, Energy Drain
  }
  \srditem{Saves}{Fort: +10, Ref: +12, Will: +20}
  \srditem{Abilities}{STR: 14, DEX: 14, CON: -, INT: 32, WIS: 20, CHA: 24}
  \srditem{Skills}{Diplomacy: 37, Bluff: 21, Concentration: 20, Knowledge
    (Arcane): 31, Knowledge (History): 31, Perform (Oratory): 27, Spellcraft:
    31
  }
  \srditem{Feats}{1: Able Learner, Improved Initiative, 3: Arcane Mastery,
    5: Extend Spell, 6: Craft Wondrous Item, 9: Quicken Spell, 10: Spell Focus
    (Necromancy), 12: Split Ray, 15: Reach Spell, Chain Spell
  }
  \srditem{Items}{Royal Regalia of Morkan (+8 Charisma, +8 Armour Bonus),
    Tara's Command (+10 Intelligence, Permanent \emph{Levitate} as spell),
    Taras' Seal (Ring, +5 Resistance, Immunity to Mind affecting spells,
    Telepathy (30 ft.)), Crown of Morkan (+8 Wisdom, +10 Diplomacy)
  }
  \srditem{Challenge Rating}{22}
  \srditem{Alignment}{Lawful Evil}
  \srditem{Advancement}{By character class}
\end{35e}
