\subsection{Grand Magi Triumvirate}
\label{sec:Triumvirate}

The \emph{Grand Magi Triumvirate} (or simply the Triumvirate) is the informal
name given to three snow-elven sisters (identical triplets), called Euryale,
Stheno and Medusa, that were powerful grand magi wizards, and the leader of the
\nameref{sec:Magistrata Arcanum}.

The sisters were born in GT:713 on the western shore of Arania, as citizens of
the rising kingdom of Esmayar. After learning what arcane knowledge they could
in the recently founded kingdom, they moved to Fes al-Bashir and applied to the
\nameref{sec:Hall of Knowledge}. Although they were accepted as students, after
several failures to adapt to the strict and traditional culture of the city and
the university, the sisters were expelled. Driven to complete their arcane
studies, they travelled north towards Forsby, and joined the Magistrata
Arcanum. After finishing their studies in the Arcanum, they joined the staff
as tutors, professors and teachers, culminating in their ascension to high
magus and leader of the Arcanum in GT:750. They ruled the Magistrata Arcanum
together, thus earning them the title of ``triumvirate''. In GT:752 they
together completed all tasks required to become Grand Magi, and were awarded
that honorific by the Hall of Knowledge.

In GT:755, during the \nameref{sec:First Devil Invasion} the three sisters
were believed to have been killed when the devils detonated a magical
artefact, causing the hall of the Magistrata to collapse. In truth the devils
had used the explosion as a ploy, and had instead abducted the three sisters
on the orders of \nameref{sec:Forneus}.

During their time in the layers, Forneus forced them to research the
``Marilith'', mightiest creature of battle the \nameref{sec:Scourge} had
produced. After the sisters had found the creatures weaknesses, capabilities
and origins, Forneus forced them to continue their research into either
freeing Mariliths from their psionic enslavement, or by producing new
Mariliths loyal to the devils. The sisters stalled as long as they could,
slowing down the work, but Forneus kept the sisters alive for centuries so
that they may be able to complete their research. The sisters almost finished
their research on breeding new marilith, but they ultimately refused to
cooperate when the devil lord wanted to test their work on captured humanoids,
aurelis and tieflings. Enraged by their refusal to cooperate, Forneus used the
conversion serum on the sisters, turning them into hideous half-human,
half-snake like creatures. Medusa's lower torso was turned into that of a
snake, and her intellect was heightened. Euryale grew an additional set of arms,
and her upper body strength increased. Stheno grew wings, allowing her to fly.
All three sisters grew patches of scaly skin all across their body, and their
eyes turned into an unnaturally glowing white. Their upper torsos remained
mostly unchanged, and their facial features remained largely elfish.

Forneus was impressed by the partial transformation, and ordered his minions to
replicate the serum, and begin converting as many of his slaves as possible.
Although he attempted to force the sisters to perfect their formula, they
instead began to research a cure. Not only for themselves, but also for those
who'd be forced through the same horrible transformation.

In \emph{GT:1082}, almost 330 years after being abducted, the forces of the
second crusade invaded the layers to free the sisters. At the eve of their
rescue, the sisters told Forneus that they had created a serum, and distributed
it to his victims, allowing them to turn back to their original form. Forneus,
in vengeful retaliation, cursed the sisters by turning their hair into snakes,
and enchanting their eyes so anyone their eyes would meet would turn into
stone. With their cure no longer working on the altered sisters, he told them
that the crusaders will not find the humanoids they were searching for, only
deadly and vicious monsters.

After the crusaders returned them from the layers of hell, the sisters split
up and hid themselves away in the remote places of Aror. Euryale went into the
Goban jungle, Stheno in the jungles of Yua'cata and Medusa hid in the Savage
Lands. Even though the lived in exile, they earned themselves followers who
attempted to aid them in finding a cure. But without the life extending magic
of Forneus their health declined faster than they progressed towards a
cure. On the behest of their followers, and \hyperref[sec:Medusa]{children},
they entered a deep sleep, a magical stasis, until a cure could be found.

In modern times the research about their cure, and more tragically, the location
of their final resting places have been lost to the aeons.

\graham{We have failed you horribly.}
