\subsubsection{Bone to Bone}
\label{sec:Bone to Bone}

\songquote{Merserburger Zaubersprüche}{
  sôse bênrenki, sôse bluotrenki, sôse lidirenki: \\
  bên zi bêna, bluot zi bluoda, \\
  lid zi geliden, sôse gelîmida sîn.
}

\emph{Bone to Bone} is an ancient healing ritual performed by the followers of
the \nameref{sec:Old Ways}. It is meant to cure someone of all wounds, as well
as restore broken or damaged limbs. It also restores one lost body part, such
as cut off limbs, lost eyes or missing ears. The ritual is cast by one shaman of
the old ways, with the help of six others.

First, a very shallow grave must be dug, in which the recipient of the healing
magic must be placed when both moons stand high up in the sky. All casters must
stand around the grave, chanting the healing words repeatedly, supported
musically by drums or a low rhythmic drone. The recipient of the ritual is fed
a specially brewed potion which puts them to sleep for twenty four hours. Once
sleep has set in, the grave is covered thinly with dirt. Not too much, so that
the patient my escape by himself, but just enough to hide him from the world.

Then, last but now least, a living creature, often livestock, captured wild
animal, is bound and shackled, and then sacrificed above the grave. The blood
of the sacrifice is then allowed to seep into the grave, giving its life to
the patient buried underground.

Once twenty four hours are up, and the ritual was completed successfully, the
live of the animal has been transferred to the patient, healing him and
restoring lost limbs. The recipient is freed from the grave, with his body
healed and any missing limb restored. If the ritual failed, the person wakes
up prematurely and unhealed, and must dig itself out or suffocate beneath the
dirt.

A variation of this ritual exists, called \emph{Blood to Blood}, in which
a sentient humanoid creature is sacrificed instead of an animal. This ritual
resurrects the dead buried in the shallow grave, but is often banned in many
tribes and societies. If this alternate version of the ritual fails, the
caster is killed along the sacrifice to allow the deceased to rise again.
However sometimes the soul of the target is broken in the process.

\begin{35e}{Bone to Bone}
  \srditem{Effective Level}{6th}
  \srditem{Skill Check}{Knowledge (soul magic) or Knowledge (old ways), DC20,
    3 successes \textbf{and} Perform (oratory), DC20, 3 successes}
  \srditem{Failure}{%
    Target awakens prematurely after 2d4 hours, and must succeed a DC13
    fortitude saving throw or suffocate to death in the shallow grave. No hit
    points or effects are healed.
  }
  \srditem{Components}{V, S, M, F}
  \srditem{Casting Time}{60 minutes}
  \srditem{Range}{Personal}
  \srditem{Target}{One target, buried in the grave}
  \srditem{Duration}{Instantaneous}
  \srditem{Saving Throw}{Will negates, harmless}
  \srditem{Spell Resistance}{Yes, harmless}
  \srditem{Focus}{Shallow grave with the patient}
  \srditem{Components}{One creature of type \emph{animal} as sacrifice. One
    potion of \emph{deep sleep} that costs 20 shards in materials to make.}
  \srditem{Description}{%
    If the ritual succeeds the patient awakens after 24 hours, and heals the
    \emph{animals number of HD x d12} of hit points, and curing all of the
    following status effects: ability damage, blinded, confused, dazed,
    dazzled, deafened, diseased, exhausted, fatigued, feebleminded, insanity,
    nauseated, sickened, stunned, and poisoned.

    The spell also regrows one lost limb.
  }
\end{35e}

\begin{35e}{Blood to Blood}
  \srditem{Effective Level}{7th}
  \srditem{Skill Check}{Knowledge (soul magic) or Knowledge (old ways), DC24,
    3 successes \textbf{and} Perform (oratory), DC20, 3 successes}
  \srditem{Failure}{%
    Target is resurrected, but the caster's live is taken (no saving throw)
    along with the sacrifice.

    There is a chance the target returns with a
    \hyperref[sec:Broken Soul]{broken soul}.
  }
  \srditem{Components}{V, S, M, F}
  \srditem{Casting Time}{60 minutes}
  \srditem{Range}{Personal}
  \srditem{Target}{One target, buried in the grave}
  \srditem{Duration}{Instantaneous}
  \srditem{Saving Throw}{Will negates, harmless}
  \srditem{Spell Resistance}{Yes, harmless}
  \srditem{Focus}{Shallow grave with the patient}
  \srditem{Components}{One creature of type \emph{humanoid} as sacrifice. One
    potion of \emph{eternal sleep} that costs 500 shards in materials to
    make.}
  \srditem{Description}{%
    Upon failure or success of the ritual, the target rises from the dead
    after 24 hours, as if the seventh level cleric spell \emph{Resurrection}
    had been cast upon it.

    Failure kills the caster (no saving throw), and might break the targets
    soul as if by \nameref{sec:Broken Soul} (will save DC 26).
  }
\end{35e}
