\subsection{Primal Curse}
\label{sec:Primal Curse}

The \emph{primal curse} is an ancient druidic ritual, in which druids bestow
the curse of \hyperref[sec:True Lycanthropes]{true lycanthrophy} upon a
target.

First a one or two litres of water must be gathered that has rested in the
foot prints of the desired animal for a few minutes. So, if the target should
become a werewolf, the water must have been in the foot prints of a wolf for a
few minutes. This water must then be blessed by mixing it with a drop of blood
of all the druids involved in the ritual. Then half of the blood of the victim
must be drained, while he is simultaneously force fed the mixture of blood and
water.

If the ritual succeeds the target becomes a
\hyperref[sec:True Lycanthropes]{true lycanthrope}, and if the spell fails the
druids that have given their blood to bless the water, are forced into rabid
animal shapes of the intended were creature, and will prey on each other.

\begin{35e}{Primal Curse}
  \srditem{Effective Level}{6th}
  \srditem{Skill Check}{Knowledge (nature) DC26, 4 successes}
  \srditem{Failure}{%
    All druids are forced into a \emph{chaotic evil} animal shape corresponding
    to the animal of the intended were creature. They cannot determine friend
    from foe, and will thus attack each other.
  }
  \srditem{Components}{V, S, M, F}
  \srditem{Casting Time}{60 minutes}
  \srditem{Range}{Personal}
  \srditem{Target}{One target, bound and helpless}
  \srditem{Duration}{Instantaneous}
  \srditem{Saving Throw}{Will negates, DC: 16 + caster's \emph{Wis} modifier}
  \srditem{Spell Resistance}{Yes}
  \srditem{Focus}{The water gathered from the animal's foot prints, as well as
    the stone altar upon which the victim is bound.}
  \srditem{Components}{One or two litres of water gathered from an animal's
    foot prints. The animal from which this water is gathered determines the
    animal form of the lycanthrope if the ritual succeeds. As well as drops of
    blood from each druid involved in the ritual, costing each druid 1000 XP.}
  \srditem{Description}{%
    If the ritual succeeds the patient turns into a true lycanthrope.

    If the ritual fails each druid that has given blood are forced into a
    \emph{chaotic evil} animal shape corresponding to the animal of the
    intended were creature. They cannot determine friend from foe, and will
    thus attack each other.
  }
\end{35e}
