\subsection{Summon Runemaster}
\label{sec:Summon Runemaster}

The ritual \emph{Summon Runemaster} is used to conjure the Runemaster and plead
for him to each one \nameref{sec:Rune Magic}. He never shows up himself, instead
sending his minions (erinyes) instead, due to security concerns.

A successful summoning requires a summoning circle in the shape of a
pentagram, adorned with candles in each corner, in which a living humanoid is
sacrificed in his honour. After the sacrifice has been killed, one must plead
his or her case on why one is worthy enough to receive the power that comes
with rune magic. The Runemaster then either honours this plea by sending a
minion (or show up directly) or deny this request by ignoring it.  If a devil
does appear, one must strike a deal with the devil which often includes aid in
learning rune magic.

Many captured rune carvers have reported that it took them several attempts to
gain the master's attention. While others have tried to impress with the
Runemaster by carving embellished runes into their summoning sacrifice's skin
with various degrees of success. Other rune carvers have offered powerful
magical artefacts, their servitude, or the souls and bodies of other living
humanoids in the hope of gaining favour with the devil.

\begin{35e}{Summon Runemaster}
  \srditem{Effective Level}{6th}
  \srditem{Skill Check}{Knowledge (planes) DC22, 1 success, Perform
    (Oratory) DC:22 3 successes
  }
  \srditem{Failure}{Nothing.}
  \srditem{Components}{V, S, M, F}
  \srditem{Casting Time}{60 minutes}
  \srditem{Range}{Personal}
  \srditem{Target}{None}
  \srditem{Duration}{Instantaneous}
  \srditem{Saving Throw}{None}
  \srditem{Spell Resistance}{No}
  \srditem{Focus}{A pentagram with five candles in each corner, and a humanoid
    sacrifice in the middle of the pentagram. As well as a dagger, short sword
    or knife that will be blessed by the Runemaster, or one of his minions,
    should they grant an audience.
  }
  \srditem{Components}{A masterwork dagger, short sword or knife. And one living
    humanoid creature as a sacrifice.
  }
  \srditem{Description}{The living humanoid sacrifice must be killed with the
    dagger, knife or short sword. After which the caster may start his plea
    on why he is worthy to receive rune magic. If the plea is heard and found
    worthy, the \nameref{sec:Runemaster} will send a minion to negotiate a deal
    which often encompasses aid in learning \nameref{sec:Rune Magic}.
  }
\end{35e}
