\subsection{Summon Beleth}
\label{sec:Summon Beleth}

This ritual attempts to summon the devil \nameref{sec:Beleth}, or one of her
minions. To complete this ritual the summoner must write his issue or problem,
often the charge brought against the summoner, onto a piece of paper with his
own blood with the feather of a raven. This paper must then be burnt while
pleading for Beleth's help.

Beleth may decline the summoning, but if she accepts she often sends one of
her minions instead. If she accepts she often demands servitude, arcane
knowledge and artefacts in exchange for aid in legal proceedings. Beleth, and
her minions, only resort to illegal activities (such as threat or blackmail)
only if the case cannot be won legally.

\begin{35e}{Summon Runemaster}
  \srditem{Effective Level}{6th}
  \srditem{Skill Check}{Knowledge (planes) DC20, 1 success, Perform
    (Oratory) DC:20 3 successes
  }
  \srditem{Failure}{Nothing}
  \srditem{Components}{V, S, M, F}
  \srditem{Casting Time}{30 minutes}
  \srditem{Range}{Personal}
  \srditem{Target}{None}
  \srditem{Duration}{Instantaneous}
  \srditem{Saving Throw}{None}
  \srditem{Spell Resistance}{No}
  \srditem{Focus}{A letter written with blood.}
  \srditem{Components}{A writing feather from a black raven, a piece of paper,
    and enough blood of the summoner to pen a letter.
  }
  \srditem{Description}{The summoner must pen a letter with the writing feather
    from a black raven and the summoner's own blood, detailing the legal problem
    the summoner is facing. Then the letter must be burnt, and the summoner may
    plead for Beleth's help. Beleth may accept the call to aid, or deny it.
  }
\end{35e}
