\subsection{Summon Ishtar}
\label{sec:Summon Ishtar}

This ritual attempts to summon the devil \nameref{sec:Ishtar}, or one of her
minions. To complete this ritual the summoner must dissect a dead corpse. Any
corpse, such as those of a dead rat, bat, or a frog will suffice. The summoner
must carefully spread out the innards on a dissecting table, and narrate the
procedure to proof is skill and knowledge of medicine and biology to Ishtar.
The summoner may then pray and plead to Ishtar herself to entice her to
appear.

Ishtar may decline the summoning, but if she accepts she often sends one of
her minions instead. If she accepts she often demands servitude, arcane
knowledge or artefacts in exchange for knowledge about medicine, healing and
biology.

\begin{35e}{Summon Ishtar}
  \srditem{Effective Level}{6th}
  \srditem{Skill Check}{Knowledge (planes) DC22 1 success, Heal DC:22 2
    successes, Perform (Oratory) DC:22 1 success
  }
  \srditem{Failure}{Nothing}
  \srditem{Components}{V, S, M, F}
  \srditem{Casting Time}{30 minutes}
  \srditem{Range}{Personal}
  \srditem{Target}{None}
  \srditem{Duration}{Instantaneous}
  \srditem{Saving Throw}{None}
  \srditem{Spell Resistance}{No}
  \srditem{Focus}{A corpse dissected on a table}
  \srditem{Components}{A corpse that was carefully and skilfully dissected,
    as well as the corpse's innards and the sharp knife that was used during
    the dissection.
  }
  \srditem{Description}{The summoner must dissect a corpse (any corpse, such
    as that of a small animal will do), showing off the summoner's skills as a
    surgeon while narrating the procedure to show off the summoner's knowledge
    about medicine. The summoner may then plead for Ishtar's help. Ishtar may
    accept the call for aid, or deny it. If successful either Ishtar herself,
    or one of her minions will appear to start negotiation.
  }
\end{35e}
